---
title: "Open Government Data, opendata.swiss"
date: "2023-11-04"
output: html_document
---

## Dataset: Geschäftsorganisationen (business organisations)

Die Geschäftsorganisationen stellen eine organisatorische Strukturierung der Transportunternehmen nach abrechnungstechnischen und kundinformativen Merkmalen dar.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/geschaftsorganisationen-business-organisations)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/goch)

Auto generated R starter code for data set goch@oevch.

## Metadata

- **Publisher** `Specialist office Open Data`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `Specialist office Open Data`
- **Maintainer_email** `opendata@sbb.ch`
- **Keywords.de** `['transportunternehmen', 'vu', 'go', 'geschaftsorganisation', 'said', 'tu', 'vvu', 'verkehrsunternehmen', 'sboid', 'transportunternehm']`
- **Issued** `2016-12-01T12:00:00`
- **Metadata_created** `2017-03-02T09:12:53.299952`
- **Metadata_modified** `2023-11-04T02:27:42.363338`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 026de4d5-5a5f-43da-b241-70760a626524
# Description              : Die Geschäftsorganisationen stellen eine organisatorische Strukturierung der Transprotunternehmen nach abrechnungstechnischen und kundinformativen Merkmalen dar.
# Issued                   : 2018-12-08T06:35:05.984593
# Modified                 : 2023-11-03T13:10:07.294765
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/291976e2-cd76-4b9f-a1c0-40da0cd45347/resource/288e35a9-e773-4005-b7e7-4aed88848ab5/download/go-liste.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@sbb.ch | Specialist office Open Data
