---
title: "Open Government Data, opendata.swiss"
date: "2023-06-23"
output: html_document
---

## Dataset: Recyclinghof

Standorte Recyclinghof

**Zweck**: Lokalisation der Standorte Recyclinghof

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/recyclinghof)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_recyclinghof)

Auto generated R starter code for data set cd3b56f9-718d-43c4-9477-be871ec6c195@stadt-zurich.

## Metadata

- **Publisher** `Datenmanagement, Entsorgung + Recycling Zürich, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['punktdaten', 'vektordaten', 'geodaten', 'geoportal', 'abfall', 'stzh', 'cargo', 'sammelstelle']`
- **Issued** `nan`
- **Metadata_created** `2022-05-10T01:08:32.927490`
- **Metadata_modified** `2023-06-23T01:18:29.789004`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 030ff409-a8e0-4f73-8e07-f8401d900899
# Description              : 
# Issued                   : 2022-05-09T02:58:15.008543
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Recyclinghof?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
