---
title: "Open Government Data, opendata.swiss"
date: "2025-12-27"
output: html_document
---

## Dataset: Katzen - Katzen in Tierheimen

Bestand der registrierten, lebenden Katzen in Tierheimen.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/katzen-katzen-in-tierheimen)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set cats-AnimalCentres@identitas.

## Metadata

- **Publisher.name** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['heimtiere', 'katzen', 'tierheime']`
- **Issued** `2025-11-30T00:00:00`
- **Metadata_created** `2025-07-01T03:21:23.862014`
- **Metadata_modified** `2025-12-23T02:10:47.297550`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 08a28f97-e186-4a21-a961-95a0f3835068
# Description              : 
# Issued                   : 2025-12-22T00:00:00
# Modified                 : None
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://tierstatistik.identitas.ch/data/cats-AnimalCentres.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
