---
title: "Open Government Data, opendata.swiss"
date: "2024-08-15"
output: html_document
---

## Dataset: Mean insect occupancy 1970–2020



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/mean-insect-occupancy-19702020)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/mean-insect-occupancy-1970-2020)

Auto generated R starter code for data set 3dce8afa-5a75-4cf5-8933-9c88308aa8f9@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2022-11-08T09:49:16+00:00`
- **Metadata_created** `2024-05-18T03:25:13.331322`
- **Metadata_modified** `2024-06-29T03:26:26.975975`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 09625a5c-622f-480d-b917-acf56cf4b960
# Description              : 
# Issued                   : 2022-11-08T14:03:20+00:00
# Modified                 : 2022-11-08T15:04:39+00:00
# Rights                   : NonCommercialWithPermission-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/mean-insect-occupancy-1970-2020/resource/28143138-04ae-4a29-bc89-466c68fa084f')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
