---
title: "Open Government Data, opendata.swiss"
date: "2024-12-12"
output: html_document
---

## Dataset: Gemeindefriedhöfe

Standorte der Friedhöfe

**Zweck**: Lokalisierung des Friedhofs.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/gemeindefriedhofe)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_gemeindefriedhoefe)

Auto generated R starter code for data set f763f769-b0e5-4a72-8183-09d4fe88aa02@stadt-zurich.

## Metadata

- **Publisher** `Bestattungs- und Friedhofamt, Bevölkerungsamt, Präsidialdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['stzh', 'geodaten', 'geoportal', 'friedhof', 'punktdaten', 'vektordaten']`
- **Issued** `nan`
- **Metadata_created** `2024-04-13T04:51:46.931270`
- **Metadata_modified** `2024-12-12T03:43:23.460127`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 0bf4b62c-6dd0-4db3-9438-1b2d4ac0c8d2
# Description              : 
# Issued                   : 2023-06-11T03:09:15.537016
# Modified                 : None
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Gemeindefriedhoefe?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
