---
title: "Open Government Data, opendata.swiss"
date: "2024-10-08"
output: html_document
---

## Dataset: Entsorgung Sammelstellen

Sammelstellen nach PLZ

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/entsorgung-sammelstellen2)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_sammelstellen)

Auto generated R starter code for data set b55cc891-10e9-4317-9061-898eac3d4b03@stadt-zurich.

## Metadata

- **Publisher** `Entsorgung + Recycling Zürich, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['entsorgung', 'abfall', 'sachdaten', 'tabellen', 'entsorgungskalender']`
- **Issued** `2012-06-25T00:00:00`
- **Metadata_created** `2023-12-02T02:26:41.648612`
- **Metadata_modified** `2024-10-08T03:48:05.401237`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 0c3c9003-20cf-4902-bfff-ea986e5173c6
# Description              : 
# Issued                   : 2023-01-12T11:55:11.758410
# Modified                 : 2024-07-10T16:15:08.081951
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_sammelstellen/download/entsorgungskalender_sammelstellen_2023.csv')

# Distribution 1
# Package_id               : 0c3c9003-20cf-4902-bfff-ea986e5173c6
# Description              : 
# Issued                   : 2023-01-12T11:55:13.980174
# Modified                 : 2024-07-10T16:15:10.062474
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_sammelstellen/download/entsorgungskalender_sammelstellen_2024.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
