---
title: "Open Government Data, opendata.swiss"
date: "2023-06-15"
output: html_document
---

## Dataset: Landratswahlen 2007 Wahlkreis Gelterkinden

Schlussresultate der regionalen Wahl 'Landratswahlen 2007 Wahlkreis Gelterkinden', 11. Februar 2007, Kanton Basel-Landschaft, aufgeschlüsselt nach Kandidaten und Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/landratswahlen-2007-wahlkreis-gelterkinden)<br>
[Direct link by **Kanton Basel-Landschaft** for dataset](https://abstimmungen.bl.ch/election/landratswahlen-2007-region-4-11-gelterkinden/data)

Auto generated R starter code for data set election-landratswahlen-2007-region-4-11-gelterkinden@kanton-basel-landschaft.

## Metadata

- **Publisher** `Basel-Landschaft`
- **Organization.display_name.de** `Kanton Basel-Landschaft`
- **Organization.url** `https://www.bl.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['wahl', 'regional-district']`
- **Issued** `2007-02-11T00:00:00`
- **Metadata_created** `2023-01-18T01:13:21.598306`
- **Metadata_modified** `2023-06-15T01:49:19.590955`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 14fb891c-6d87-4e78-9354-0147600c00ac
# Description              : 
# Issued                   : 2023-01-17T06:23:36+00:00
# Modified                 : 2023-02-01T11:27:36+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://abstimmungen.bl.ch/election/landratswahlen-2007-region-4-11-gelterkinden/data-csv')

# Distribution 1
# Package_id               : 14fb891c-6d87-4e78-9354-0147600c00ac
# Description              : 
# Issued                   : 2023-01-17T06:23:36+00:00
# Modified                 : 2023-02-01T11:27:36+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://abstimmungen.bl.ch/election/landratswahlen-2007-region-4-11-gelterkinden/data-parties-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

wahlen-abstimmungen@bl.ch | Basel-Landschaft
