---
title: "Open Government Data, opendata.swiss"
date: "2023-03-06"
output: html_document
---

## Dataset: Rinder - Entwicklung nach Fleischigkeit

Anzahl geschlachteter Kühe nach Fleischigkeit gemäss CH-TAX Klassifizierung pro Monat und Jahr. Die Angaben zu CH-TAX wurden von der Proviande zur Verfügung gestellt.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/rinder-entwicklung-nach-fleischigkeit)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set cattle-evolBeefiness@identitas.

## Metadata

- **Publisher** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `Team Tierstatistik Identitas AG`
- **Maintainer_email** `tierstatistik@identitas.ch`
- **Keywords.de** `['rinder', 'ch-tax', 'nutztiere']`
- **Issued** `nan`
- **Metadata_created** `2022-06-07T11:20:35.324104`
- **Metadata_modified** `2023-02-28T01:23:36.466761`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 15af7ca7-d1f3-4598-88db-1e1b78031619
# Description              : 
# Issued                   : None
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://tierstatistik.identitas.ch/data/cattle-evolBeefiness.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
