---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Number of avalanche fatalities per calendar year in Switzerland since 1937



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/number-of-avalanche-fatalities-per-calendar-year-in-switzerland-since-1937)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/avalanche-fatalities-per-calendar-year-since-1936)

Auto generated R starter code for data set b00052bc-11da-4c51-a062-ee1fa1d158d8@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `EnviDat Support`
- **Maintainer_email** `envidat@wsl.ch`
- **Keywords.de** `[]`
- **Issued** `2018-03-07T00:00:00`
- **Metadata_created** `2021-06-15T16:18:22.060437`
- **Metadata_modified** `2023-01-14T01:14:43.422236`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 17bac1a2-49cf-4fdc-b629-c03236295cdf
# Description              : 
# Issued                   : 2018-11-12T00:00:00
# Modified                 : 2021-12-14T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/avalanche-fatalities-per-calendar-year-since-1936/resource/7b223d38-c471-488b-a390-3e1e2a8412a9')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
