---
title: "Open Government Data, opendata.swiss"
date: "2025-12-27"
output: html_document
---

## Dataset: Regenmessung Stadt St.Gallen

Der Datensatz zeigt die Regenmessung an drei Standorten in der Stadt St.Gallen. Die Daten werden stündlich aggregiert.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/regenmessung-stadt-st-gallen)<br>
[Direct link by **Stadt St.Gallen** for dataset](https://daten.stadt.sg.ch/explore/dataset/regenmessung-stadt-st-gallen/)

Auto generated R starter code for data set regenmessung-stadt-st-gallen@stadt-st-gallen.

## Metadata

- **Publisher.name** `nan`
- **Organization.display_name.de** `Stadt St.Gallen`
- **Organization.url** `https://www.stadt.sg.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['real-time', 'offene-sensordaten', 'sensor', 'niederschlag']`
- **Issued** `2024-07-16T00:00:00`
- **Metadata_created** `2024-10-11T05:00:46.591274`
- **Metadata_modified** `2025-12-26T05:02:11.622341`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 1dc2791a-afb9-443c-bd24-afe2e880bcc6
# Description              : Regenmessung Stadt St.Gallen (csv)
# Issued                   : 2024-07-16T00:00:00
# Modified                 : 2025-12-26T04:00:08.521000+00:00
# Rights                   : http://www.opendefinition.org/licenses/cc-by/

df <- read_delim('https://daten.stadt.sg.ch/api/v2/catalog/datasets/regenmessung-stadt-st-gallen/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@stadt.sg.ch | OGD-Koordinationsstelle St.Gallen
