---
title: "Open Government Data, opendata.swiss"
date: "2023-06-17"
output: html_document
---

## Dataset: Zürich Glasfasernetz Leistungsdaten

Leistungsdaten (Up- und Downstream) im Glasfasernetz der Stadt Zürich in Bit pro Sekunde.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/zurich-glasfasernetz-leistungsdaten)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet)

Auto generated R starter code for data set bd1b7dee-a392-477b-a129-88599538f2be@stadt-zurich.

## Metadata

- **Publisher** `Elektrizitätswerk der Stadt Zürich, Departement der Industriellen Betriebe`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['traffic', 'sachdaten', 'glasfasernetz', 'leistungsdaten']`
- **Issued** `2017-10-01T00:00:00`
- **Metadata_created** `2019-07-30T00:41:12.241753`
- **Metadata_modified** `2023-06-17T02:21:58.826871`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 66 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:49:21.498902
# Modified                 : 2023-06-16T19:02:52.288075
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2019-09.csv')

# Distribution 1
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-05-01T05:07:33.228507
# Modified                 : 2023-06-16T19:04:59.182852
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-05.csv')

# Distribution 2
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-11-01T06:59:24.887240
# Modified                 : 2023-06-16T19:04:37.873781
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-11.csv')

# Distribution 3
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-03-01T06:07:05.047590
# Modified                 : 2023-06-16T19:04:53.373278
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-03.csv')

# Distribution 4
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:48:10.954912
# Modified                 : 2023-06-16T19:00:53.161489
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-03.csv')

# Distribution 5
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-11-01T06:19:58.865248
# Modified                 : 2023-06-16T19:03:44.194794
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2020-11.csv')

# Distribution 6
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:46:03.292996
# Modified                 : 2023-06-16T19:02:56.474501
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2019-10.csv')

# Distribution 7
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:48:31.263272
# Modified                 : 2023-06-16T19:02:35.199904
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2019-06.csv')

# Distribution 8
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-10-01T05:04:51.482389
# Modified                 : 2023-06-16T19:04:34.128792
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-10.csv')

# Distribution 9
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2023-03-01T11:34:27.990814
# Modified                 : 2023-06-16T19:05:29.483274
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2023-03.csv')

# Distribution 10
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2023-02-01T07:54:17.673993
# Modified                 : 2023-06-16T19:05:26.449177
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2023-02.csv')

# Distribution 11
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:49:32.690858
# Modified                 : 2023-06-16T19:00:45.980038
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-02.csv')

# Distribution 12
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-09-01T05:10:18.534043
# Modified                 : 2023-06-16T19:05:11.719772
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-09.csv')

# Distribution 13
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-09-01T05:06:24.512716
# Modified                 : 2023-06-16T19:04:30.585812
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-09.csv')

# Distribution 14
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-08-01T05:17:52.560947
# Modified                 : 2023-06-16T19:04:26.426229
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-08.csv')

# Distribution 15
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-02-01T06:08:20.171416
# Modified                 : 2023-06-16T19:04:47.604340
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-02.csv')

# Distribution 16
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-10-01T05:10:38.711324
# Modified                 : 2023-06-16T19:05:15.461953
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-10.csv')

# Distribution 17
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:47:28.622114
# Modified                 : 2023-06-16T19:00:34.614328
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2017-12.csv')

# Distribution 18
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:48:00.492802
# Modified                 : 2023-06-16T19:01:39.343015
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-08.csv')

# Distribution 19
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:46:13.192197
# Modified                 : 2023-06-16T19:03:07.344023
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2020-03.csv')

# Distribution 20
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:50:16.222683
# Modified                 : 2023-06-16T19:02:15.685654
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2019-02.csv')

# Distribution 21
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2023-06-01T06:54:58.974033
# Modified                 : 2023-06-16T19:05:37.355076
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2023-06.csv')

# Distribution 22
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:46:49.123066
# Modified                 : 2023-06-16T19:03:01.704064
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2019-11.csv')

# Distribution 23
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-12-17T07:45:39.326340
# Modified                 : 2023-06-16T19:03:50.087602
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2020-12.csv')

# Distribution 24
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-12-01T06:15:33.551326
# Modified                 : 2023-06-16T19:04:40.957176
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-12.csv')

# Distribution 25
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-01-01T07:45:29.370891
# Modified                 : 2023-06-16T19:03:54.062343
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-01.csv')

# Distribution 26
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:48:53.577213
# Modified                 : 2023-06-16T19:01:11.362880
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-05.csv')

# Distribution 27
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-11-01T07:52:20.602160
# Modified                 : 2023-06-16T19:05:18.821811
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-11.csv')

# Distribution 28
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-06-01T05:14:25.303618
# Modified                 : 2023-06-16T19:04:16.537000
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-06.csv')

# Distribution 29
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-04-01T05:06:49.723408
# Modified                 : 2023-06-16T19:04:56.476295
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-04.csv')

# Distribution 30
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:46:32.255180
# Modified                 : 2023-06-16T19:02:03.916080
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-12.csv')

# Distribution 31
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:46:40.149392
# Modified                 : 2023-06-16T19:01:58.028161
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-11.csv')

# Distribution 32
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:50:06.794324
# Modified                 : 2023-06-16T19:01:01.530846
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-04.csv')

# Distribution 33
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-08-01T05:08:45.234739
# Modified                 : 2023-06-16T19:05:09.115929
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-08.csv')

# Distribution 34
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:47:49.177041
# Modified                 : 2023-06-16T19:00:41.030669
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-01.csv')

# Distribution 35
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-04-01T06:46:26.286638
# Modified                 : 2023-06-16T19:04:07.571001
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-04.csv')

# Distribution 36
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-07-05T14:52:12.362405
# Modified                 : 2023-06-16T19:04:21.726823
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-07.csv')

# Distribution 37
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:47:38.501035
# Modified                 : 2023-06-16T19:02:20.201275
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2019-03.csv')

# Distribution 38
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:48:22.297444
# Modified                 : 2023-06-16T19:03:28.303329
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2020-07.csv')

# Distribution 39
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:49:56.234156
# Modified                 : 2023-06-16T19:02:10.419241
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2019-01.csv')

# Distribution 40
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:46:58.883713
# Modified                 : 2023-06-16T19:02:39.872851
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2019-07.csv')

# Distribution 41
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:50:23.344127
# Modified                 : 2023-06-16T19:02:25.913809
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2019-04.csv')

# Distribution 42
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:50:47.841774
# Modified                 : 2023-06-16T19:03:23.840970
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2020-06.csv')

# Distribution 43
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-03-01T12:47:01.394352
# Modified                 : 2023-06-16T19:04:03.809417
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-03.csv')

# Distribution 44
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2023-01-01T07:55:20.754091
# Modified                 : 2023-06-16T19:05:24.288631
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2023-01.csv')

# Distribution 45
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:46:22.934344
# Modified                 : 2023-06-16T19:00:22.944821
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2017-11.csv')

# Distribution 46
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:48:41.512573
# Modified                 : 2023-06-16T19:03:13.185788
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2020-04.csv')

# Distribution 47
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-06-01T05:10:14.189759
# Modified                 : 2023-06-16T19:05:02.103635
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-06.csv')

# Distribution 48
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-10-01T05:04:51.520096
# Modified                 : 2023-06-16T19:03:40.521428
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2020-10.csv')

# Distribution 49
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-05-06T06:46:35.091535
# Modified                 : 2023-06-16T19:04:12.148591
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-05.csv')

# Distribution 50
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-12-01T07:50:38.308454
# Modified                 : 2023-06-16T19:05:21.581957
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-12.csv')

# Distribution 51
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2023-04-01T06:55:49.792064
# Modified                 : 2023-06-16T19:05:31.611960
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2023-04.csv')

# Distribution 52
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:45:31.429998
# Modified                 : 2023-06-16T19:03:32.794148
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2020-08.csv')

# Distribution 53
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2023-05-03T10:54:30.053956
# Modified                 : 2023-06-16T19:05:33.952163
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2023-05.csv')

# Distribution 54
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2021-02-01T06:52:09.510181
# Modified                 : 2023-06-16T19:03:59.740814
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2021-02.csv')

# Distribution 55
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:47:08.415796
# Modified                 : 2023-06-16T19:03:36.894528
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2020-09.csv')

# Distribution 56
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-07-01T05:10:32.419444
# Modified                 : 2023-06-16T19:05:05.699889
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-07.csv')

# Distribution 57
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2022-01-01T07:47:13.308517
# Modified                 : 2023-06-16T19:04:44.172020
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2022-01.csv')

# Distribution 58
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:45:39.229038
# Modified                 : 2023-06-16T19:03:18.675263
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2020-05.csv')

# Distribution 59
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:45:30.376427
# Modified                 : 2023-06-16T19:00:06.845384
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2017-10.csv')

# Distribution 60
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:49:00.816744
# Modified                 : 2023-06-16T19:01:46.342018
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-09.csv')

# Distribution 61
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:49:09.991435
# Modified                 : 2023-06-16T19:01:52.437919
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-10.csv')

# Distribution 62
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:49:42.953245
# Modified                 : 2023-06-16T19:01:31.279917
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-07.csv')

# Distribution 63
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:47:17.800161
# Modified                 : 2023-06-16T19:02:30.278324
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2019-05.csv')

# Distribution 64
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:50:33.836903
# Modified                 : 2023-06-16T19:02:45.988462
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2019-08.csv')

# Distribution 65
# Package_id               : 22960da1-74ed-4087-9981-6af4688b9bed
# Description              : 
# Issued                   : 2020-09-12T08:45:47.677856
# Modified                 : 2023-06-16T19:01:18.794376
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/ewz_leistungsdaten_zuerinet/download/zuerinet_leistungsdaten_2018-06.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
