---
title: "Open Government Data, opendata.swiss"
date: "2024-12-17"
output: html_document
---

## Dataset: Challenging the sustainability of urban beekeeping: evidence from Swiss cities



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/challenging-the-sustainability-of-urban-beekeeping-evidence-from-swiss-cities)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/challenging-the-sustainability-of-urban-beekeeping-evidence-from-swiss-cities)

Auto generated R starter code for data set 07e84672-abe5-43c2-ae7d-f15d28674db7@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `Marco Moretti`
- **Maintainer_email** `marco.moretti@wsl.ch`
- **Keywords.de** `[]`
- **Issued** `2021-08-16T16:43:17+00:00`
- **Metadata_created** `2022-12-17T01:18:58.836576`
- **Metadata_modified** `2024-12-14T04:38:45.782147`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 3 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 22995f9e-c201-417e-acce-00fad99a0c87
# Description              : 
# Issued                   : 2024-03-26T15:21:15+00:00
# Modified                 : 2024-03-26T16:22:20+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.envidat.ch/dataset/challenging-the-sustainability-of-urban-beekeeping-evidence-from-swiss-cities/resource/29911cdc-420c-4fe5-aa2f-ac5be06a4acf')

# Distribution 1
# Package_id               : 22995f9e-c201-417e-acce-00fad99a0c87
# Description              : 
# Issued                   : 2021-08-16T20:28:02+00:00
# Modified                 : 2024-03-26T16:38:02+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.envidat.ch/dataset/challenging-the-sustainability-of-urban-beekeeping-evidence-from-swiss-cities/resource/67cc3748-cca6-491a-a259-90835d32bde9')

# Distribution 2
# Package_id               : 22995f9e-c201-417e-acce-00fad99a0c87
# Description              : 
# Issued                   : 2021-08-16T20:28:45+00:00
# Modified                 : 2021-08-16T20:28:45+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.envidat.ch/dataset/challenging-the-sustainability-of-urban-beekeeping-evidence-from-swiss-cities/resource/0dfd2c10-a6f8-4ef0-85f6-0fa1d99dad8e')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

marco.moretti@wsl.ch | Marco Moretti
