---
title: "Open Government Data, opendata.swiss"
date: "2024-08-09"
output: html_document
---

## Dataset: Factors slowing down upward shifts of trees’ upper elevation limits



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/factors-slowing-down-upward-shifts-of-trees-upper-elevation-limits)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/factors-slowing-down-upward-shifts-of-trees-upper-elevation-limits)

Auto generated R starter code for data set 50bcbe58-bdbb-4937-aa83-0b983a7ff64d@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2020-06-13T09:16:07+00:00`
- **Metadata_created** `2024-05-18T03:30:18.676130`
- **Metadata_modified** `2024-06-29T03:30:33.771625`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 26577bd5-a65b-44c9-be42-e4e17aa25011
# Description              : 
# Issued                   : 2020-06-13T09:19:44+00:00
# Modified                 : 2020-06-13T09:19:44+00:00
# Rights                   : NonCommercialWithPermission-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/factors-slowing-down-upward-shifts-of-trees-upper-elevation-limits/resource/cbd5e811-0e38-45ed-b00e-fe7a86ed88db')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

daniel.scherrer@wsl.ch | Daniel Scherrer
