---
title: "Open Government Data, opendata.swiss"
date: "2025-03-17"
output: html_document
---

## Dataset: Zivilrechtliche Bevölkerung nach Altersgruppe und Gemeinde ab 2010



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/zivilrechtliche-bevolkerung-nach-altersgruppe-und-gemeinde-ab-2010)<br>
[Direct link by **Amt für Statistik und Daten Freiburg** for dataset](https://opendata.fr.ch/explore/dataset/01_02_pop_legale_par_groupe_d_age/)

Auto generated R starter code for data set 01_02_pop_legale_par_groupe_d_age@ssd.

## Metadata

- **Publisher** `ssd`
- **Organization.display_name.de** `Amt für Statistik und Daten Freiburg`
- **Organization.url** `https://www.fr.ch/deef/ssd`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['zivilrechtliche-bevolkerung', 'gemeinde', 'altersgruppen']`
- **Issued** `2025-01-07T00:00:00`
- **Metadata_created** `2025-01-30T19:23:32.747228`
- **Metadata_modified** `2025-03-16T04:45:31.868839`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 266e8d99-e7a6-47fb-be74-2765677eaa2e
# Description              : Zivilrechtliche Bevölkerung nach Altersgruppe und Gemeinde ab 2010 (csv)
# Issued                   : 2025-01-07T00:00:00
# Modified                 : 2025-01-07T08:07:13.827000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://opendata.fr.ch/api/explore/v2.1/catalog/datasets/01_02_pop_legale_par_groupe_d_age/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@fr.ch | Centre de compétences et de coordination OGD / Kompetenz- und Koordinationszentrum für OGD
