---
title: "Open Government Data, opendata.swiss"
date: "2024-09-07"
output: html_document
---

## Dataset: publi - e bike availability bern

alle 10 Minuten werden die Publibike Daten ab dem OpenJourneyPlaner (OJP) abgefragt:----------------    Aufruf:curl --location --request POST 'https://api.opentransportdata.swiss/ojp2020' |--header 'Content-Type: application/xml' |--header 'Authorization: Bearer 57c5dbbbf1fe4d00010000185bca6120cfa442c3a3d562b2de8fa9a7' |--data-raw '            OJP SDK v1.0      2023-03-03T15:34:33.777Z              2023-03-03T15:34:33.777Z                                                            7.33644                  46.98743                                            7.53302                46.91661                                                              300          poi                                                    amenity                bicycle_rental                                                        ' -o $dateiname

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/publi-e-bike-availability-bern)<br>
[Direct link by **Schweizerische Bundesbahnen SBB** for dataset](https://data.sbb.ch/explore/dataset/publi-e-bike-availability-bern/)

Auto generated R starter code for data set publi-e-bike-availability-bern@schweizerische-bundesbahnen-sbb.

## Metadata

- **Publisher** `schweizerische-bundesbahnen-sbb`
- **Organization.display_name.de** `Schweizerische Bundesbahnen SBB`
- **Organization.url** ``
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2023-03-03T00:00:00`
- **Metadata_created** `2023-03-06T00:40:25.937678`
- **Metadata_modified** `2024-09-07T02:08:21.549200`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 29d403d2-fec5-45d3-90ef-06107343e3f8
# Description              : publi - e bike availability bern (csv)
# Issued                   : 2023-03-03T00:00:00
# Modified                 : 2023-03-03T15:51:40+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://data.sbb.ch/api/v2/catalog/datasets/publi-e-bike-availability-bern/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

geoinformation@bfe.admin.ch | Bundesamt für Energie
