---
title: "Open Government Data, opendata.swiss"
date: "2025-04-07"
output: html_document
---

## Dataset: Haushaltsgrössen nach Gemeinde 1970 - 2000

Anzahl Haushalte nach Grösse in den Gemeinden des Kantons Zug in den Jahren 1970, 1980, 1990 und 2000.


(QUELLE: Bundesamt für Statistik, Volkszählung)

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/haushaltsgrossen-nach-gemeinde-1970-2000)<br>
[Direct link by **Kanton Zug** for dataset]()

Auto generated R starter code for data set ac5b3f9d-829d-4017-9326-f14a57cece1f@kanton-zug.

## Metadata

- **Publisher.name** `nan`
- **Organization.display_name.de** `Kanton Zug`
- **Organization.url** ``
- **Maintainer** `Open Data Zug`
- **Maintainer_email** `opendata@zg.ch`
- **Keywords.de** `['haushalte', 'bevolkerung']`
- **Issued** `2025-02-26T00:00:00`
- **Metadata_created** `2025-02-26T12:58:20.161576`
- **Metadata_modified** `2025-03-18T10:23:17.034469`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 2a11f26c-7a64-4f7b-884d-7a7e971ddcd6
# Description              : 
# Issued                   : None
# Modified                 : None
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.zg.ch/store/1/resource/1904')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zg.ch | Open Data Zug
