---
title: "Open Government Data, opendata.swiss"
date: "2023-05-07"
output: html_document
---

## Dataset: Fundbüro

Standorte der Fundbüros

**Zweck**: Lokalisation der Fundbüros

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/fundburo)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_fundbuero)

Auto generated R starter code for data set 439aaf67-9469-46a8-88a0-6dd339f8b68a@stadt-zurich.

## Metadata

- **Publisher** `Newsroom, Verkehrsbetriebe, Departement der Industriellen Betriebe`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['postauto', 'geodaten', 'buslinien', 'tram', 'vbz', 'fundburo', 'punktdaten', 'offentlicher-verkehr', 'vektordaten', 'bus', 'geoportal', 'tramlinien', 'stzh', 'strassenbahn', 'vbg']`
- **Issued** `nan`
- **Metadata_created** `2022-05-10T01:07:52.545719`
- **Metadata_modified** `2023-05-07T01:17:49.257274`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 2c0f7006-814c-4b95-9e05-4afb709bfde7
# Description              : 
# Issued                   : 2022-05-09T00:00:00
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Fundbuero?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
