---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Fernwärme: Primärenergiemix

Anteil der Primärenergien Kehricht, Holz, Wärmepumpe, Erdgas und Heizöl in MWh pro Jahr

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/fernwarme-primarenergiemix)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/erz_fw_primaerenergiemix)

Auto generated R starter code for data set 5a3372d7-ad36-4776-9df0-03a8c3418a1a@stadt-zurich.

## Metadata

- **Publisher** `Fernwärme, Entsorgung + Recycling Zürich, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['primarenergie', 'fernwarme', 'energie']`
- **Issued** `2021-12-31T00:00:00`
- **Metadata_created** `2022-05-12T01:07:20.670602`
- **Metadata_modified** `2023-01-16T00:51:44.794448`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 2c959f1a-d4fc-4ae1-a2d8-72dd6c5ab63b
# Description              : 
# Issued                   : 2022-05-11T00:00:00
# Modified                 : 2023-01-15T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_fw_primaerenergiemix/download/fw_primaerenergiemix.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
