---
title: "Open Government Data, opendata.swiss"
date: "2024-02-04"
output: html_document
---

## Dataset: Ständeratswahlen 2007

Schlussresultate der kantonalen Wahl 'Ständeratswahlen 2007', 21. Oktober 2007, Kanton Basel-Landschaft, aufgeschlüsselt nach Kandidaten und Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/standeratswahlen-2007)<br>
[Direct link by **Kanton Basel-Landschaft** for dataset](https://abstimmungen.bl.ch/election/staenderatswahlen-2007/data)

Auto generated R starter code for data set election-staenderatswahlen-2007@kanton-basel-landschaft.

## Metadata

- **Publisher** `Basel-Landschaft`
- **Organization.display_name.de** `Kanton Basel-Landschaft`
- **Organization.url** `https://www.baselland.ch`
- **Maintainer** `Basel-Landschaft`
- **Maintainer_email** `wahlen-abstimmungen@bl.ch`
- **Keywords.de** `['wahl', 'kantonal']`
- **Issued** `2007-10-21T00:00:00`
- **Metadata_created** `2023-01-17T01:26:25.784837`
- **Metadata_modified** `2024-02-04T03:14:40.723603`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 3066ec5a-53b5-4b6f-b0ad-db04048fb331
# Description              : 
# Issued                   : 2023-01-16T08:47:07+00:00
# Modified                 : 2023-02-01T11:49:18+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://abstimmungen.bl.ch/election/staenderatswahlen-2007/data-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

wahlen-abstimmungen@bl.ch | Basel-Landschaft
