---
title: "Open Government Data, opendata.swiss"
date: "2026-01-11"
output: html_document
---

## Dataset: Gasverbrauch, in Tausend kWh, pro Halbjahr ab 2021



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/gasverbrauch-in-tausend-kwh-pro-halbjahr-ab-2021)<br>
[Direct link by **Amt für Statistik und Daten Freiburg** for dataset](https://opendata.fr.ch/explore/dataset/08_03_conso_gaz/)

Auto generated R starter code for data set 08_03_conso_gaz@ssd.

## Metadata

- **Publisher.name** `nan`
- **Organization.display_name.de** `Amt für Statistik und Daten Freiburg`
- **Organization.url** `https://www.fr.ch/deef/ssd`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['gasverbrauch']`
- **Issued** `2025-10-20T00:00:00`
- **Metadata_created** `2025-01-30T19:22:16.039834`
- **Metadata_modified** `2026-01-09T01:26:09.495887`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 34c9ae53-9f0b-4908-bcce-4fbe095bcac9
# Description              : Gasverbrauch, in Tausend kWh, pro Halbjahr ab 2021 (csv)
# Issued                   : 2025-10-20T00:00:00
# Modified                 : 2025-10-20T07:49:26.401000+00:00
# Rights                   : http://www.opendefinition.org/licenses/cc-by-sa

df <- read_delim('https://opendata.fr.ch/api/explore/v2.1/catalog/datasets/08_03_conso_gaz/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@fr.ch | Centre de compétences et de coordination OGD / Kompetenz- und Koordinationszentrum für OGD
