---
title: "Open Government Data, opendata.swiss"
date: "2024-06-25"
output: html_document
---

## Dataset: Data from: Estimation of breeding probbability can make monitoring data more revealing: a case study of amphibians



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/data-from-estimation-of-breeding-probbability-can-make-monitoring-data-more-revealing-a-case-st)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/data-amphibian-monitoring)

Auto generated R starter code for data set 67e8cb7a-0fde-4c55-b2b0-eaf0221ec2d8@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2021-03-30T15:56:39+00:00`
- **Metadata_created** `2024-05-18T03:27:47.930767`
- **Metadata_modified** `2024-06-22T03:41:00.283536`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 35159d2e-1855-4cee-ac5c-dc0cb05a8b47
# Description              : 
# Issued                   : 2021-03-30T15:58:07+00:00
# Modified                 : 2021-03-30T15:58:07+00:00
# Rights                   : NonCommercialWithPermission-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/data-amphibian-monitoring/resource/459b81a0-980d-4f98-ac72-0dacbb8ae7f2')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
