---
title: "Open Government Data, opendata.swiss"
date: "2024-06-05"
output: html_document
---

## Dataset: Dynamics of insect natural enemies of bark beetles



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/dynamics-of-insect-natural-enemies-of-bark-beetles)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/dynamics-of-insect-natural-enemies-of-bark-beetles)

Auto generated R starter code for data set a8128568-6978-421e-9abd-1344a2339af0@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2022-04-22T12:02:12+00:00`
- **Metadata_created** `2024-05-18T03:23:57.428845`
- **Metadata_modified** `2024-06-01T03:36:38.777880`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 364710f7-ca73-4a5c-99d7-6953f31b986c
# Description              : 
# Issued                   : 2022-04-22T12:08:44+00:00
# Modified                 : 2022-04-27T14:45:02+00:00
# Rights                   : NonCommercialWithPermission-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/dynamics-of-insect-natural-enemies-of-bark-beetles/resource/fb75f405-9823-4dd6-aa73-f79733d0574f')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

martin.gossner@wsl.ch | Martin Gossner
