---
title: "Open Government Data, opendata.swiss"
date: "2024-12-23"
output: html_document
---

## Dataset: Bruttoprämien (Versicherungssektor)

Bruttoprämien (Versicherungssektor)

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/bruttopramien-versicherungssektor)<br>
[Direct link by **Finanzmarktaufsicht Liechtenstein** for dataset]()

Auto generated R starter code for data set fbe74fa11b6a2eb4face051152d3d3b093f8b58e2a9d757af54591775eaf35a9@finanzmarktaufsicht-fl.

## Metadata

- **Publisher** `Finanzmarktaufsicht Liechtenstein`
- **Organization.display_name.de** `Finanzmarktaufsicht Liechtenstein`
- **Organization.url** `https://www.fma-li.li/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `nan`
- **Metadata_created** `2024-12-16T11:13:46.606471`
- **Metadata_modified** `2024-12-18T10:54:09.323613`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 3a3badbf-99c1-4f88-8eb6-bc0710082df2
# Description              : Bruttoprämien (quartalsweise) des Liechtensteiner Versicherungssektors in CHF
# Issued                   : None
# Modified                 : 2024-11-25T16:32:51.753000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://catalog.opendata.li/store/13/resource/63')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

info@fma-li.li | Finanzmarktaufsicht Liechtenstein
