---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Unternehmenssteuerreformgesetz III

Schlussresultate der eidgenössischen Abstimmung 'Unternehmenssteuerreformgesetz III', 12. Februar 2017, Graubünden - Grischun - Grigioni, aufgeschlüsselt nach Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/unternehmenssteuerreformgesetz-iii)<br>
[Direct link by **Standeskanzlei Graubünden** for dataset](https://abstimmungen.gr.ch/vote/unternehmenssteuerreformgesetz-iii/data)

Auto generated R starter code for data set vote-unternehmenssteuerreformgesetz-iii@standeskanzlei-graubuenden.

## Metadata

- **Publisher** `Standeskanzlei Graubünden`
- **Organization.display_name.de** `Standeskanzlei Graubünden`
- **Organization.url** ``
- **Maintainer** `Standeskanzlei Graubünden`
- **Maintainer_email** `info@gr.ch`
- **Keywords.de** `['national', 'abstimmung']`
- **Issued** `2017-02-12T00:00:00`
- **Metadata_created** `2017-08-22T07:47:39.662145`
- **Metadata_modified** `2023-01-11T18:02:53.772108`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 3cf75313-d5da-46e1-ab55-9dbb939297d3
# Description              : 
# Issued                   : 2017-02-10T00:00:00
# Modified                 : 2022-01-19T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://abstimmungen.gr.ch/vote/unternehmenssteuerreformgesetz-iii/data-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

info@gr.ch | Standeskanzlei Graubünden
