---
title: "Open Government Data, opendata.swiss"
date: "2023-12-14"
output: html_document
---

## Dataset: Hunde - Anzahl Hundehalter:innen pro Kanton

Entwicklung der Anzahl Halterinnen und Halter der registrierten und lebenden Hunde pro Kanton.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/hunde-anzahl-hundehalter-innen-pro-kanton)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set dogs-OwnersCanton@identitas.

## Metadata

- **Publisher** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `Team Tierstatistik Identitas AG`
- **Maintainer_email** `tierstatistik@identitas.ch`
- **Keywords.de** `['eigentumerinnen', 'hunde', 'heimtiere']`
- **Issued** `2023-11-30T00:00:00`
- **Metadata_created** `2023-02-21T01:13:43.395959`
- **Metadata_modified** `2023-12-12T03:34:33.907055`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 401f7c8b-cb86-4778-b810-42374a1f9db3
# Description              : 
# Issued                   : 2023-12-04T00:00:00
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://tierstatistik.identitas.ch/data/dogs-OwnersCanton.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
