---
title: "Open Government Data, opendata.swiss"
date: "2025-06-28"
output: html_document
---

## Dataset: Nuclear microsatellite genotypes of Pinus cembra



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/nuclear-microsatellite-genotypes-of-pinus-cembra)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/nuclear-microsatellite-genotypes-of-pinus-cembra-from-fribourg-and-the-alps)

Auto generated R starter code for data set 71fd7622-d0a6-421d-b6ad-436c2cafebd6@envidat.

## Metadata

- **Publisher.name** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `EnviDat Support`
- **Maintainer_email** `envidat@wsl.ch`
- **Keywords.de** `[]`
- **Issued** `2023-12-07T11:07:50+00:00`
- **Metadata_created** `2024-08-17T04:02:12.548291`
- **Metadata_modified** `2025-06-21T04:43:02.591116`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 4 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 40597424-664d-4668-9655-9fd4cc754b00
# Description              : 
# Issued                   : 2023-12-07T11:17:46+00:00
# Modified                 : 2023-12-07T11:17:46+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://www.envidat.ch/dataset/nuclear-microsatellite-genotypes-of-pinus-cembra-from-fribourg-and-the-alps/resource/8a9e5104-43b4-4e09-a3b8-ceae90131f0d')

# Distribution 1
# Package_id               : 40597424-664d-4668-9655-9fd4cc754b00
# Description              : 
# Issued                   : 2023-12-07T11:17:12+00:00
# Modified                 : 2023-12-07T11:17:12+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://www.envidat.ch/dataset/nuclear-microsatellite-genotypes-of-pinus-cembra-from-fribourg-and-the-alps/resource/80c99523-79be-4f9d-b9e6-f42932bfe941')

# Distribution 2
# Package_id               : 40597424-664d-4668-9655-9fd4cc754b00
# Description              : 
# Issued                   : 2023-12-07T11:14:17+00:00
# Modified                 : 2023-12-07T11:14:17+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://www.envidat.ch/dataset/nuclear-microsatellite-genotypes-of-pinus-cembra-from-fribourg-and-the-alps/resource/5fd90c6f-ee7d-4b34-bfb3-01a457760aa2')

# Distribution 3
# Package_id               : 40597424-664d-4668-9655-9fd4cc754b00
# Description              : 
# Issued                   : 2023-12-07T11:18:00+00:00
# Modified                 : 2023-12-07T11:18:00+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://www.envidat.ch/dataset/nuclear-microsatellite-genotypes-of-pinus-cembra-from-fribourg-and-the-alps/resource/557bdce7-f96a-474f-8302-d1ff00cae2b7')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

felix.gugerli@wsl.ch | Felix Gugerli
