---
title: "Open Government Data, opendata.swiss"
date: "2025-07-11"
output: html_document
---

## Dataset: Katzen - Katzenhalter:innen nach Geschlecht

Anzahl Tierhalterinnen und Tierhalter der registrierten und lebenden Katzen nach Geschlecht.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/katzen-katzenhalter-innen-nach-geschlecht)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set cats-keepersTypes@identitas.

## Metadata

- **Publisher.name** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `Team Tierstatistik Identitas AG`
- **Maintainer_email** `tierstatistik@identitas.ch`
- **Keywords.de** `['tierhalterinnen', 'katzen', 'geschlecht', 'heimtiere']`
- **Issued** `2025-06-30T00:00:00`
- **Metadata_created** `2022-06-07T11:18:46.112053`
- **Metadata_modified** `2025-07-08T04:12:28.833052`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 40f21da1-0b4c-4a52-8174-af1c6d941206
# Description              : 
# Issued                   : 2025-07-07T00:00:00
# Modified                 : None
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://tierstatistik.identitas.ch/data/cats-keepersTypes.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
