---
title: "Open Government Data, opendata.swiss"
date: "2023-08-03"
output: html_document
---

## Dataset: Swiss Line ID Subline



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/swiss-line-id-subline)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/swiss-line-id-subline)

Auto generated R starter code for data set swiss-line-id-subline@oevch.

## Metadata

- **Publisher** `Publisher 1`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2023-08-02T15:43:25.616293`
- **Metadata_created** `2023-08-03T00:42:39.108390`
- **Metadata_modified** `2023-08-03T00:42:39.108407`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 3 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 41a92b76-943e-47d8-801a-10ebd95ca765
# Description              : 
# Issued                   : 2023-08-02T15:44:57.552367
# Modified                 : 2023-08-02T15:44:57.552367
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/8a911ef8-3ffc-4925-a229-db88cdbcdffe/resource/60a62ab3-271f-499e-8a97-09fd71d05dd2/download/full_subline_versions_2023-08-02.csv')

# Distribution 1
# Package_id               : 41a92b76-943e-47d8-801a-10ebd95ca765
# Description              : 
# Issued                   : 2023-08-02T15:44:01.846651
# Modified                 : 2023-08-02T15:44:01.846651
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/8a911ef8-3ffc-4925-a229-db88cdbcdffe/resource/042d8f49-ea91-4dd8-96e8-549dae480a43/download/actual_date_subline_versions_2023-08-02.csv')

# Distribution 2
# Package_id               : 41a92b76-943e-47d8-801a-10ebd95ca765
# Description              : 
# Issued                   : 2023-08-02T15:46:15.773549
# Modified                 : 2023-08-02T15:46:15.773549
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/8a911ef8-3ffc-4925-a229-db88cdbcdffe/resource/6d4d743e-e91f-4c8f-83bb-cabedbc2d6c3/download/future_timetable_subline_versions_2023-08-02.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

contact@example.com | Contact Name
