---
title: "Open Government Data, opendata.swiss"
date: "2026-01-04"
output: html_document
---

## Dataset: Demonstrationen in der Stadt Zürich

Bewilligte und unbewilligte Demonstrationen in der Stadt Zürich

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/demonstrationen)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/sid_stapo_sicherheitsbericht_demonstrationen_od1010)

Auto generated R starter code for data set 6dce121d-cceb-4b1e-9584-d4edfb4f8230@stadt-zurich.

## Metadata

- **Publisher.name** `Stadtpolizei Zürich, Sicherheitsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['kriminalitaet', 'sachdaten', 'sasa', 'stadtpolizei', 'tabelle', 'zeitreihe']`
- **Issued** `nan`
- **Metadata_created** `2025-11-11T02:09:58.373995`
- **Metadata_modified** `2026-01-04T00:51:50.812756`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 425da342-521b-4345-a4cf-65f4838b39f4
# Description              : 
# Issued                   : 2025-10-11T16:04:03.956221
# Modified                 : 2026-03-01T10:30:45.010117
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://data.stadt-zuerich.ch/dataset/sid_stapo_sicherheitsbericht_demonstrationen_od1010/download/RCH101OD1010.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
