---
title: "Open Government Data, opendata.swiss"
date: "2024-07-22"
output: html_document
---

## Dataset: Fatal avalanche accidents in Switzerland since 1936/37



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/fatal-avalanche-accidents-in-switzerland-since-1936-37)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/fatal-avalanche-accidents-in-switzerland-since-1936-37)

Auto generated R starter code for data set 91c9414e-13ce-49c2-9b1e-3ccc9e4a5314@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2023-06-09T14:03:59+00:00`
- **Metadata_created** `2024-05-18T03:23:36.596032`
- **Metadata_modified** `2024-06-29T03:26:10.314968`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 436dd014-a7c1-4b6a-839e-e10f9e4d28b4
# Description              : 
# Issued                   : 2023-06-09T14:07:18+00:00
# Modified                 : 2023-06-09T14:07:20+00:00
# Rights                   : NonCommercialWithPermission-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/fatal-avalanche-accidents-in-switzerland-since-1936-37/resource/3b0f1900-b0a3-4023-896a-f5ae7c36924c')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
