---
title: "Open Government Data, opendata.swiss"
date: "2025-09-06"
output: html_document
---

## Dataset: Kernkapitalquote (Bankensektor)

Verhältnis von hartem Kernkapital (CET1) zu risikogewichteten Aktiva (RWA)

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/kernkapitalquote-bankensektor)<br>
[Direct link by **Finanzmarktaufsicht Liechtenstein** for dataset]()

Auto generated R starter code for data set 963dda88a642a8255ea440d4b712f22bca59aa8b0e735fe34e6c99d6d2cb542c@finanzmarktaufsicht-fl.

## Metadata

- **Publisher.name** `Financial Market Authority Liechtenstein`
- **Organization.display_name.de** `Finanzmarktaufsicht Liechtenstein`
- **Organization.url** `https://www.fma-li.li/`
- **Maintainer** `Finanzmarktaufsicht Liechtenstein`
- **Maintainer_email** `info@fma-li.li`
- **Keywords.de** `[]`
- **Issued** `nan`
- **Metadata_created** `2024-12-16T11:13:47.227132`
- **Metadata_modified** `2025-06-24T08:59:28.602208`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 48967a87-4cef-4208-ac4f-e2a2ceaa1952
# Description              : Kernkapitalquote des Bankensektor
# Issued                   : None
# Modified                 : 2025-06-10T11:30:27.393000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://catalog.opendata.li/store/13/resource/40')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

info@fma-li.li | Finanzmarktaufsicht Liechtenstein
