---
title: "Open Government Data, opendata.swiss"
date: "2024-09-25"
output: html_document
---

## Dataset: Freiräume in der Stadt St.Gallen (Geokoordinaten)

Die Freiräume in der Stadt St.Gallen nach deren Art und deren Bedeutung. Der Datensatz wurde für den Open Data Hack St.Gallen 2021 veröffentlicht. 

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/freiraume-in-der-stadt-st-gallen-geokoordinaten)<br>
[Direct link by **Stadt St.Gallen** for dataset](https://daten.stadt.sg.ch/explore/dataset/freiraume-in-der-stadt-stgallen-geokoordinaten/)

Auto generated R starter code for data set freiraume-in-der-stadt-stgallen-geokoordinaten@stadt-st-gallen.

## Metadata

- **Publisher** `stadt-st-gallen`
- **Organization.display_name.de** `Stadt St.Gallen`
- **Organization.url** `https://www.stadt.sg.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['siedlung', 'grunflachen', 'schule', 'wohnungen', 'kindergarten', 'spielplatz', 'open-data-hack-stgallen']`
- **Issued** `2021-11-05T00:00:00`
- **Metadata_created** `2023-12-21T12:47:09.897427`
- **Metadata_modified** `2024-09-20T05:03:33.044344`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 496b84b0-7db8-4b4c-a24a-f00ebb8bf7b3
# Description              : Freiräume in der Stadt St.Gallen (Geokoordinaten) (csv)
# Issued                   : 2021-11-05T00:00:00
# Modified                 : 2024-08-19T06:19:53.921000+00:00
# Rights                   : NonCommercialAllowed-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://daten.stadt.sg.ch/api/v2/catalog/datasets/freiraume-in-der-stadt-stgallen-geokoordinaten/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@stadt.sg.ch | OGD-Koordinationsstelle St.Gallen
