---
title: "Open Government Data, opendata.swiss"
date: "2024-03-04"
output: html_document
---

## Dataset: Ziegen - Entwicklung der Tierhaltungen nach Kantonen

Anzahl Tierhaltungen mit Ziegen, unterteilt nach Kantonen. 

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/ziegen-entwicklung-der-tierhaltungen-nach-kantonen)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set goats-holdingCanton@identitas.

## Metadata

- **Publisher** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `Team Tierstatistik Identitas AG`
- **Maintainer_email** `tierstatistik@identitas.ch`
- **Keywords.de** `['tierhaltungen', 'nutztiere', 'ziegen']`
- **Issued** `2024-01-31T00:00:00`
- **Metadata_created** `2023-10-17T01:56:34.713881`
- **Metadata_modified** `2024-02-27T05:03:10.784301`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 4b74e710-8fb0-4dbd-87cb-fcd2a3a509ab
# Description              : 
# Issued                   : 2024-02-26T00:00:00
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://tierstatistik.identitas.ch/data/goats-holdingCanton.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
