---
title: "Open Government Data, opendata.swiss"
date: "2025-03-07"
output: html_document
---

## Dataset: Naturschulen

Standorte der Naturschulen in der Stadt Zürich

**Zweck**: Lokalisierung der Naturschulen

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/naturschulen)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_naturschulen)

Auto generated R starter code for data set ae0cc56c-f8e8-433a-aa4e-ef4b6454c840@stadt-zurich.

## Metadata

- **Publisher** `Naturschulen_1, Grün Stadt Zürich, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['naturschule', 'punktdaten', 'stzh', 'vektordaten', 'geoportal', 'geodaten']`
- **Issued** `nan`
- **Metadata_created** `2023-11-07T03:41:51.481731`
- **Metadata_modified** `2025-03-07T03:00:43.363300`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 4cffea1f-5d9a-4347-9661-1b3908de6ed3
# Description              : 
# Issued                   : 2023-06-11T03:29:29.939524
# Modified                 : None
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Naturschulen?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
