---
title: "Open Government Data, opendata.swiss"
date: "2024-04-09"
output: html_document
---

## Dataset: Fernwärme, jährlich abonnierte Leistung


Summe der gemäss den Wärmelieferungsverträgen abonnierten Leistung in MW pro Jahr


[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/fernwarme-jahrlich-abonnierte-leistung)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/erz_fw_abonnierte_leistung)

Auto generated R starter code for data set 99f01b8c-cd03-46f5-b473-4e33a84dbd7c@stadt-zurich.

## Metadata

- **Publisher** `Fernwärme`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['fernwarme-leistung']`
- **Issued** `2021-12-31T00:00:00`
- **Metadata_created** `2022-05-12T01:06:45.929099`
- **Metadata_modified** `2024-04-08T05:46:50.145856`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 4e9d1334-966c-4026-af50-1ec80edddfb8
# Description              : 
# Issued                   : 2022-11-05T14:10:15.458112
# Modified                 : 2024-07-04T16:10:24.757592
# Rights                   : None

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_fw_abonnierte_leistung/download/fw_abonnierte_leistung.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
