---
title: "Open Government Data, opendata.swiss"
date: "2025-02-27"
output: html_document
---

## Dataset: Entsorgungsdaten Karton

Sammeltage der Kartonentsorgung nach PLZ

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/entsorgungsdaten-karton)<br>
[Direct link by **Stadt Z端rich** for dataset](https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_karton)

Auto generated R starter code for data set 74d1af2e-ebee-4011-b149-10b0aed61771@stadt-zurich.

## Metadata

- **Publisher** `Entsorgung + Recycling Z端rich, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Z端rich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['entsorgung', 'kalender', 'tabellen', 'entsorgungsdaten', 'abfall', 'sachdaten', 'entsorgungskalender']`
- **Issued** `2012-06-25T00:00:00`
- **Metadata_created** `2024-12-03T03:49:27.262475`
- **Metadata_modified** `2025-02-27T03:05:07.410408`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 4e9e8692-f25a-4395-9bdd-e3a3b66c5c3a
# Description              : 
# Issued                   : 2024-02-12T07:59:47.343518
# Modified                 : 2025-02-26T16:10:38.052970
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_karton/download/entsorgungskalender_karton_2024.csv')

# Distribution 1
# Package_id               : 4e9e8692-f25a-4395-9bdd-e3a3b66c5c3a
# Description              : 
# Issued                   : 2024-02-12T07:59:48.117672
# Modified                 : 2025-02-26T16:10:39.027482
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_karton/download/entsorgungskalender_karton_2025.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Z端rich
