---
title: "Open Government Data, opendata.swiss"
date: "2024-06-12"
output: html_document
---

## Dataset: Effects of canopy disturbance on Swiss forests



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/effects-of-canopy-disturbance-on-swiss-forests)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/effects-of-canopy-disturbance-on-swiss-forests)

Auto generated R starter code for data set 4e57b948-5e00-4ed3-9047-f528b8857264@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2021-04-20T07:26:19+00:00`
- **Metadata_created** `2024-05-18T03:23:35.542051`
- **Metadata_modified** `2024-06-01T03:29:44.893888`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 4eb8a83d-2859-43e1-961b-12bedafa3dc2
# Description              : 
# Issued                   : 2021-04-20T07:30:59+00:00
# Modified                 : 2021-04-20T07:30:59+00:00
# Rights                   : NonCommercialWithPermission-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/effects-of-canopy-disturbance-on-swiss-forests/resource/0e3fddb2-66e9-44d7-b48b-36d1611dc815')

# Distribution 1
# Package_id               : 4eb8a83d-2859-43e1-961b-12bedafa3dc2
# Description              : 
# Issued                   : 2021-04-20T07:31:59+00:00
# Modified                 : 2021-04-20T07:31:59+00:00
# Rights                   : NonCommercialWithPermission-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/effects-of-canopy-disturbance-on-swiss-forests/resource/83a2907e-051c-41fa-8fbc-3aa62b318792')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

fabrizio.cioldi@wsl.ch | Fabrizio Cioldi
