---
title: "Open Government Data, opendata.swiss"
date: "2024-04-17"
output: html_document
---

## Dataset: Hunde - Entwicklung nach Listenrassen

Bestand der registrierten, lebenden Hunde, mit Angehörigkeit zu einer als potentiell gefährlich eingestuften Rasse im Zeitverlauf. Siehe auch Rasseliste.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/hunde-entwicklung-nach-listenrassen)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set dogs-breedslist@identitas.

## Metadata

- **Publisher** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `Team Tierstatistik Identitas AG`
- **Maintainer_email** `tierstatistik@identitas.ch`
- **Keywords.de** `['rassen', 'populationsentwicklung', 'hunde', 'heimtiere']`
- **Issued** `2024-03-31T00:00:00`
- **Metadata_created** `2023-06-27T02:12:08.647657`
- **Metadata_modified** `2024-04-16T04:59:52.958394`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 4ffc597d-4bdd-4060-b2ae-1fb640d5b60a
# Description              : 
# Issued                   : 2024-04-15T00:00:00
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://tierstatistik.identitas.ch/data/dogs-breedslist.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
