---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Boteninformationen

Enthält Boteninformationen auf Stufe Hausnummer (Briefzustellung).

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/boteninformationen)<br>
[Direct link by **Die Schweizerische Post** for dataset](https://swisspost.opendatasoft.com/explore/dataset/boteninformationen_v2)

Auto generated R starter code for data set boteninformationen_v2@swisspost.

## Metadata

- **Publisher** `Die Schweizerische Post`
- **Organization.display_name.de** `Die Schweizerische Post`
- **Organization.url** `http://www.post.ch`
- **Maintainer** `Kontaktstelle Open Data`
- **Maintainer_email** `opendata@post.ch`
- **Keywords.de** `[]`
- **Issued** `2017-11-22T00:00:00`
- **Metadata_created** `2018-06-05T07:22:50.439048`
- **Metadata_modified** `2022-05-03T14:40:01.149080`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 590549b8-6fc2-48b8-91f6-bb46205299ed
# Description              : 
# Issued                   : 2017-11-22T00:00:00
# Modified                 : 2018-05-07T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://swisspost.opendatasoft.com/api/v2/catalog/datasets/boteninformationen_v2/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@post.ch | Kontaktstelle Open Data
