---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Rinder - Entwicklung nach Nutzungsarten

Prozentuale Aufteilung sowie Gesamtbestand je Nutzungsart (Milchkuh, andere Kuh, nicht definiert) der registrierten, lebenden Rinder. 

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/rinder-entwicklung-nach-nutzungsarten)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set cattle-usage@identitas.

## Metadata

- **Publisher** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['nutztiere', 'nutzungsarten', 'rinder', 'populationsentwicklung']`
- **Issued** `nan`
- **Metadata_created** `2022-06-07T11:22:06.443529`
- **Metadata_modified** `2023-01-10T01:10:49.672976`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5a5ba08a-a66c-4d1e-95fd-5ab99c755129
# Description              : 
# Issued                   : None
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://tierstatistik.identitas.ch/data/cattle-usage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
