---
title: "Open Government Data, opendata.swiss"
date: "2023-12-22"
output: html_document
---

## Dataset: Wohnungen (Gebäude- und Wohnungsregister GWR)

Wohnungen gemäss Gebäude- und Wohnungsregister (GWR)

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/wohnungen-gebaude-und-wohnungsregister-gwr)<br>
[Direct link by **Kanton Basel-Stadt** for dataset](https://data.bs.ch/explore/dataset/100232/)

Auto generated R starter code for data set 100232@kanton-basel-stadt.

## Metadata

- **Publisher** `Statistisches Amt`
- **Organization.display_name.de** `Kanton Basel-Stadt`
- **Organization.url** `https://www.opendata.bs.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['wohnen', 'gebaude', 'wohnung', 'adresse']`
- **Issued** `2022-11-24T00:00:00`
- **Metadata_created** `2023-12-20T11:59:23.755202`
- **Metadata_modified** `2023-12-22T01:42:43.267872`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5a87cb50-9cda-4356-ad09-ac34c9d66afb
# Description              : Wohnungen (Gebäude- und Wohnungsregister GWR) (csv)
# Issued                   : 2022-11-24T00:00:00
# Modified                 : 2023-12-21T02:27:29.375000+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://data.bs.ch/api/v2/catalog/datasets/100232/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@bs.ch | Fachstelle für OGD Basel-Stadt
