---
title: "Open Government Data, opendata.swiss"
date: "2025-03-01"
output: html_document
---

## Dataset: Newsfeed Medienmitteilungen Kanton St.Gallen

Der Datensatz zeigt die Medienmitteilungen des Kantons St.Gallen per Newsfeed. Der Datensatz wird stündlich aktualisiert. Der Link zum RSS-Feed befindet sich unter 'Referenzen'.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/newsfeed-medienmitteilungen-kanton-st-gallen)<br>
[Direct link by **Kanton St. Gallen** for dataset](https://daten.sg.ch/explore/dataset/newsfeed-medienmitteilungen-kanton-stgallen/)

Auto generated R starter code for data set newsfeed-medienmitteilungen-kanton-stgallen@kanton-st-gallen.

## Metadata

- **Publisher** `kanton-st-gallen`
- **Organization.display_name.de** `Kanton St. Gallen`
- **Organization.url** `https://www.sg.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['news', 'real-time', 'medien']`
- **Issued** `2020-06-11T00:00:00`
- **Metadata_created** `2024-03-01T17:11:30.748204`
- **Metadata_modified** `2025-03-01T03:33:28.060151`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5b365677-23d5-4eb2-9e4e-5a18750d9db9
# Description              : Newsfeed Medienmitteilungen Kanton St.Gallen (csv)
# Issued                   : 2020-06-11T00:00:00
# Modified                 : 2025-02-28T23:03:15.073000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://daten.sg.ch/api/v2/catalog/datasets/newsfeed-medienmitteilungen-kanton-stgallen/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@stadt.sg.ch | OGD-Koordinationsstelle St.Gallen
