---
title: "Open Government Data, opendata.swiss"
date: "2026-01-11"
output: html_document
---

## Dataset: Zivilschutzkataster Block

Einteilung und Gliederung der Zivilschutzorganisation in Basel-Stadt und Ausdehnung der einzelnen Zivilschutz-Blockpläne auf Blockebene.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/zivilschutzkataster-block)<br>
[Direct link by **Kanton Basel-Stadt** for dataset](https://data.bs.ch/explore/dataset/100421/)

Auto generated R starter code for data set 100421@kanton-basel-stadt.

## Metadata

- **Publisher.name** `nan`
- **Organization.display_name.de** `Kanton Basel-Stadt`
- **Organization.url** `https://data.bs.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['militar', 'sicherheit']`
- **Issued** `2025-10-22T00:00:00`
- **Metadata_created** `2025-10-23T01:39:31.794139`
- **Metadata_modified** `2026-01-09T00:26:20.137283`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5bc75f2b-e33c-47be-90cf-0a54d0166dc1
# Description              : Zivilschutzkataster Block (csv)
# Issued                   : 2025-10-22T00:00:00
# Modified                 : 2023-09-05T00:00:00+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.bs.ch/api/v2/catalog/datasets/100421/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@bs.ch | Open Data Basel-Stadt
