---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Stadtkreise

Stadtkreise

**Zweck**: Die Stadtkreise dienen den Dienststellen der Stadt Zürich als Grundlage für die verwaltungsinternen Aufgaben.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/stadtkreise1)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_stadtkreise)

Auto generated R starter code for data set d0ca11f9-f312-42de-866c-3e82a79e9d03@stadt-zurich.

## Metadata

- **Publisher** `GIS-Zentrum, Geomatik + Vermessung, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['stadtkreise', 'geoportal', 'quartiere', 'punktdaten', 'vektordaten', 'geodaten', 'gebietseinteilungen', 'polygondaten', 'stzh']`
- **Issued** `nan`
- **Metadata_created** `2022-05-10T01:13:09.057190`
- **Metadata_modified** `2023-01-16T00:55:11.630121`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5bcb49d1-1194-4c0f-adb0-4369e46aef07
# Description              : 
# Issued                   : 2022-05-09T00:00:00
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Stadtkreise?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
