---
title: "Open Government Data, opendata.swiss"
date: "2023-10-09"
output: html_document
---

## Dataset: Kreisschulbehörde

Standorte der Kreisschulbehörde

**Zweck**: Lokalisation der Standorte der Kreisschulbehörde

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/kreisschulbehorde)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_kreisschulbehoerde)

Auto generated R starter code for data set 8bd7d578-89c0-483b-ac68-a7bb6148ffe4@stadt-zurich.

## Metadata

- **Publisher** `Infrastruktur, Schulamt, Schul- und Sportdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['bildung', 'stzh', 'schule', 'geoportal', 'vektordaten', 'geodaten', 'punktdaten']`
- **Issued** `nan`
- **Metadata_created** `2022-05-10T01:11:27.516321`
- **Metadata_modified** `2023-10-09T01:33:55.511015`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5c4c4e70-192a-4583-9bc0-519a608257bf
# Description              : 
# Issued                   : 2022-05-09T02:56:33.341734
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Kreisschulbehoerde?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
