---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Grossratswahlen 2022

Schlussresultate der kantonalen Wahl 'Grossratswahlen 2022', 15. Mai 2022, Graubünden - Grischun - Grigioni, aufgeschlüsselt nach Kandidaten und Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/grossratswahlen-2022)<br>
[Direct link by **Standeskanzlei Graubünden** for dataset](https://abstimmungen.gr.ch/elections/grw2022/data)

Auto generated R starter code for data set election-grw2022@standeskanzlei-graubuenden.

## Metadata

- **Publisher** `Standeskanzlei Graubünden`
- **Organization.display_name.de** `Standeskanzlei Graubünden`
- **Organization.url** ``
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['kantonal', 'wahl']`
- **Issued** `2022-05-15T00:00:00`
- **Metadata_created** `2022-04-06T18:02:31.967894`
- **Metadata_modified** `2023-01-11T18:02:01.618740`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5dc1e4b3-7cd9-410a-9d8f-132aca7f6d28
# Description              : 
# Issued                   : 2022-04-04T00:00:00
# Modified                 : 2022-05-15T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://abstimmungen.gr.ch/elections/grw2022/data-csv')

# Distribution 1
# Package_id               : 5dc1e4b3-7cd9-410a-9d8f-132aca7f6d28
# Description              : 
# Issued                   : 2022-04-04T00:00:00
# Modified                 : 2022-05-15T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://abstimmungen.gr.ch/elections/grw2022/data-parties-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

info@gr.ch | Standeskanzlei Graubünden
