---
title: "Open Government Data, opendata.swiss"
date: "2023-11-09"
output: html_document
---

## Dataset: Ständeratswahlen 2003

Schlussresultate der kantonalen Wahl 'Ständeratswahlen 2003', 19. Oktober 2003, Kanton Basel-Landschaft, aufgeschlüsselt nach Kandidaten und Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/standeratswahlen-2003)<br>
[Direct link by **Kanton Basel-Landschaft** for dataset](https://abstimmungen.bl.ch/election/staenderatswahlen-2003/data)

Auto generated R starter code for data set election-staenderatswahlen-2003@kanton-basel-landschaft.

## Metadata

- **Publisher** `Basel-Landschaft`
- **Organization.display_name.de** `Kanton Basel-Landschaft`
- **Organization.url** `https://www.baselland.ch`
- **Maintainer** `Basel-Landschaft`
- **Maintainer_email** `wahlen-abstimmungen@bl.ch`
- **Keywords.de** `['wahl', 'kantonal']`
- **Issued** `2003-10-19T00:00:00`
- **Metadata_created** `2023-01-17T01:24:46.735035`
- **Metadata_modified** `2023-11-09T02:58:43.744203`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5dee5bc0-5e2f-4781-a74c-6b9350963cbb
# Description              : 
# Issued                   : 2023-01-16T08:44:43+00:00
# Modified                 : 2023-02-01T11:50:06+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://abstimmungen.bl.ch/election/staenderatswahlen-2003/data-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

wahlen-abstimmungen@bl.ch | Basel-Landschaft
