---
title: "Open Government Data, opendata.swiss"
date: "2024-12-08"
output: html_document
---

## Dataset: Maienfeld

Schlussresultate der regionalen Wahl 'Maienfeld', 15. Mai 2022, Graubünden - Grischun - Grigioni, aufgeschlüsselt nach Kandidaten und Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/maienfeld)<br>
[Direct link by **Standeskanzlei Graubünden** for dataset](https://abstimmungen.gr.ch/election/grw-2022-1821/data)

Auto generated R starter code for data set election-grw-2022-1821@standeskanzlei-graubuenden.

## Metadata

- **Publisher** `Standeskanzlei Graubünden`
- **Organization.display_name.de** `Standeskanzlei Graubünden`
- **Organization.url** ``
- **Maintainer** `Standeskanzlei Graubünden`
- **Maintainer_email** `info@gr.ch`
- **Keywords.de** `['wahl', 'regional-regionlabelgr']`
- **Issued** `2022-05-15T00:00:00`
- **Metadata_created** `2022-04-06T18:01:31.782834`
- **Metadata_modified** `2024-10-03T19:11:50.281651`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 5e98acab-da4c-4a0e-9f01-e42caaf9a412
# Description              : 
# Issued                   : 2022-04-04T07:21:54+00:00
# Modified                 : 2024-04-17T05:32:48+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://abstimmungen.gr.ch/election/grw-2022-1821/data-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

info@gr.ch | Standeskanzlei Graubünden
