---
title: "Open Government Data, opendata.swiss"
date: "2024-05-26"
output: html_document
---

## Dataset: Intercantonal Forest Observation Program – Interkantonale Walddauerbeobachtung (WDB)



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/intercantonal-forest-observation-program-interkantonale-walddauerbeobachtung-wdb)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/interkantonale-walddauerbeobachtung-wdb)

Auto generated R starter code for data set 484a5ee9-7c17-4622-b577-4bdb429a9ae2@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2023-01-09T11:53:18+00:00`
- **Metadata_created** `2024-05-18T03:24:14.717276`
- **Metadata_modified** `2024-05-25T03:41:16.046508`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 608118b4-6412-43c2-a937-26e14ab51fc8
# Description              : 
# Issued                   : 2023-01-09T11:54:23+00:00
# Modified                 : 2023-01-09T11:54:23+00:00
# Rights                   : NonCommercialWithPermission-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/interkantonale-walddauerbeobachtung-wdb/resource/7fc6005b-6d01-4142-b843-e659a0f74772')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
