---
title: "Open Government Data, opendata.swiss"
date: "2025-03-12"
output: html_document
---

## Dataset: Cargo- und E-Tram

Standorte Cargo- und E-Tram

**Zweck**: Lokalisation der Standorte Cargo- und E-Tram

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/cargo-und-e-tram2)<br>
[Direct link by **Stadt Z端rich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_cargo__und_e_tram)

Auto generated R starter code for data set 2d66e140-44c1-4af8-959b-bdcec608bb78@stadt-zurich.

## Metadata

- **Publisher** `Datenmanagement, Entsorgung + Recycling Z端rich, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Z端rich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['punktdaten', 'sammelstelle', 'geoportal', 'geodaten', 'cargo', 'abfall', 'stzh']`
- **Issued** `nan`
- **Metadata_created** `2024-01-11T04:56:58.721647`
- **Metadata_modified** `2025-03-12T03:28:32.497859`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 6126cdb2-6d29-4301-ac00-fdfb909d8b53
# Description              : 
# Issued                   : 2023-06-11T03:27:34.923149
# Modified                 : None
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Cargo__und_E_Tram?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Z端rich
