---
title: "Open Government Data, opendata.swiss"
date: "2023-12-24"
output: html_document
---

## Dataset: Liniennetz VBSG Stadt St.Gallen (grafisch)

Darstellung der Liniennetze des öff. Verkehrs

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/liniennetz-vbsg-stadt-st-gallen-grafisch)<br>
[Direct link by **Stadt St.Gallen** for dataset](https://daten.stadt.sg.ch/explore/dataset/ov-vbsg/)

Auto generated R starter code for data set ov-vbsg@stadt-st-gallen.

## Metadata

- **Publisher** `stadt-st-gallen`
- **Organization.display_name.de** `Stadt St.Gallen`
- **Organization.url** `2023-12-21-092646.943088Logostgallenrgb300dpi.jpg`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['bus', 'offentlicher-verkehr', 'linie', 'ov']`
- **Issued** `2023-08-23T04:30:09+00:00`
- **Metadata_created** `2023-12-21T12:46:30.390594`
- **Metadata_modified** `2023-12-21T16:41:43.112965`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 645a5093-d908-4184-86ec-81d132d7073f
# Description              : Liniennetz VBSG Stadt St.Gallen (grafisch) (csv)
# Issued                   : 2023-08-23T04:30:09+00:00
# Modified                 : 2023-08-23T04:30:09+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://daten.stadt.sg.ch/api/v2/catalog/datasets/ov-vbsg/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@stadt.sg.ch | OGD-Koordinationsstelle St.Gallen
