---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Nicht formulierte Spitalinitiative

Schlussresultate der kantonalen Abstimmung 'Nicht formulierte Spitalinitiative', 16. Mai 2004, Kanton Basel-Landschaft, aufgeschlüsselt nach Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/nicht-formulierte-spitalinitiative)<br>
[Direct link by **Kanton Basel-Landschaft** for dataset](https://abstimmungen.bl.ch/vote/nicht-formulierte-spitalinitiative/data)

Auto generated R starter code for data set vote-nicht-formulierte-spitalinitiative@kanton-basel-landschaft.

## Metadata

- **Publisher** `Basel-Landschaft`
- **Organization.display_name.de** `Kanton Basel-Landschaft`
- **Organization.url** `https://www.bl.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['kantonal', 'abstimmung']`
- **Issued** `2004-05-16T00:00:00`
- **Metadata_created** `2022-12-13T15:02:51.996083`
- **Metadata_modified** `2023-01-16T01:11:23.101462`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 69ff7d61-502b-4b68-8a00-2ecd01e34822
# Description              : 
# Issued                   : 2021-09-01T00:00:00
# Modified                 : 2022-01-19T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://abstimmungen.bl.ch/vote/nicht-formulierte-spitalinitiative/data-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

wahlen-abstimmungen@bl.ch | Basel-Landschaft
