---
title: "Open Government Data, opendata.swiss"
date: "2024-09-24"
output: html_document
---

## Dataset: Tree species profiles from Sentinel-2 time series



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/tree-species-profiles-from-sentinel-2-time-series)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/tree-species-profiles-from-sentinel-2-time-series)

Auto generated R starter code for data set 2746ea85-4a12-4354-b94d-bc1806bf24af@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2024-06-11T12:13:19+00:00`
- **Metadata_created** `2024-08-17T04:02:29.877067`
- **Metadata_modified** `2024-09-21T04:05:37.541830`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 29 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:36:31+00:00
# Modified                 : 2024-06-11T14:36:45+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/c6a39077-2b73-489e-8318-131e253cc40f')

# Distribution 1
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:33:23+00:00
# Modified                 : 2024-06-11T14:33:36+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/202363b4-59c9-4b6d-baf8-9eabcd0302f5')

# Distribution 2
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:35:39+00:00
# Modified                 : 2024-06-11T14:35:58+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/46b7f83a-94af-42b0-8926-b4698e952ec7')

# Distribution 3
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:34:25+00:00
# Modified                 : 2024-06-11T14:34:32+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/422f7b32-4c4b-4342-872a-f94d80aa3da9')

# Distribution 4
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:30:05+00:00
# Modified                 : 2024-06-11T14:30:19+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/7d4a9c97-95a3-4664-9338-1f71a4bae056')

# Distribution 5
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:37:39+00:00
# Modified                 : 2024-06-11T14:38:19+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/90c3d891-ccb8-4f3e-9027-196e8ca23db6')

# Distribution 6
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:17:01+00:00
# Modified                 : 2024-06-11T14:19:50+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/f21074d5-e87b-4223-98d9-a05f44ffefae')

# Distribution 7
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:26:35+00:00
# Modified                 : 2024-06-11T14:29:34+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/18ce0d13-7849-4a87-80c4-ff4b05f8abe4')

# Distribution 8
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:34:55+00:00
# Modified                 : 2024-06-11T14:35:17+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/5dfcb505-2b26-46c8-a1a3-6a8f5cd72a3d')

# Distribution 9
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:31:35+00:00
# Modified                 : 2024-06-11T12:31:35+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/748347fc-11aa-4b76-8963-95e06d9f02c0')

# Distribution 10
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:29:39+00:00
# Modified                 : 2024-06-11T14:30:43+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/a47097da-342a-4d06-b313-b296ab5a7872')

# Distribution 11
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:39:31+00:00
# Modified                 : 2024-06-11T14:39:54+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/ded3845c-4915-4ac8-987c-4baaf747dcf6')

# Distribution 12
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:19:56+00:00
# Modified                 : 2024-06-11T14:26:09+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/bc4ed4c2-a517-4adc-b11e-dc6e12bbb6e2')

# Distribution 13
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:38:53+00:00
# Modified                 : 2024-06-11T14:39:08+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/5a3b439d-8190-4b80-990b-30dbd40e573c')

# Distribution 14
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:34:04+00:00
# Modified                 : 2024-06-11T14:34:18+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/120c0f55-0b03-4f62-aeb8-13d0d1b82599')

# Distribution 15
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:33:43+00:00
# Modified                 : 2024-06-11T14:34:00+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/2bcbf5f8-0dc1-4f4f-be1e-1fa71f891916')

# Distribution 16
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:36:55+00:00
# Modified                 : 2024-06-11T14:37:09+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/480510d3-8e5e-4ee2-9212-f3a4d8368705')

# Distribution 17
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:36:02+00:00
# Modified                 : 2024-06-11T14:36:18+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/2acf8fbf-0462-4a92-b574-8c43ea57f8da')

# Distribution 18
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:30:29+00:00
# Modified                 : 2024-06-11T14:30:56+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/609f4479-8ede-4c24-83e7-9aaa029f5759')

# Distribution 19
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:39:14+00:00
# Modified                 : 2024-06-11T14:39:28+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/69234bc5-a96c-45cd-acd2-129267ee0a61')

# Distribution 20
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:37:13+00:00
# Modified                 : 2024-06-11T14:37:23+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/405ac49f-cd5f-4efe-9e2c-3a15dd77ebb7')

# Distribution 21
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:34:38+00:00
# Modified                 : 2024-06-11T14:34:51+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/55705d99-10e2-4a4c-bf61-ea7815c54a6b')

# Distribution 22
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:38:39+00:00
# Modified                 : 2024-06-11T14:38:48+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/272b5859-e4bc-43db-aa95-52ac5cf042a3')

# Distribution 23
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:37:27+00:00
# Modified                 : 2024-06-11T14:37:34+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/09fcb980-d9fb-41a5-a6cf-8c6fb25c1250')

# Distribution 24
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:32:35+00:00
# Modified                 : 2024-06-11T14:33:00+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/a6a91e7d-f1f6-4f1d-a8d3-b9a088fe280b')

# Distribution 25
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:38:25+00:00
# Modified                 : 2024-06-11T14:38:35+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/c6e48054-36e5-4b29-9aff-2b63a2153964')

# Distribution 26
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:39:58+00:00
# Modified                 : 2024-06-11T14:40:05+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/b92d92ad-c31e-4686-bb6a-5d255705571a')

# Distribution 27
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:35:21+00:00
# Modified                 : 2024-06-11T14:35:29+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/5088ebc1-0c60-40cd-8021-8d25c7d68703')

# Distribution 28
# Package_id               : 6e7fb861-377a-4175-b461-87906c6dace8
# Description              : 
# Issued                   : 2024-06-11T12:40:09+00:00
# Modified                 : 2024-06-11T14:40:18+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/tree-species-profiles-from-sentinel-2-time-series/resource/e6f925c6-cf31-4327-a9a9-3dec78e3fe53')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
