---
title: "Open Government Data, opendata.swiss"
date: "2024-01-17"
output: html_document
---

## Dataset: Endverbrauch von Elektrizität nach Gemeinde und Jahr (seit 1990)

Energiestatistik

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/endverbrauch-von-elektrizitat-nach-gemeinde-und-jahr-ab-1990)<br>
[Direct link by **Kanton Basel-Landschaft** for dataset](https://data.bl.ch/explore/dataset/10190/)

Auto generated R starter code for data set 10190@kanton-basel-landschaft.

## Metadata

- **Publisher** `kanton-basel-landschaft`
- **Organization.display_name.de** `Kanton Basel-Landschaft`
- **Organization.url** `https://www.baselland.ch`
- **Maintainer** `Luca Hüsler`
- **Maintainer_email** `luca.huesler@bl.ch`
- **Keywords.de** `['stromverbrauch', 'elektrizitat', 'statistikdaten']`
- **Issued** `2022-09-05T00:00:00`
- **Metadata_created** `2022-12-13T15:07:37.113330`
- **Metadata_modified** `2024-01-17T03:32:42.957335`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 6ebce170-a363-4719-8727-a0d0a43b1a9e
# Description              : Endverbrauch von Elektrizität nach Gemeinde und Jahr (seit 1990) (csv)
# Issued                   : 2022-09-05T00:00:00
# Modified                 : 2024-01-02T10:40:08.198000+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://data.bl.ch/api/v2/catalog/datasets/10190/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

statistik@bl.ch | Fachbereich Raum, Umwelt
