---
title: "Open Government Data, opendata.swiss"
date: "2023-03-31"
output: html_document
---

## Dataset: S3 Prod GO dataset



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/s3-prod-go-dataset)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/s3-prod-go-dataset)

Auto generated R starter code for data set s3-prod-go-dataset@oevch.

## Metadata

- **Publisher** `Publisher 1`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2023-03-30T00:00:00`
- **Metadata_created** `2023-03-31T00:34:12.673935`
- **Metadata_modified** `2023-03-31T00:34:12.673949`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 6fd52dcf-6f8c-4667-8ad0-2991b35b5f4e
# Description              : 
# Issued                   : 2023-03-30T00:00:00
# Modified                 : 2023-03-30T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/2ebced96-0466-479e-9a20-7fe806453fa7/resource/88d05b66-30d1-4bfc-8be6-830fcfaf378f/download/future_timetable_business_organisation_versions_2023-03-30.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

contact@example.com | Contact Name
