---
title: "Open Government Data, opendata.swiss"
date: "2026-01-18"
output: html_document
---

## Dataset: Bevölkerung nach Bevölkerungsdefinition


Wohnbevölkerung der Stadt Zürich nach Bevölkerungsdefinition



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/bevolkerung-nach-bevolkerungsdefinition)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/bev_bestand_jahr_bevdef_od3270)

Auto generated R starter code for data set 0b562ba0-a40b-4209-9a66-bddc37cb179b@stadt-zurich.

## Metadata

- **Publisher.name** `Bevölkerungsamt, Präsidialdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['bevoelkerungsbestand', 'bevoelkerungsdefinition', 'sachdaten', 'sasa', 'tabelle', 'zeitreihe']`
- **Issued** `2025-03-13T00:00:00`
- **Metadata_created** `2025-02-06T03:07:07.063817`
- **Metadata_modified** `2026-01-18T00:32:00.947928`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 7243fb11-95b0-4bb2-b1ee-1f620e062392
# Description              : 
# Issued                   : 2025-05-02T10:03:09.371323
# Modified                 : 2026-01-17T21:05:11.128402
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://data.stadt-zuerich.ch/dataset/bev_bestand_jahr_bevdef_od3270/download/BEV327OD3270.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
