---
title: "Open Government Data, opendata.swiss"
date: "2025-07-11"
output: html_document
---

## Dataset: Begegnungszonen Stadt St.Gallen

Realisierte Begegnungszonen, mit Angabe Gebiet, Nr. und Einführungsdatum

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/begegnungszonen2)<br>
[Direct link by **Stadt St.Gallen** for dataset](https://daten.stadt.sg.ch/explore/dataset/begegnungszonen/)

Auto generated R starter code for data set begegnungszonen@stadt-st-gallen.

## Metadata

- **Publisher.name** `stadt-st-gallen`
- **Organization.display_name.de** `Stadt St.Gallen`
- **Organization.url** `https://www.stadt.sg.ch/`
- **Maintainer** `OGD-Koordinationsstelle St.Gallen`
- **Maintainer_email** `opendata@stadt.sg.ch`
- **Keywords.de** `['passanten', 'fussganger', 'langsamverkehr']`
- **Issued** `2024-01-15T12:31:07+00:00`
- **Metadata_created** `2023-12-21T12:47:57.662325`
- **Metadata_modified** `2025-07-04T06:10:52.035281`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 72a03057-a10d-4e2d-ad23-901dbe3fe2f7
# Description              : Begegnungszonen Stadt St.Gallen (csv)
# Issued                   : 2024-01-15T12:31:07+00:00
# Modified                 : 2024-01-15T12:31:07+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by_ask

df <- read_delim('https://daten.stadt.sg.ch/api/v2/catalog/datasets/begegnungszonen/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@stadt.sg.ch | OGD-Koordinationsstelle St.Gallen
