---
title: "Open Government Data, opendata.swiss"
date: "2024-03-21"
output: html_document
---

## Dataset: R

b

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/bfr-rollstuhlzuganglichkeit)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/bfr-rollstuhl)

Auto generated R starter code for data set bfr-rollstuhl@oevch.

## Metadata

- **Publisher** `INFO+ und BehiG-Bestandsaufnahme`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `SKI Fachstelle BehiG`
- **Maintainer_email** `behig.ski@sbb.ch`
- **Keywords.de** `['verkehrsmittel', 'bus', 'haltestelle', 'rollstuhlfahrer', 'rollstuhlzuganglichkeit', 'proprietar', 'daten', 'haltekante', 'behig', 'zug', 'passagier']`
- **Issued** `2023-06-15T11:01:51.704407`
- **Metadata_created** `2023-12-13T02:42:48.278807`
- **Metadata_modified** `2024-03-21T02:42:49.946386`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 3 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 7313feab-787e-4f7c-891c-985098483bdf
# Description              : 
# Issued                   : 2024-03-20T07:50:56.627608
# Modified                 : 2024-03-20T07:50:56.627608
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/8456c028-4d73-4f2e-8127-9ce8ec889c9d/resource/f55d2803-3f2d-4c12-a0e5-6ee604dfbb7c/download/bfr_kombinationslogik.csv')

# Distribution 1
# Package_id               : 7313feab-787e-4f7c-891c-985098483bdf
# Description              : 
# Issued                   : 2024-03-20T07:50:50.628191
# Modified                 : 2024-03-20T07:50:50.628191
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/8456c028-4d73-4f2e-8127-9ce8ec889c9d/resource/d62adf5d-9e37-4aca-8f62-f543cc6f655c/download/bfr_fahrzeugmapping.csv')

# Distribution 2
# Package_id               : 7313feab-787e-4f7c-891c-985098483bdf
# Description              : 
# Issued                   : 2024-03-20T07:50:53.895302
# Modified                 : 2024-03-20T07:50:53.895302
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/8456c028-4d73-4f2e-8127-9ce8ec889c9d/resource/f6035754-3924-4b28-87ec-e3793e074b3d/download/bfr_haltestellendaten.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

behig.ski@sbb.ch | SKI Fachstelle BehiG
