---
title: "Open Government Data, opendata.swiss"
date: "2024-03-28"
output: html_document
---

## Dataset: d

j

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/bestandsaufnahme-behig)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/prm_data)

Auto generated R starter code for data set prm_data@oevch.

## Metadata

- **Publisher** `BehiG-Bestandsaufnahme`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `DiDok Fachstelle`
- **Maintainer_email** `didok@sbb.ch`
- **Keywords.de** `['verbindung', 'behig', 'billettschalter', 'rollstuhlzuganglichkeit', 'bus', 'passagier', 'ohne-beforderungsleistung', 'parkplatz', 'referenzpunkt', 'dienstleistungsort', 'rollstuhlfahrer', 'toilette', 'informationsschalter', 'daten', 'haltekante', 'haltestelle', 'proprietar', 'zug']`
- **Issued** `2021-03-19T07:15:25.225671`
- **Metadata_created** `2021-03-20T02:58:35.589811`
- **Metadata_modified** `2024-03-28T02:23:33.732883`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 8 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 749efe48-a8f6-4912-807a-6e7f666eeb0a
# Description              : ä
# Issued                   : 2024-03-28T02:50:47.814537
# Modified                 : 2024-03-28T02:50:47.814537
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/a00b9bb8-fb1e-41a3-8280-343c4c0994ce/resource/ac8b5bec-1d36-4b80-babf-d46ced3d0e12/download/prm_ticket_counters.csv')

# Distribution 1
# Package_id               : 749efe48-a8f6-4912-807a-6e7f666eeb0a
# Description              :  
# Issued                   : 2024-03-28T02:50:44.513707
# Modified                 : 2024-03-28T02:50:44.513707
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/a00b9bb8-fb1e-41a3-8280-343c4c0994ce/resource/af7b9ed7-80dd-4154-bed0-25dd4a074d3a/download/prm_reference_points.csv')

# Distribution 2
# Package_id               : 749efe48-a8f6-4912-807a-6e7f666eeb0a
# Description              : H
# Issued                   : 2024-03-28T02:50:46.624159
# Modified                 : 2024-03-28T02:50:46.624159
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/a00b9bb8-fb1e-41a3-8280-343c4c0994ce/resource/cc461233-617d-42b3-99a3-2ed1226705f5/download/prm_stop_places.csv')

# Distribution 3
# Package_id               : 749efe48-a8f6-4912-807a-6e7f666eeb0a
# Description              : ä
# Issued                   : 2024-03-28T02:50:35.184310
# Modified                 : 2024-03-28T02:50:35.184310
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/a00b9bb8-fb1e-41a3-8280-343c4c0994ce/resource/48601694-e635-476c-bbae-5c38d8c12f53/download/prm_connections.csv')

# Distribution 4
# Package_id               : 749efe48-a8f6-4912-807a-6e7f666eeb0a
# Description              : ä
# Issued                   : 2024-03-28T02:50:43.118490
# Modified                 : 2024-03-28T02:50:43.118490
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/a00b9bb8-fb1e-41a3-8280-343c4c0994ce/resource/98b6efdd-bdba-4d7d-8699-20c631938fb8/download/prm_platforms.csv')

# Distribution 5
# Package_id               : 749efe48-a8f6-4912-807a-6e7f666eeb0a
# Description              : h
# Issued                   : 2024-03-28T02:50:49.613207
# Modified                 : 2024-03-28T02:50:49.613207
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/a00b9bb8-fb1e-41a3-8280-343c4c0994ce/resource/7e8f5b11-f817-4c6e-9d56-c771ad41050f/download/prm_toilets.csv')

# Distribution 6
# Package_id               : 749efe48-a8f6-4912-807a-6e7f666eeb0a
# Description              : k
# Issued                   : 2024-03-28T02:50:37.102861
# Modified                 : 2024-03-28T02:50:37.102861
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/a00b9bb8-fb1e-41a3-8280-343c4c0994ce/resource/1b4dbb5b-23ef-4a28-b8a0-4870daae8bf9/download/prm_info_desks.csv')

# Distribution 7
# Package_id               : 749efe48-a8f6-4912-807a-6e7f666eeb0a
# Description              : n
# Issued                   : 2024-03-28T02:50:38.483741
# Modified                 : 2024-03-28T02:50:38.483741
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/a00b9bb8-fb1e-41a3-8280-343c4c0994ce/resource/4f40d9dd-4b12-45d6-94a9-0cc0189c0546/download/prm_parking_lots.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

behig.ski@sbb.ch | SKI Fachstelle BehiG
