---
title: "Open Government Data, opendata.swiss"
date: "2025-12-27"
output: html_document
---

## Dataset: Strassenlänge (ohne Nationalstrassen) nach Gemeinde 2020

Die Beschreibungen der Variablen in der CSV-Datei sind im Anhang verfügbar.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/strassenlange-ohne-nationalstrassen-nach-gemeinde-2020)<br>
[Direct link by **Bundesamt für Statistik BFS** for dataset](https://www.bfs.admin.ch/asset/de/ts-x-11.03.01.07)

Auto generated R starter code for data set 18084201@bundesamt-fur-statistik-bfs.

## Metadata

- **Publisher.name** `nan`
- **Organization.display_name.de** `Bundesamt für Statistik BFS`
- **Organization.url** `https://www.bfs.admin.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['mobilitat-und-verkehr']`
- **Issued** `2020-11-03T07:30:00+00:00`
- **Metadata_created** `2025-10-06T13:59:59.822077`
- **Metadata_modified** `2025-12-26T10:59:27.378107`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 75a0375f-9841-472f-841f-17919cf7b56a
# Description              : Die Beschreibungen der Variablen in der CSV-Datei sind im Anhang verfügbar.
# Issued                   : 2020-11-03T07:30:00+00:00
# Modified                 : 2021-07-02T06:40:54.448000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by_ask

df <- read_delim('https://dam-api.bfs.admin.ch/hub/api/dam/assets/18084204/master')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

auskunftsdienst@bfs.admin.ch | info@bfs.admin.ch
