---
title: "Open Government Data, opendata.swiss"
date: "2023-08-30"
output: html_document
---

## Dataset: Abfuhrtermine

Abfuhrtermine der Stadtreinigung (Tiefbauamt) der Stadt Basel. Siehe auch http://www.tiefbauamt.bs.ch/abfuhrplaene. Abfuhranmeldung unter http://www.tiefbauamt.bs.ch/abfuhranmeldung

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/abfuhrtermine)<br>
[Direct link by **Kanton Basel-Stadt** for dataset](https://data.bs.ch/explore/dataset/100096/)

Auto generated R starter code for data set 100096@kanton-basel-stadt.

## Metadata

- **Publisher** `Tiefbauamt`
- **Organization.display_name.de** `Kanton Basel-Stadt`
- **Organization.url** `https://www.opendata.bs.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['recycling', 'grungut', 'abfall']`
- **Issued** `2020-08-27T00:00:00`
- **Metadata_created** `2023-07-04T12:33:37.167300`
- **Metadata_modified** `2023-08-30T00:27:03.555557`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 75be3356-4987-4d82-8bb1-458de681a7ea
# Description              : Abfuhrtermine (csv)
# Issued                   : 2020-08-27T00:00:00
# Modified                 : 2023-08-29T10:01:56.495000+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://data.bs.ch/api/v2/catalog/datasets/100096/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@bs.ch | Fachstelle für OGD Basel-Stadt
