---
title: "Open Government Data, opendata.swiss"
date: "2026-01-18"
output: html_document
---

## Dataset: Steuerertrag Total [Mio.Fr.]

Nettosteuerertrag im Rechnungsjahr

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/steuerertrag-total-mio-fr)<br>
[Direct link by **Statistisches Amt Kanton Z端rich** for dataset](https://www.zh.ch/de/politik-staat/gemeinden/gemeindeportraet.html)

Auto generated R starter code for data set 196@statistisches-amt-kanton-zuerich.

## Metadata

- **Publisher.name** `Statistisches Amt des Kantons Z端rich`
- **Organization.display_name.de** `Statistisches Amt Kanton Z端rich`
- **Organization.url** `https://www.zh.ch/de/direktion-der-justiz-und-des-innern/statistisches-amt.html`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['gemeindefinanzen', 'kantonzuerich', 'steuerertrag', 'steuern', 'bezirke', 'gemeinden']`
- **Issued** `2016-01-20T00:00:00+01:00`
- **Metadata_created** `2021-01-14T17:27:38.664203`
- **Metadata_modified** `2026-01-18T03:01:57.452409`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 7821b855-f1ad-48d6-a526-b27e06057b16
# Description              : 
# Issued                   : 2016-01-21T00:00:00+01:00
# Modified                 : 2025-08-14T00:00:00+02:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://www.web.statistik.zh.ch/ogd/data/KANTON_ZUERICH_287.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

datashop@statistik.zh.ch | Statistisches Amt des Kantons Z端rich, Data Shop
