---
title: "Open Government Data, opendata.swiss"
date: "2025-07-07"
output: html_document
---

## Dataset: Equiden - Entwicklung der Widerristhöhe

Bestand der registrierten, lebenden Equiden, unterteilt nach Widerristhöhe <>148cm.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/equiden-entwicklung-der-widerristhohe)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set equids-size@identitas.

## Metadata

- **Publisher.name** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `Team Tierstatistik Identitas AG`
- **Maintainer_email** `tierstatistik@identitas.ch`
- **Keywords.de** `['equiden', 'heimtiere', 'nutztiere', 'populationsentwicklung', 'widerrist']`
- **Issued** `2025-05-31T00:00:00`
- **Metadata_created** `2022-06-07T11:20:46.465665`
- **Metadata_modified** `2025-07-01T03:21:42.603510`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 796e8b58-0788-49a6-a4bb-6a39a67184de
# Description              : 
# Issued                   : 2025-06-30T00:00:00
# Modified                 : None
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://tierstatistik.identitas.ch/data/equids-size.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
