---
title: "Open Government Data, opendata.swiss"
date: "2023-12-03"
output: html_document
---

## Dataset: Gemeinschaftszentrum

Gemeinschaftszentrumstandorte in der Stadt Z端rich

**Zweck**: Lokalisierung der Gemeinschaftszentren

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/gemeinschaftszentrum1)<br>
[Direct link by **Stadt Z端rich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_gemeinschaftszentrum)

Auto generated R starter code for data set 1e2848c7-da52-459d-b009-44f3699b40d3@stadt-zurich.

## Metadata

- **Publisher** `Integration & Soziokultur, Departementssekretariat SD, Sozialdepartement`
- **Organization.display_name.de** `Stadt Z端rich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['quartiere', 'geodaten', 'geoportal', 'vektordaten', 'stzh', 'punktdaten']`
- **Issued** `nan`
- **Metadata_created** `2023-11-07T03:42:19.484118`
- **Metadata_modified** `2023-12-03T02:30:26.617480`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 81ecd947-7f13-46df-b188-81aa9959b464
# Description              : 
# Issued                   : 2023-06-11T03:18:01.485312
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Gemeinschaftszentrum?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Z端rich
