---
title: "Open Government Data, opendata.swiss"
date: "2024-08-09"
output: html_document
---

## Dataset: Ist-Daten

Die Ist-Daten enthalten die effektiv gefahrenen Fahrten des letzten bzw. des entsprechenden Tages. Die Ist-Daten sind entweder effektive Ist-Daten oder die letzte Prognose, die das Kundeninformationssystem erhalten hat. Wenn keine Echtzeitinformationen vorhanden waren, so fehlt die entsprechende Fahrt.

Ist-Daten Archiv: https://opentransportdata.swiss/de/ist-daten-archiv/

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/ist-daten-actual-data)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/istdaten)

Auto generated R starter code for data set istdaten@oevch.

## Metadata

- **Publisher** `CUS`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `Specialist office Open Data`
- **Maintainer_email** `opendata@sbb.ch`
- **Keywords.de** `['punktlichkeit', 'verspatung', 'passagier', 'zug', 'proprietar', 'daten', 'ist-daten', 'prognose', 'embag', 'bus']`
- **Issued** `2016-12-01T12:00:00`
- **Metadata_created** `2017-03-02T09:12:01.220199`
- **Metadata_modified** `2024-08-08T02:17:49.990956`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 51 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-07T03:12:46.666236
# Modified                 : 2024-07-07T03:12:46.666236
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/1aef01b4-343e-45d4-a227-4819f2b3ef94/download/2024-07-06_istdaten.csv')

# Distribution 1
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-28T01:16:49.991996
# Modified                 : 2024-07-28T01:16:49.991996
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/b6847fb2-f576-4d23-9186-85158092cf51/download/2024-07-27_istdaten.csv')

# Distribution 2
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-03T03:27:19.154297
# Modified                 : 2024-07-03T03:27:19.154297
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/21798661-91c2-40ff-8ebf-1b4fe6321701/download/2024-07-02_istdaten.csv')

# Distribution 3
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-28T03:52:17.546560
# Modified                 : 2024-06-28T03:52:17.546560
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/757c5fbb-d380-402f-86f4-3bfc0d77f09a/download/2024-06-27_istdaten.csv')

# Distribution 4
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-26T00:57:09.742593
# Modified                 : 2024-07-26T00:57:09.742593
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/66a513ca-102f-4525-9e57-ec22077e0385/download/2024-07-25_istdaten.csv')

# Distribution 5
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-25T01:07:31.852555
# Modified                 : 2024-07-25T01:07:31.852555
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/2f4f7440-6642-4eca-984d-8f00214fd89c/download/2024-07-24_istdaten.csv')

# Distribution 6
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-17T01:47:26.321768
# Modified                 : 2024-07-17T01:47:26.321768
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/10061d82-48cc-4720-bfde-6e14ec2dd953/download/2024-07-16_istdaten.csv')

# Distribution 7
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-23T03:23:14.435205
# Modified                 : 2024-06-23T03:23:14.435205
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/ecca05a7-0866-41ad-909e-af6a80765564/download/2024-06-22_istdaten.csv')

# Distribution 8
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-12T01:03:04.304737
# Modified                 : 2024-07-12T01:03:04.304737
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/437a9ee9-cf3a-4c1b-af53-6fa6ee073437/download/2024-07-11_istdaten.csv')

# Distribution 9
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-04T03:07:17.419700
# Modified                 : 2024-07-04T03:07:17.419700
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/d91fb141-3b45-4406-8d80-ce6f6248977f/download/2024-07-03_istdaten.csv')

# Distribution 10
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-08-03T01:47:11.837980
# Modified                 : 2024-08-03T01:47:11.837980
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/9c41d6b9-2836-4c2e-8e4e-1c9903c2f4da/download/2024-08-02_istdaten.csv')

# Distribution 11
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-08T03:02:17.941552
# Modified                 : 2024-07-08T03:02:17.941552
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/e76b7bc2-891f-497f-b391-64c7b55793b6/download/2024-07-07_istdaten.csv')

# Distribution 12
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-16T01:17:10.125525
# Modified                 : 2024-07-16T01:17:10.125525
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/7eb44ea5-2352-41a6-add6-c65ececc3d7f/download/2024-07-15_istdaten.csv')

# Distribution 13
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-08-06T01:47:17.369881
# Modified                 : 2024-08-06T01:47:17.369881
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/2f238b70-270e-41ec-8eae-b0451a0257ff/download/2024-08-05_istdaten.csv')

# Distribution 14
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-08-07T01:27:17.475218
# Modified                 : 2024-08-07T01:27:17.475218
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/2132fcc4-9e54-440f-92b0-5561e2fbf3dc/download/2024-08-06_istdaten.csv')

# Distribution 15
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-11T03:32:16.779390
# Modified                 : 2024-07-11T03:32:16.779390
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/b67eb463-dc33-41ad-aa74-dd9f491ebf2d/download/2024-07-10_istdaten.csv')

# Distribution 16
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-08-04T01:21:53.018978
# Modified                 : 2024-08-04T01:21:53.018978
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/f9c04093-e688-4401-84d6-e83353baae48/download/2024-08-03_istdaten.csv')

# Distribution 17
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-30T01:17:14.688286
# Modified                 : 2024-07-30T01:17:14.688286
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/858dc54a-7ce9-42dd-9b71-f3db559a4f96/download/2024-07-29_istdaten.csv')

# Distribution 18
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-08-08T00:58:04.906299
# Modified                 : 2024-08-08T00:58:04.906299
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/59fe51c4-0942-4de4-a0fe-2f0f059a05bc/download/2024-08-07_istdaten.csv')

# Distribution 19
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-20T03:47:21.911436
# Modified                 : 2024-06-20T03:47:21.911436
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/80e91b5a-e247-4e9a-abd6-1a1708695aee/download/2024-06-19_istdaten.csv')

# Distribution 20
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-05T02:57:16.187495
# Modified                 : 2024-07-05T02:57:16.187495
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/a4e74acd-4a46-490c-8f68-2ebaeb45c117/download/2024-07-04_istdaten.csv')

# Distribution 21
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-19T03:02:47.149337
# Modified                 : 2024-06-19T03:02:47.149337
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/2fe6884e-5b62-4b9e-9eab-51ec1ca15daf/download/2024-06-18_istdaten.csv')

# Distribution 22
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-15T01:41:25.588076
# Modified                 : 2024-07-15T01:41:25.588076
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/99c61f52-6fec-45bb-a598-468223f3f561/download/2024-07-14_istdaten.csv')

# Distribution 23
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-06T03:37:21.612591
# Modified                 : 2024-07-06T03:37:21.612591
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/ed282bf4-b548-4dc9-9eb8-957a6b5719c5/download/2024-07-05_istdaten.csv')

# Distribution 24
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-08-01T01:22:15.076792
# Modified                 : 2024-08-01T01:22:15.076792
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/f4f0f970-1379-4d9c-a4a4-dc9f44b3fd3f/download/2024-07-31_istdaten.csv')

# Distribution 25
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-14T01:06:54.109388
# Modified                 : 2024-07-14T01:06:54.109388
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/ce145125-c31c-45e6-914e-ed75e6c95de5/download/2024-07-13_istdaten.csv')

# Distribution 26
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-21T03:27:26.423678
# Modified                 : 2024-06-21T03:27:26.423678
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/4058e206-03e0-4454-8b91-0f29332adef4/download/2024-06-20_istdaten.csv')

# Distribution 27
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-09T02:52:26.459480
# Modified                 : 2024-07-09T02:52:26.459480
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/8e8ff24f-7565-4843-86ff-eb305036fd54/download/2024-07-08_istdaten.csv')

# Distribution 28
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-21T01:21:54.665958
# Modified                 : 2024-07-21T01:21:54.665958
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/d0e30f7c-f279-4473-9660-b1c28d64d260/download/2024-07-20_istdaten.csv')

# Distribution 29
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-31T00:57:08.720984
# Modified                 : 2024-07-31T00:57:08.720984
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/c1151af9-1df0-4ea5-a880-0afa678967e1/download/2024-07-30_istdaten.csv')

# Distribution 30
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-30T03:11:52.838625
# Modified                 : 2024-06-30T03:11:52.838625
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/7d9b16a1-dc2b-40e4-8fad-1812d513e26b/download/2024-06-29_istdaten.csv')

# Distribution 31
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-24T01:27:11.665313
# Modified                 : 2024-07-24T01:27:11.665313
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/489718cd-a958-46aa-8d38-ec579e48d433/download/2024-07-23_istdaten.csv')

# Distribution 32
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-08-05T01:01:45.647613
# Modified                 : 2024-08-05T01:01:45.647613
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/0b99ecf5-5d9b-4c92-bf9c-6a8ac090eff9/download/2024-08-04_istdaten.csv')

# Distribution 33
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-25T03:34:26.212804
# Modified                 : 2024-06-25T03:34:26.212804
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/b80bbf96-6886-43da-ad34-3a54195609b6/download/2024-06-24_istdaten.csv')

# Distribution 34
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-02T04:10:58.192670
# Modified                 : 2024-07-02T04:10:58.192670
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/598289b7-7fb8-4fcc-87c7-26a64fbb4894/download/2024-07-01_istdaten.csv')

# Distribution 35
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-22T01:02:05.025687
# Modified                 : 2024-07-22T01:02:05.025687
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/a159f7d1-9366-4507-9b81-eab96b1c148c/download/2024-07-21_istdaten.csv')

# Distribution 36
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-27T01:42:14.962395
# Modified                 : 2024-07-27T01:42:14.962395
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/65129c45-09a5-4e67-9fc6-3c25a5703385/download/2024-07-26_istdaten.csv')

# Distribution 37
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-23T01:52:12.535766
# Modified                 : 2024-07-23T01:52:12.535766
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/668ef168-8d32-45ef-9f42-526dd39308fb/download/2024-07-22_istdaten.csv')

# Distribution 38
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-20T01:52:15.526657
# Modified                 : 2024-07-20T01:52:15.526657
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/533cbd21-e537-44d3-b3f0-54d47ed98558/download/2024-07-19_istdaten.csv')

# Distribution 39
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-13T01:37:17.062543
# Modified                 : 2024-07-13T01:37:17.062543
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/dccd1d0e-2acd-4ffc-967d-aaad89d1e829/download/2024-07-12_istdaten.csv')

# Distribution 40
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-24T02:46:37.970901
# Modified                 : 2024-06-24T02:46:37.970901
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/7f699087-dc40-41d8-b141-705be4b54ee1/download/2024-06-23_istdaten.csv')

# Distribution 41
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-29T00:46:26.063066
# Modified                 : 2024-07-29T00:46:26.063066
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/af53a0d1-2dbd-4ea3-9d47-50736ef90be0/download/2024-07-28_istdaten.csv')

# Distribution 42
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-01T02:51:34.919724
# Modified                 : 2024-07-01T02:51:34.919724
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/10ce9b34-1934-484e-8bb1-c9c12b248637/download/2024-06-30_istdaten.csv')

# Distribution 43
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-19T01:07:13.107906
# Modified                 : 2024-07-19T01:07:13.107906
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/8a990ef7-f25a-4abb-ae80-314923ae3992/download/2024-07-18_istdaten.csv')

# Distribution 44
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-08-02T01:01:58.008426
# Modified                 : 2024-08-02T01:01:58.008426
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/e9de46e0-10a3-4403-a0f8-6de03cc457bf/download/2024-08-01_istdaten.csv')

# Distribution 45
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-26T03:40:43.816456
# Modified                 : 2024-06-26T03:40:43.816456
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/e5ce0a67-3295-4357-aa33-b06a9271dbe5/download/2024-06-25_istdaten.csv')

# Distribution 46
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-18T01:32:26.766293
# Modified                 : 2024-07-18T01:32:26.766293
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/2928f3f0-2dda-4c8e-9400-67b46795fb90/download/2024-07-17_istdaten.csv')

# Distribution 47
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-29T03:54:38.065175
# Modified                 : 2024-06-29T03:54:38.065175
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/1627b254-dedc-469a-a219-adc740c6c72b/download/2024-06-28_istdaten.csv')

# Distribution 48
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-27T03:02:21.098218
# Modified                 : 2024-06-27T03:02:21.098218
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/72afce14-3057-40a5-85e9-cf8966ac2e75/download/2024-06-26_istdaten.csv')

# Distribution 49
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-07-10T03:47:16.919975
# Modified                 : 2024-07-10T03:47:16.919975
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/4172daf6-795f-4aee-898c-5a8a37cadb3c/download/2024-07-09_istdaten.csv')

# Distribution 50
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2024-06-22T03:18:49.922363
# Modified                 : 2024-06-22T03:18:49.922363
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/ab818455-c65f-4a0c-9661-c692852303ae/download/2024-06-21_istdaten.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@sbb.ch |  Open Data Mobilität Schweiz
