---
title: "Open Government Data, opendata.swiss"
date: "2023-12-09"
output: html_document
---

## Dataset: Ist-Daten (actual data)

Die Ist-Daten enthalten die effektiv gefahrenen Fahrten des letzten bzw. des entsprechenden Tages. Die Ist-Daten sind entweder effektive Ist-Daten oder die letzte Prognose, die das Kundeninformationssystem erhalten hat. Wenn keine Echtzeitinformationen vorhanden waren, so fehlt die entsprechende Fahrt.

Ist-Daten Archiv: https://opentransportdata.swiss/de/ist-daten-archiv/

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/ist-daten-actual-data)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/istdaten)

Auto generated R starter code for data set istdaten@oevch.

## Metadata

- **Publisher** `Specialist office Open Data`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `Specialist office Open Data`
- **Maintainer_email** `opendata@sbb.ch`
- **Keywords.de** `['kundeninformation', 'ist-daten', 'punktlichkeit', 'ist', 'verspatung', 'bpuic']`
- **Issued** `2016-12-01T12:00:00`
- **Metadata_created** `2017-03-02T09:12:01.220199`
- **Metadata_modified** `2023-12-09T02:26:55.869148`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 50 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-30T15:24:50.675360
# Modified                 : 2023-10-30T15:24:50.675360
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/e7147dd4-a942-4b77-ab62-f03928014144/download/2023-10-29_istdaten.csv')

# Distribution 1
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-26T02:11:42.325316
# Modified                 : 2023-11-26T02:11:42.325316
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/08929adf-ff92-49d2-aaef-ac5bd9cc7b8c/download/2023-11-25_istdaten.csv')

# Distribution 2
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-12-06T01:51:59.518793
# Modified                 : 2023-12-06T01:51:59.518793
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/2c369dc5-a8c1-47d6-abc5-8aadfeeea7ca/download/2023-12-05_istdaten.csv')

# Distribution 3
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-04T02:22:00.845014
# Modified                 : 2023-11-04T02:22:00.845014
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/1fbf987b-0186-46d6-a1f2-321c981afe90/download/2023-11-03_istdaten.csv')

# Distribution 4
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-18T02:05:00.605659
# Modified                 : 2023-11-18T02:05:00.605659
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/0b814d8a-beb8-4e49-a2d6-aee49f12ec83/download/2023-11-17_istdaten.csv')

# Distribution 5
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-10T02:41:53.907549
# Modified                 : 2023-11-18T01:06:39.309777
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/4e9191b6-a7f4-409a-92fd-3702d3d919bd/download/2023-11-09_istdaten.csv')

# Distribution 6
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-20T01:47:32.180397
# Modified                 : 2023-10-30T03:45:40.442035
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/8ccd407f-a19b-410e-a5b8-592d36adb5c4/download/2023-10-19_istdaten.csv')

# Distribution 7
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-12T02:06:35.899642
# Modified                 : 2023-11-18T01:10:24.572555
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/5b588b38-d698-4101-b549-26fb080ce8da/download/2023-11-11_istdaten.csv')

# Distribution 8
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-22T01:12:01.518646
# Modified                 : 2023-10-30T03:48:43.458570
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/ee90789e-bb4f-42ef-8c4e-76376ae7b583/download/2023-10-21_istdaten.csv')

# Distribution 9
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-29T03:52:47.285848
# Modified                 : 2023-10-30T04:05:25.019972
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/b8db540f-88ed-4abd-8d4f-815e5cf051af/download/2023-10-28_istdaten.csv')

# Distribution 10
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-27T01:56:18.190455
# Modified                 : 2023-11-27T01:56:18.190455
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/5b3cccbf-7322-4b34-980a-71b1acaffe16/download/2023-11-26_istdaten.csv')

# Distribution 11
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-12-07T02:38:13.648823
# Modified                 : 2023-12-07T02:38:13.648823
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/3496b929-25f7-4b13-b406-a5438ff2f54b/download/2023-12-06_istdaten.csv')

# Distribution 12
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-28T00:51:58.422495
# Modified                 : 2023-10-30T04:02:59.128825
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/ed337104-2481-4376-9f57-13821a820e6a/download/2023-10-27_istdaten.csv')

# Distribution 13
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-06T01:46:05.718369
# Modified                 : 2023-11-18T00:56:55.313457
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/aa61b921-c118-49d7-b91f-89e9d7d9f120/download/2023-11-05_istdaten.csv')

# Distribution 14
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-01T01:56:53.468620
# Modified                 : 2023-11-01T01:56:53.468620
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/1431d9b2-370c-4d11-9bf9-9e139665503d/download/2023-10-31_istdaten.csv')

# Distribution 15
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-31T05:37:57.115204
# Modified                 : 2023-10-31T05:37:57.115204
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/c082a674-2e0d-4adc-bbde-0cb528f2291b/download/2023-10-30_istdaten.csv')

# Distribution 16
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-12-01T02:38:31.884753
# Modified                 : 2023-12-01T02:38:31.884753
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/ec49172d-d135-459b-be88-2f1c9a5525ab/download/2023-11-30_istdaten.csv')

# Distribution 17
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-08T02:06:52.742463
# Modified                 : 2023-11-18T01:02:35.176520
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/d4ccc040-eeaa-417c-9d58-23acc83ee95e/download/2023-11-07_istdaten.csv')

# Distribution 18
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-25T02:40:24.349719
# Modified                 : 2023-11-25T02:40:24.349719
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/95e6b739-ee7d-47fb-8af3-212b5301bffa/download/2023-11-24_istdaten.csv')

# Distribution 19
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-20T02:21:14.585012
# Modified                 : 2023-11-20T02:21:14.585012
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/3d82c342-feba-4af2-9f22-8571109e538f/download/2023-11-19_istdaten.csv')

# Distribution 20
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-23T00:51:13.557229
# Modified                 : 2023-10-30T03:50:04.881571
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/1aa18f2f-9d3d-48a7-a95a-a90ee7fbaaf4/download/2023-10-22_istdaten.csv')

# Distribution 21
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-12-08T02:26:57.837970
# Modified                 : 2023-12-08T02:26:57.837970
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/14d40afb-c884-43d5-914f-14d0d3f635b6/download/2023-12-07_istdaten.csv')

# Distribution 22
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-12-03T02:51:34.356586
# Modified                 : 2023-12-03T02:51:34.356586
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/694eda30-462a-4450-bb16-494019481d7b/download/2023-12-02_istdaten.csv')

# Distribution 23
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-12-04T02:26:22.021696
# Modified                 : 2023-12-04T02:26:22.021696
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/93446c7b-569c-4311-891b-b92ec0b85b6f/download/2023-12-03_istdaten.csv')

# Distribution 24
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-26T01:35:05.288415
# Modified                 : 2023-10-30T03:57:20.579544
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/d81ec1df-75db-4d38-a9c7-c3c361091b04/download/2023-10-25_istdaten.csv')

# Distribution 25
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-14T01:51:31.605979
# Modified                 : 2023-11-18T01:13:43.759716
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/cbbf8851-0fff-4941-a232-0cd7a8ac1470/download/2023-11-13_istdaten.csv')

# Distribution 26
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-23T01:46:57.014075
# Modified                 : 2023-11-23T01:46:57.014075
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/e3d0dfc0-8e7c-45a8-a89f-602ed1210ce0/download/2023-11-22_istdaten.csv')

# Distribution 27
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-19T02:46:31.983829
# Modified                 : 2023-11-19T02:46:31.983829
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/5d4b751f-e1a5-46c0-ad0c-9ed0bb37af12/download/2023-11-18_istdaten.csv')

# Distribution 28
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-24T02:36:53.038177
# Modified                 : 2023-11-24T02:36:53.038177
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/00a10a20-221c-473d-8b3a-9d746c2d041b/download/2023-11-23_istdaten.csv')

# Distribution 29
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-29T02:42:01.537078
# Modified                 : 2023-11-29T02:42:01.537078
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/518d980d-6ff5-43b4-9105-40d3053d60ab/download/2023-11-28_istdaten.csv')

# Distribution 30
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-28T02:51:57.605646
# Modified                 : 2023-11-28T02:51:57.605646
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/4ac21d45-c389-4f87-b232-c47cc45d7d43/download/2023-11-27_istdaten.csv')

# Distribution 31
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-12-05T02:08:04.924765
# Modified                 : 2023-12-05T02:08:04.924765
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/b351ac59-a2f1-4339-b319-d6cc255b705a/download/2023-12-04_istdaten.csv')

# Distribution 32
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-30T02:32:10.391531
# Modified                 : 2023-11-30T02:32:10.391531
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/896c6229-6ba5-4581-a894-ed896923b20c/download/2023-11-29_istdaten.csv')

# Distribution 33
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-15T02:36:53.966797
# Modified                 : 2023-11-18T01:15:58.447182
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/4f4b43ee-8435-40a9-954a-02e4c63ce6cb/download/2023-11-14_istdaten.csv')

# Distribution 34
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-03T02:36:54.392005
# Modified                 : 2023-11-03T02:36:54.392005
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/a582f2ad-37a3-47a2-b2f5-b1f5415741ef/download/2023-11-02_istdaten.csv')

# Distribution 35
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-07T02:38:18.777482
# Modified                 : 2023-11-18T01:00:16.271943
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/b7f7f6c7-c5d8-4477-8697-c4e9a3527ecc/download/2023-11-06_istdaten.csv')

# Distribution 36
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-05T02:05:06.827024
# Modified                 : 2023-11-05T02:05:06.827024
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/79d0289e-27c0-4006-806c-4a5ffa181ec3/download/2023-11-04_istdaten.csv')

# Distribution 37
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-12-02T02:37:22.940787
# Modified                 : 2023-12-02T02:37:22.940787
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/30fb9926-39f2-4851-bfd8-ee8097a7cb90/download/2023-12-01_istdaten.csv')

# Distribution 38
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-13T01:56:11.300214
# Modified                 : 2023-11-18T01:11:40.886994
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/96f12a27-0f98-4b96-97bd-1df47383a742/download/2023-11-12_istdaten.csv')

# Distribution 39
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-24T01:43:17.183307
# Modified                 : 2023-10-30T03:52:08.207447
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/0d3b555d-d03c-4df4-9516-87e2113d8ab2/download/2023-10-23_istdaten.csv')

# Distribution 40
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-11T02:16:56.910636
# Modified                 : 2023-11-18T01:08:45.661379
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/c90a50f5-f4b3-4850-8777-b2c3d9429826/download/2023-11-10_istdaten.csv')

# Distribution 41
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-25T01:37:01.331409
# Modified                 : 2023-10-30T03:54:40.411372
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/4112d0c6-dae2-436e-b92a-a565c6a77849/download/2023-10-24_istdaten.csv')

# Distribution 42
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-22T01:56:57.622371
# Modified                 : 2023-11-22T01:56:57.622371
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/463f3a77-abad-4f1b-a9f7-18fd498d2c41/download/2023-11-21_istdaten.csv')

# Distribution 43
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-17T02:36:02.714184
# Modified                 : 2023-11-18T01:20:07.128870
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/5a1fd9fd-eedb-4b28-93cd-dad5e714c383/download/2023-11-16_istdaten.csv')

# Distribution 44
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-02T02:51:47.518368
# Modified                 : 2023-11-02T02:51:47.518368
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/c498b172-9012-4e1f-a73c-cfdb07648e6c/download/2023-11-01_istdaten.csv')

# Distribution 45
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-21T01:32:21.719335
# Modified                 : 2023-10-30T03:47:23.413360
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/39009658-dad0-4dba-b838-688e760262f6/download/2023-10-20_istdaten.csv')

# Distribution 46
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-16T02:22:15.082285
# Modified                 : 2023-11-18T01:18:00.951016
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/0b0475fb-b629-4aad-959f-d514cbd87137/download/2023-11-15_istdaten.csv')

# Distribution 47
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-10-27T01:06:56.687841
# Modified                 : 2023-10-30T04:00:06.340410
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/1e04621c-cd7d-452c-8c13-c253cf747c82/download/2023-10-26_istdaten.csv')

# Distribution 48
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-21T02:11:53.736096
# Modified                 : 2023-11-21T02:11:53.736096
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/1ab30085-67f8-4730-b32e-5cff8693f94a/download/2023-11-20_istdaten.csv')

# Distribution 49
# Package_id               : 81f884db-c99b-4bfd-8cdd-598f75b74285
# Description              : The actual service provided is displayed. The final forecast is used where no actual data are available.
# Issued                   : 2023-11-09T03:56:52.661820
# Modified                 : 2023-11-18T01:04:37.366817
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/0edc74a3-ad4d-486e-8657-f8f3b34a0979/resource/8f90544d-669e-4ca0-b016-6c88879ca829/download/2023-11-08_istdaten.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@sbb.ch | Specialist office Open Data
