---
title: "Open Government Data, opendata.swiss"
date: "2023-07-23"
output: html_document
---

## Dataset: Standorte Mess-Stationen Smart Climate Luftklima

Der Datensatz zeigt die Standorte der Mess-Stationen für den Datensatz «Luftklima Smart Regio Basel».

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/standorte-mess-stationen-smart-climate-luftklima)<br>
[Direct link by **Kanton Basel-Stadt** for dataset](https://data.bs.ch/explore/dataset/100082/)

Auto generated R starter code for data set 100082@kanton-basel-stadt.

## Metadata

- **Publisher** `meteoblue AG`
- **Organization.display_name.de** `Kanton Basel-Stadt`
- **Organization.url** `https://www.opendata.bs.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['smart-city-lab', 'niederschlag', 'regen', 'wetter', 'temperatur', 'sensoren', 'wolf-areal', 'klima']`
- **Issued** `2020-05-12T00:00:00`
- **Metadata_created** `2023-07-05T14:14:19.049495`
- **Metadata_modified** `2023-07-23T00:30:14.532637`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 82d909fe-8059-45c5-8791-2d73b5526e1b
# Description              : Standorte Mess-Stationen Smart Climate Luftklima (csv)
# Issued                   : 2020-05-12T00:00:00
# Modified                 : 2023-07-23T00:10:52.153000+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://data.bs.ch/api/v2/catalog/datasets/100082/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@bs.ch | Fachstelle für OGD Basel-Stadt
