---
title: "Open Government Data, opendata.swiss"
date: "2025-09-15"
output: html_document
---

## Dataset: Dispositionen

Dispositionen von Schutz und Rettung nach Gebiet und Jahr

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/dispositionen)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/sid_srz_od1052_dispositionen_jahr_gebiet)

Auto generated R starter code for data set 7917f0d1-1cea-410e-b77c-195c7acec61c@stadt-zurich.

## Metadata

- **Publisher.name** `Schutz und Rettung, Sicherheitsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['feuerwehr', 'sicherheit', 'rettungsdienste', 'dispositionen', 'zeitreihe', 'tabelle', 'gesundheit', 'sachdaten', 'sasa']`
- **Issued** `2024-08-31T00:00:00`
- **Metadata_created** `2025-05-03T05:21:54.437830`
- **Metadata_modified** `2025-09-14T03:11:01.653962`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 8328f053-d2cb-47dc-a4bd-8af3651ccfbe
# Description              : 
# Issued                   : 2024-01-12T11:17:21.332754
# Modified                 : 2025-09-13T10:51:29.621431
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://data.stadt-zuerich.ch/dataset/sid_srz_od1052_dispositionen_jahr_gebiet/download/GES105OD1052.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
