---
title: "Open Government Data, opendata.swiss"
date: "2024-07-26"
output: html_document
---

## Dataset: Aménagement cyclable



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/amenagement-cyclable)<br>
[Direct link by **** for dataset](https://viageo.ch/md/eb867568-c511-4304-b902-1bbfbd0d8806)

Auto generated R starter code for data set eb867568-c511-4304-b902-1bbfbd0d8806@lausanne.

## Metadata

- **Publisher** `Lausanne`
- **Organization.display_name.de** ``
- **Organization.url** `https://www.lausanne.ch/`
- **Maintainer** `Frédéric Ducry, Responsable de diffusion`
- **Maintainer_email** `frederic.ducry@lausanne.ch`
- **Keywords.de** `[]`
- **Issued** `2016-06-20T00:00:00`
- **Metadata_created** `2023-06-12T15:12:03.034351`
- **Metadata_modified** `2024-07-26T03:25:46.521386`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 8586ae53-6d7d-41f3-935f-dc093f085c96
# Description              : 
# Issued                   : 2016-06-20T00:00:00
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://viageo.ch/md/eb867568-c511-4304-b902-1bbfbd0d8806#downloadAction')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

map@lausanne.ch | Service de la mobilité et de l’aménagement des espaces publics Ville de Lausanne, Gestionnaire de la donnée
