---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Rinder - Sömmerung Geburten nach Kantonen

Geburten der Rinder während der Sömmerung im Sömmerungsgebiet nach Geburtskantonen im Zeitverlauf.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/rinder-sommerung-geburten-nach-kantonen)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set cattle-summering-births-canton@identitas.

## Metadata

- **Publisher** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['rinder', 'kanton', 'nutztiere', 'sommerung']`
- **Issued** `nan`
- **Metadata_created** `2022-10-25T01:34:19.245190`
- **Metadata_modified** `2023-01-10T01:09:38.875270`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 870508c6-2655-467f-8680-826dfff01176
# Description              : 
# Issued                   : None
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://tierstatistik.identitas.ch/data/cattle-summering-births-canton.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
