---
title: "Open Government Data, opendata.swiss"
date: "2024-09-29"
output: html_document
---

## Dataset: Brandschutzwand



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/brandschutzwand)<br>
[Direct link by **Schweizerische Bundesbahnen SBB** for dataset](https://data.sbb.ch/explore/dataset/brandschutzwand/)

Auto generated R starter code for data set brandschutzwand@schweizerische-bundesbahnen-sbb.

## Metadata

- **Publisher** `schweizerische-bundesbahnen-sbb`
- **Organization.display_name.de** `Schweizerische Bundesbahnen SBB`
- **Organization.url** ``
- **Maintainer** `Ansprechstelle für Daten`
- **Maintainer_email** `data@sbb.ch`
- **Keywords.de** `[]`
- **Issued** `2021-09-14T08:29:01+00:00`
- **Metadata_created** `2021-09-17T00:52:39.682537`
- **Metadata_modified** `2024-09-29T02:02:20.035886`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 88e711a4-8fd0-4432-91e5-520d5c034f33
# Description              : 
# Issued                   : 2021-09-14T08:29:01+00:00
# Modified                 : 2021-09-14T08:29:01+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://data.sbb.ch/api/v2/catalog/datasets/brandschutzwand/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

data@sbb.ch | Ansprechstelle für Daten
