---
title: "Open Government Data, opendata.swiss"
date: "2023-02-14"
output: html_document
---

## Dataset: Unternehmensschliessungen

Die Beschreibungen der Variablen in der CSV-Datei sind im Anhang verf端gbar.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/unternehmensschliessungen4)<br>
[Direct link by **Bundesamt f端r Statistik BFS** for dataset](https://www.bfs.admin.ch/asset/de/ts-x-06.02.02.01.05)

Auto generated R starter code for data set 23705252@bundesamt-fur-statistik-bfs.

## Metadata

- **Publisher** `BFS/OFS`
- **Organization.display_name.de** `Bundesamt f端r Statistik BFS`
- **Organization.url** `https://www.bfs.admin.ch`
- **Maintainer** `info@bfs.admin.ch`
- **Maintainer_email** `auskunftsdienst@bfs.admin.ch`
- **Keywords.de** `['tabelle', 'industrie-und-dienstleistungen', 'statistik-der-unternehmensdemografie', 'vollerhebung']`
- **Issued** `2022-12-07T00:00:00`
- **Metadata_created** `2022-12-07T09:36:17.223799`
- **Metadata_modified** `2023-02-13T10:59:26.314442`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 89349bea-fb85-4f00-9e98-2158a62d04d0
# Description              : Die Beschreibungen der Variablen in der CSV-Datei sind im Anhang verf端gbar.
# Issued                   : 2022-12-07T00:00:00
# Modified                 : 2023-01-25T00:00:00
# Rights                   : NonCommercialAllowed-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.bfs.admin.ch/bfsstatic/dam/assets/23705255/master')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

auskunftsdienst@bfs.admin.ch | info@bfs.admin.ch
