---
title: "Open Government Data, opendata.swiss"
date: "2025-04-19"
output: html_document
---

## Dataset: Nationalratswahlen 2023: Panaschierstatistik (Kandidierende), nach Kantonen



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/nationalratswahlen-2023-panaschierstatistik-kandidierende-nach-kantonen)<br>
[Direct link by **Bundesamt für Statistik BFS** for dataset](https://www.bfs.admin.ch/asset/de/su-d-17.02.02.06.03.za.2023.k)

Auto generated R starter code for data set 32011752@bundesamt-fur-statistik-bfs.

## Metadata

- **Publisher.name** `BFS/OFS`
- **Organization.display_name.de** `Bundesamt für Statistik BFS`
- **Organization.url** `https://www.bfs.admin.ch`
- **Maintainer** `info@bfs.admin.ch`
- **Maintainer_email** `auskunftsdienst@bfs.admin.ch`
- **Keywords.de** `['politik']`
- **Issued** `2024-05-24T14:51:00+00:00`
- **Metadata_created** `2024-05-27T09:35:24.457300`
- **Metadata_modified** `2025-04-18T10:17:58.253644`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 897e4f5d-ab71-4654-81e4-c411311d69a6
# Description              : 
# Issued                   : 2024-05-24T14:51:00+00:00
# Modified                 : 2024-07-05T09:36:38.682000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by_ask

df <- read_delim('https://dam-api.bfs.admin.ch/hub/api/dam/assets/32011766/master')

# Distribution 1
# Package_id               : 897e4f5d-ab71-4654-81e4-c411311d69a6
# Description              : 
# Issued                   : 2024-05-24T14:51:00+00:00
# Modified                 : 2024-07-05T09:36:38.650000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by_ask

df <- read_delim('https://dam-api.bfs.admin.ch/hub/api/dam/assets/32011761/master')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

auskunftsdienst@bfs.admin.ch | info@bfs.admin.ch
