---
title: "Open Government Data, opendata.swiss"
date: "2023-12-12"
output: html_document
---

## Dataset: Swiss Line Directory (SLNID) - Line

Rohdaten aus dem Schweizer Linienverzeichnis. 
Dieser Datensatz enthält die Linien. Für die Sublinien s. https://opentransportdata.swiss/dataset/slnid-subline. 

Die Daten werden auch als API publiziert: https://developer.sbb.ch/apis/atlas/information (Lines, Sublines)

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/swiss-line-directory-slnid-line)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/slnid-line)

Auto generated R starter code for data set slnid-line@oevch.

## Metadata

- **Publisher** `Geschäftsstelle SKI`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['linien', 'slnid', 'linienverzeichnis', 'swiss-line-directory']`
- **Issued** `2023-12-11T15:22:26.089436`
- **Metadata_created** `2023-12-12T02:17:23.737581`
- **Metadata_modified** `2023-12-12T02:17:23.737590`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 3 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 8edb656a-93dd-47ac-8f4f-1299b2342311
# Description              : 
# Issued                   : 2023-12-11T15:24:59.333499
# Modified                 : 2023-12-11T15:24:59.333499
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/a9d650b8-9776-4194-8f59-4e8b1c6d71d4/resource/14b2ed71-0807-4ff0-a043-cbd1b15591ee/download/future_timetable_line_versions_2023-12-11.csv')

# Distribution 1
# Package_id               : 8edb656a-93dd-47ac-8f4f-1299b2342311
# Description              : 
# Issued                   : 2023-12-11T15:23:54.239585
# Modified                 : 2023-12-11T15:23:54.239585
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/a9d650b8-9776-4194-8f59-4e8b1c6d71d4/resource/4b3df62b-25e6-4bb9-99c7-6b617ff7fae7/download/full_line_versions_2023-12-11.csv')

# Distribution 2
# Package_id               : 8edb656a-93dd-47ac-8f4f-1299b2342311
# Description              : 
# Issued                   : 2023-12-11T15:23:03.318691
# Modified                 : 2023-12-11T15:23:03.318691
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/de/dataset/a9d650b8-9776-4194-8f59-4e8b1c6d71d4/resource/b3216987-187b-48cd-b3ca-d43445a1dccf/download/actual_date_line_versions_2023-12-11.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

atlas@sbb.ch | Fachstelle atlas
