---
title: "Open Government Data, opendata.swiss"
date: "2024-12-28"
output: html_document
---

## Dataset: Adressen der Sonderschulen und Schulheime (Juni 2024)

Liste der Tagessonderschulen und Schulheime

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/adressen-der-sonderschulen-und-schulheime-juni-2024)<br>
[Direct link by **Kanton Basel-Landschaft** for dataset](https://data.bl.ch/explore/dataset/11200/)

Auto generated R starter code for data set 11200@kanton-basel-landschaft.

## Metadata

- **Publisher** `kanton-basel-landschaft`
- **Organization.display_name.de** `Kanton Basel-Landschaft`
- **Organization.url** `https://www.baselland.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['adressdaten', 'heim', 'sonderpadagogik', 'telefonnummer', 'sonderschule', 'e-mail-adresse']`
- **Issued** `2024-06-06T00:00:00`
- **Metadata_created** `2024-06-07T03:22:22.402093`
- **Metadata_modified** `2024-12-27T03:53:24.208518`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 8f7f4e70-27dc-4a28-b66e-23cecd328562
# Description              : Adressen der Sonderschulen und Schulheime (Juni 2024) (csv)
# Issued                   : 2024-06-06T00:00:00
# Modified                 : 2024-10-15T13:23:36.499000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.bl.ch/api/v2/catalog/datasets/11200/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

avs@bl.ch  | Michael Schiegg
