---
title: "Open Government Data, opendata.swiss"
date: "2025-07-31"
output: html_document
---

## Dataset: Schafe - Entwicklung nach landwirtschaft-lichen Zonen

Bestand der registrierten, lebenden Schafe, unterteilt nach  landwirtschaftlichen Zonen  im Zeitverlauf.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/schafe-entwicklung-nach-landwirtschaft-lichen-zonen)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set sheep-agriculturalZones@identitas.

## Metadata

- **Publisher.name** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `Team Tierstatistik Identitas AG`
- **Maintainer_email** `tierstatistik@identitas.ch`
- **Keywords.de** `['schafe', 'populationsentwicklung', 'nutztiere', 'landwirtschaftliche-zonen']`
- **Issued** `2025-06-30T00:00:00`
- **Metadata_created** `2022-10-25T01:35:29.370830`
- **Metadata_modified** `2025-07-29T03:19:09.374775`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 8fd5a973-55f6-4aa0-ad00-cf4f657fde41
# Description              : 
# Issued                   : 2025-07-28T00:00:00
# Modified                 : None
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://tierstatistik.identitas.ch/data/sheep-agriculturalZones.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
