---
title: "Open Government Data, opendata.swiss"
date: "2024-10-30"
output: html_document
---

## Dataset: Dienstleistungen

Standorte von städtischen Dienstleistungen

**Zweck**: Auffinden und Darstellen der Daten im Kontaktparagraphen der städtischen Internetseiten sowie im Stadtplan.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/dienstleistungen)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_dienstleistungen)

Auto generated R starter code for data set 5bda2ced-f37a-4cae-9f7d-35a6bbec8ccb@stadt-zurich.

## Metadata

- **Publisher** `GIS-Zentrum, Geomatik + Vermessung, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['geodaten', 'vektordaten', 'dienstleistung', 'stzh', 'geoportal', 'punktdaten']`
- **Issued** `nan`
- **Metadata_created** `2023-11-07T03:43:45.067424`
- **Metadata_modified** `2024-10-30T02:58:43.053740`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 8fdbaaab-2733-4110-88b6-128edfbb9cbc
# Description              : 
# Issued                   : 2023-06-11T03:21:14.839434
# Modified                 : None
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Dienstleistungen?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
