---
title: "Open Government Data, opendata.swiss"
date: "2023-11-17"
output: html_document
---

## Dataset: (Beta) Fahrplan 2023 (NeTEx)

Der Fahrplan enthält die grundlegenden topologischen, sowie die zeitlichen Element, die eine Fahrplandarstellung und -auskunft ermöglichen. Dies ist ein erster Testdatensatz in NeTEx. Er umfasst den westlichen Teil der Schweiz. 


[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/fahrplan-2023-netex-beta)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/timetable-2023-netex)

Auto generated R starter code for data set timetable-2023-netex@oevch.

## Metadata

- **Publisher** `Publisher 1`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `Fachstelle Open-Data-Plattform Mobilität Schweiz`
- **Maintainer_email** `opendata@sbb.ch`
- **Keywords.de** `[]`
- **Issued** `2023-01-05T10:39:20.698143`
- **Metadata_created** `2023-01-06T00:27:31.059334`
- **Metadata_modified** `2023-11-17T01:55:07.874307`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 8 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 90ee5386-002a-46d7-8a96-6c6f9bec88b2
# Description              : 
# Issued                   : 2023-11-10T00:40:07.744427
# Modified                 : 2023-11-10T00:40:07.744427
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/bf6061ef-829e-42fd-9b98-8990bfbaf03f/resource/71ba39d5-6e35-454e-beaa-8d56c12e44ca/download/prod_netex_tt_1.10_che_ski_2023_oev-schweiz_readme_1_1_202311090811.csv')

# Distribution 1
# Package_id               : 90ee5386-002a-46d7-8a96-6c6f9bec88b2
# Description              : 
# Issued                   : 2023-11-16T01:05:07.357551
# Modified                 : 2023-11-16T01:05:07.357551
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/bf6061ef-829e-42fd-9b98-8990bfbaf03f/resource/8d5a7da5-88b1-4fac-9338-b87d90d765c0/download/prod_netex_tt_1.10_che_ski_2023_oev-schweiz_readme_1_1_202311150611.csv')

# Distribution 2
# Package_id               : 90ee5386-002a-46d7-8a96-6c6f9bec88b2
# Description              : 
# Issued                   : 2023-09-06T20:35:06.876340
# Modified                 : 2023-09-06T20:35:06.876340
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/bf6061ef-829e-42fd-9b98-8990bfbaf03f/resource/9602ed95-fdc0-4b3d-8f2b-3b99853f5630/download/prod_netex_tt_1.10_che_ski_2023_oev-schweiz_readme_1_1_202309060609.csv')

# Distribution 3
# Package_id               : 90ee5386-002a-46d7-8a96-6c6f9bec88b2
# Description              : 
# Issued                   : 2023-09-13T21:05:07.183724
# Modified                 : 2023-10-25T23:45:07.430509
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/bf6061ef-829e-42fd-9b98-8990bfbaf03f/resource/ccced87e-8592-47e8-acd3-5525b2d0ef6d/download/prod_netex_tt_1.10_che_ski_2023_oev-schweiz_readme_1_1_202309130609.csv')

# Distribution 4
# Package_id               : 90ee5386-002a-46d7-8a96-6c6f9bec88b2
# Description              : 
# Issued                   : 2023-10-25T23:45:10.722543
# Modified                 : 2023-10-25T23:45:10.722543
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/bf6061ef-829e-42fd-9b98-8990bfbaf03f/resource/dc6a52b6-1340-4164-b20f-73f424f57b47/download/prod_netex_tt_1.10_che_ski_2023_oev-schweiz_readme_1_1_202310251110.csv')

# Distribution 5
# Package_id               : 90ee5386-002a-46d7-8a96-6c6f9bec88b2
# Description              : 
# Issued                   : 2023-08-25T19:45:07.155276
# Modified                 : 2023-08-25T19:45:07.155276
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/bf6061ef-829e-42fd-9b98-8990bfbaf03f/resource/f437d564-769f-4d68-8592-ff888ad80e9b/download/prod_netex_tt_1.10_che_ski_2023_oev-schweiz_readme_1_1_202308230608.csv')

# Distribution 6
# Package_id               : 90ee5386-002a-46d7-8a96-6c6f9bec88b2
# Description              : 
# Issued                   : 2023-11-02T00:10:07.951259
# Modified                 : 2023-11-09T00:40:07.327635
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/bf6061ef-829e-42fd-9b98-8990bfbaf03f/resource/66df0412-22eb-48c4-90b8-b98f49746512/download/prod_netex_tt_1.10_che_ski_2023_oev-schweiz_readme_1_1_202311010611.csv')

# Distribution 7
# Package_id               : 90ee5386-002a-46d7-8a96-6c6f9bec88b2
# Description              : 
# Issued                   : 2023-08-30T20:05:08.445795
# Modified                 : 2023-08-30T20:05:08.445795
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/bf6061ef-829e-42fd-9b98-8990bfbaf03f/resource/dbb36a52-4b70-4530-bd79-730ae60a2169/download/prod_netex_tt_1.10_che_ski_2023_oev-schweiz_readme_1_1_202308300608.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@sbb.ch | Fachstelle Open-Data-Plattform Mobilität Schweiz
