---
title: "Open Government Data, opendata.swiss"
date: "2025-05-16"
output: html_document
---

## Dataset: Phenotypic and Growth Stage Development Data of a Quercus robur Mycorrhization Experiment



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/phenotypic-and-growth-stage-development-data-of-a-quercus-robur-mycorrhization-experiment)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/cenococcum-geophilum-and-quercus-robur-mycorrhization-experiment)

Auto generated R starter code for data set 9d0661cc-cbbc-452e-8bd9-574161c73cd1@envidat.

## Metadata

- **Publisher.name** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2025-05-09T06:09:27+00:00`
- **Metadata_created** `2025-05-10T03:48:53.381866`
- **Metadata_modified** `2025-05-10T03:48:53.381874`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 913a5abe-2d42-4056-84bd-1cb57be8ec67
# Description              : 
# Issued                   : 2025-05-09T06:10:35+00:00
# Modified                 : 2025-05-09T09:17:40+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://www.envidat.ch/dataset/cenococcum-geophilum-and-quercus-robur-mycorrhization-experiment/resource/2664abc3-ba85-4000-bb9d-162677eb47b7')

# Distribution 1
# Package_id               : 913a5abe-2d42-4056-84bd-1cb57be8ec67
# Description              : 
# Issued                   : 2025-05-09T06:12:21+00:00
# Modified                 : 2025-05-09T09:18:08+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://www.envidat.ch/dataset/cenococcum-geophilum-and-quercus-robur-mycorrhization-experiment/resource/e0197cc6-6279-4f22-8e6a-3cc51a8973e1')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
