---
title: "Open Government Data, opendata.swiss"
date: "2025-07-29"
output: html_document
---

## Dataset: Schulanlagen

Standorte der Schulanlagen (Kindergarten, Kinderhort, Volksschule, Sonderschule)

**Zweck**: Lokalisation der Standorte der Schulanlagen

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/schulanlagen)<br>
[Direct link by **Stadt Z端rich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_schulanlagen)

Auto generated R starter code for data set 62f69136-712e-492e-8de3-61549aa218d3@stadt-zurich.

## Metadata

- **Publisher.name** `Schulraumplanung, Schulamt, Schul- und Sportdepartement`
- **Organization.display_name.de** `Stadt Z端rich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Z端rich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['stzh', 'geoportal', 'schule', 'kindergarten', 'kinderhort', 'punktdaten', 'volksschule', 'sonderschule', 'bildung', 'geodaten']`
- **Issued** `nan`
- **Metadata_created** `2023-11-07T03:43:33.367838`
- **Metadata_modified** `2025-07-29T02:58:04.312298`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 95a395a4-39a7-41f5-addb-f8342bd51cde
# Description              : 
# Issued                   : 2023-06-11T03:19:49.332585
# Modified                 : None
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Schulanlagen?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Z端rich
