---
title: "Open Government Data, opendata.swiss"
date: "2024-06-19"
output: html_document
---

## Dataset: LiDAR metrics predict suitable forest foraging areas of endangered Mouse-eared bats (Myotis myotis)



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/lidar-metrics-predict-suitable-forest-foraging-areas-of-endangered-mouse-eared-bats-myotis-myot)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/lidar_forest_myotis-myotis)

Auto generated R starter code for data set b64e697c-bef8-455f-a2ca-96e269fdfd1c@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2022-04-08T08:45:26+00:00`
- **Metadata_created** `2024-05-18T03:23:13.529786`
- **Metadata_modified** `2024-06-15T03:28:16.418032`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 962d6064-d04f-49c8-ae84-e220bf37b43a
# Description              : 
# Issued                   : 2022-04-12T11:11:09+00:00
# Modified                 : 2022-04-12T13:11:11+00:00
# Rights                   : NonCommercialWithPermission-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/lidar_forest_myotis-myotis/resource/121b2a4d-d2a0-416e-bd23-3a744cb57b1b')

# Distribution 1
# Package_id               : 962d6064-d04f-49c8-ae84-e220bf37b43a
# Description              : 
# Issued                   : 2022-04-10T15:06:16+00:00
# Modified                 : 2022-04-10T15:06:16+00:00
# Rights                   : NonCommercialWithPermission-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/lidar_forest_myotis-myotis/resource/8b121238-5319-4a48-ad15-a0382e8e37f8')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
