---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Aerosol Data Davos Wolfgang



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/aerosol-data-davos-wolfgang)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/aerosol-data-davos-wolfgang)

Auto generated R starter code for data set 03a2914e-d0c6-438a-b4c0-5f576db641da@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `EnviDat Support`
- **Maintainer_email** `envidat@wsl.ch`
- **Keywords.de** `[]`
- **Issued** `2020-03-26T00:00:00`
- **Metadata_created** `2021-06-15T16:22:29.885265`
- **Metadata_modified** `2023-01-14T01:15:28.526405`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 96b729ba-6f7e-4a76-b9ec-99d5437bc552
# Description              : 
# Issued                   : 2020-03-26T00:00:00
# Modified                 : 2020-03-26T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/aerosol-data-davos-wolfgang/resource/2632179e-3c62-45f8-9454-c3d946ccf430')

# Distribution 1
# Package_id               : 96b729ba-6f7e-4a76-b9ec-99d5437bc552
# Description              : 
# Issued                   : 2020-03-26T00:00:00
# Modified                 : 2020-03-26T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/aerosol-data-davos-wolfgang/resource/a0a29389-e885-4e4d-bc5f-a65913a0ba46')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
