---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Entsorgungskalender Papier

Sammeltage der Papierentsorgung nach PLZ

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/entsorgungskalender-papier1)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_papier)

Auto generated R starter code for data set 266fe85f-3ae0-466a-b6f5-2a8e663893cc@stadt-zurich.

## Metadata

- **Publisher** `Entsorgung + Recycling Zürich, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['entsorgungskalender', 'kalender', 'abfall', 'tabellen', 'entsorgung', 'sachdaten']`
- **Issued** `2012-06-28T00:00:00`
- **Metadata_created** `2020-12-23T15:29:28.237265`
- **Metadata_modified** `2023-01-16T00:51:50.747764`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 9baf7969-630f-4d09-92da-128326e93b4c
# Description              : 
# Issued                   : 2021-12-23T00:00:00
# Modified                 : 2023-01-15T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_papier/download/entsorgungskalender_papier_2022.csv')

# Distribution 1
# Package_id               : 9baf7969-630f-4d09-92da-128326e93b4c
# Description              : 
# Issued                   : 2022-12-20T00:00:00
# Modified                 : 2023-01-15T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_papier/download/entsorgungskalender_papier_2023.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
