---
title: "Open Government Data, opendata.swiss"
date: "2024-03-17"
output: html_document
---

## Dataset: Schulferien und Feiertage Stadt St.Gallen

Der Datensatz zeigt die Daten der Schulferien und Feiertage in der Stadt St.Gallen.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/schulferien-und-feiertage-stadt-st-gallen)<br>
[Direct link by **Stadt St.Gallen** for dataset](https://daten.stadt.sg.ch/explore/dataset/schulferien-feiertage-stadt-stgallen/)

Auto generated R starter code for data set schulferien-feiertage-stadt-stgallen@stadt-st-gallen.

## Metadata

- **Publisher** `stadt-st-gallen`
- **Organization.display_name.de** `Stadt St.Gallen`
- **Organization.url** `https://www.stadt.sg.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['feiertage', 'ferien', 'schule']`
- **Issued** `2022-02-22T00:00:00`
- **Metadata_created** `2023-12-21T12:47:37.387464`
- **Metadata_modified** `2024-03-15T05:01:00.350015`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 9dd75eb2-cac9-48a3-b9b2-b70e6d8fa3b9
# Description              : Schulferien und Feiertage Stadt St.Gallen (csv)
# Issued                   : 2022-02-22T00:00:00
# Modified                 : 2024-01-30T09:51:04.666000+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://daten.stadt.sg.ch/api/v2/catalog/datasets/schulferien-feiertage-stadt-stgallen/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@stadt.sg.ch | OGD-Koordinationsstelle St.Gallen
