---
title: "Open Government Data, opendata.swiss"
date: "2023-05-12"
output: html_document
---

## Dataset: Test GO dataset 1



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/test-go-dataset-1)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/test-go-dataset-1)

Auto generated R starter code for data set test-go-dataset-1@oevch.

## Metadata

- **Publisher** `Publisher 1`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2023-05-11T00:00:00`
- **Metadata_created** `2023-05-12T00:43:40.962085`
- **Metadata_modified** `2023-05-12T00:43:40.962092`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 3 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : 9e846b72-1af9-4b69-85a1-13d91e28758a
# Description              : 
# Issued                   : 2023-05-11T00:00:00
# Modified                 : 2023-05-11T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/20d18ab7-e953-4d59-ba48-3596909e6996/resource/0cb3b62c-78c6-49d1-bb31-216f6faaadd1/download/full_business_organisation_versions_2023-05-11.csv')

# Distribution 1
# Package_id               : 9e846b72-1af9-4b69-85a1-13d91e28758a
# Description              : 
# Issued                   : 2023-05-11T00:00:00
# Modified                 : 2023-05-11T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/20d18ab7-e953-4d59-ba48-3596909e6996/resource/66eef592-5a27-4ab1-9829-abd5d6094196/download/actual_date_business_organisation_versions_2023-05-10.csv')

# Distribution 2
# Package_id               : 9e846b72-1af9-4b69-85a1-13d91e28758a
# Description              : 
# Issued                   : 2023-05-11T00:00:00
# Modified                 : 2023-05-11T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/20d18ab7-e953-4d59-ba48-3596909e6996/resource/41fab8cc-9d29-459a-83e1-c7bca9276a9b/download/actual_date_business_organisation_versions_2023-05-11.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

contact@example.com | Contact Name
