---
title: "Open Government Data, opendata.swiss"
date: "2023-10-11"
output: html_document
---

## Dataset: Gesch채ftsorganisationen

Die Gesch채ftsorganisationen stellen eine organisatorische Strukturierung der Transportunternehmen nach abrechnungstechnischen und kundinformativen Merkmalen dar.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/geschaftsorganisationen)<br>
[Direct link by **Gesch채ftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/go)

Auto generated R starter code for data set go@oevch.

## Metadata

- **Publisher** `Fachstelle Open Data`
- **Organization.display_name.de** `Gesch채ftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['transportunternehmen', 'verkehrsunternehmen', 'go', 'sboid', 'geschaftsorganisation', 'vu', 'said', 'tu']`
- **Issued** `2023-05-12T13:55:14.771637`
- **Metadata_created** `2023-06-24T00:40:52.692588`
- **Metadata_modified** `2023-10-11T00:36:56.560772`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 3 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : a14410db-19ee-414b-bc2a-f02a40c53b25
# Description              : 
# Issued                   : 2023-10-10T14:40:09.347059
# Modified                 : 2023-10-10T14:40:09.347059
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/11eaa47d-6f9d-4ddc-a660-02ad0eeaea8f/resource/8360a553-be71-417e-b2e4-a99f8117f0ef/download/actual_date_business_organisation_versions_2023-10-10.csv')

# Distribution 1
# Package_id               : a14410db-19ee-414b-bc2a-f02a40c53b25
# Description              : 
# Issued                   : 2023-10-10T14:40:13.863902
# Modified                 : 2023-10-10T14:40:13.863902
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/11eaa47d-6f9d-4ddc-a660-02ad0eeaea8f/resource/36fc11bb-6b01-443e-9ecc-96deeba70039/download/future_timetable_business_organisation_versions_2023-10-10.csv')

# Distribution 2
# Package_id               : a14410db-19ee-414b-bc2a-f02a40c53b25
# Description              : 
# Issued                   : 2023-10-10T14:40:11.679299
# Modified                 : 2023-10-10T14:40:11.679299
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/11eaa47d-6f9d-4ddc-a660-02ad0eeaea8f/resource/f7393b36-c32f-4d81-b3a1-bc8d9183d0d2/download/full_business_organisation_versions_2023-10-10.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@sbb.ch | Fachstelle Open Data
