---
title: "Open Government Data, opendata.swiss"
date: "2025-02-25"
output: html_document
---

## Dataset: Archiv Wahlresultate Ständeratswahlen

Ergebnisse der Erneuerungswahlen der zürcherischen Mitglieder des Ständerates

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/wahlarchiv-standeratswahlen)<br>
[Direct link by **Statistisches Amt Kanton Zürich** for dataset](https://www.zh.ch/de/politik-staat/wahlen-abstimmungen/national-staenderatswahlen.html)

Auto generated R starter code for data set 695@statistisches-amt-kanton-zuerich.

## Metadata

- **Publisher** `Statistisches Amt des Kantons Zürich`
- **Organization.display_name.de** `Statistisches Amt Kanton Zürich`
- **Organization.url** `https://www.zh.ch/de/direktion-der-justiz-und-des-innern/statistisches-amt.html`
- **Maintainer** `Statistisches Amt des Kantons Zürich, Wahlen & Abstimmungen`
- **Maintainer_email** `wahlen@statistik.ji.zh.ch`
- **Keywords.de** `['staenderatswahlen', 'wahlergebnisse', 'politischeparteien', 'wahlen', 'politik', 'staenderat', 'kantonzuerich']`
- **Issued** `2020-07-07T16:48:00+01:00`
- **Metadata_created** `2021-01-14T17:21:36.184288`
- **Metadata_modified** `2025-02-24T05:06:00.061050`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 20 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2020-07-07T17:01:08+01:00
# Modified                 : 2023-11-24T16:29:23+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001698.csv')

# Distribution 1
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2020-07-07T17:01:28+01:00
# Modified                 : 2023-11-24T16:28:39+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001699.csv')

# Distribution 2
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2023-10-22T19:16:33+01:00
# Modified                 : 2023-11-24T16:27:52+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00004686.csv')

# Distribution 3
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2023-11-22T14:44:47+01:00
# Modified                 : 2023-11-24T16:27:25+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00004904.csv')

# Distribution 4
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2023-10-22T19:15:10+01:00
# Modified                 : 2023-12-08T09:56:48+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00004685.csv')

# Distribution 5
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2021-06-01T12:59:42+01:00
# Modified                 : 2023-12-08T09:55:52+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001819.csv')

# Distribution 6
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2021-06-01T13:07:24+01:00
# Modified                 : 2023-12-08T09:56:31+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001824.csv')

# Distribution 7
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2020-07-07T17:00:45+01:00
# Modified                 : 2023-11-24T16:30:01+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001697.csv')

# Distribution 8
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2021-06-01T13:03:51+01:00
# Modified                 : 2023-12-08T10:02:32+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001823.csv')

# Distribution 9
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2021-06-01T13:00:38+01:00
# Modified                 : 2023-12-08T10:02:12+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001820.csv')

# Distribution 10
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2021-06-01T10:59:23+01:00
# Modified                 : 2023-12-08T10:01:51+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001818.csv')

# Distribution 11
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2020-07-07T16:58:36+01:00
# Modified                 : 2023-11-22T15:11:43+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001694.csv')

# Distribution 12
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2023-11-22T14:46:11+01:00
# Modified                 : 2023-12-08T10:03:03+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00004905.csv')

# Distribution 13
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2021-06-01T10:46:51+01:00
# Modified                 : 2023-12-08T09:55:18+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001817.csv')

# Distribution 14
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2020-07-07T16:59:19+01:00
# Modified                 : 2023-11-22T15:10:11+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001696.csv')

# Distribution 15
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2020-07-07T16:58:17+01:00
# Modified                 : 2023-11-22T15:12:31+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001693.csv')

# Distribution 16
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2021-06-01T13:10:50+01:00
# Modified                 : 2023-12-08T10:02:49+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001825.csv')

# Distribution 17
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2021-06-01T13:01:26+01:00
# Modified                 : 2023-12-08T09:56:13+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001821.csv')

# Distribution 18
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2020-07-07T16:59:00+01:00
# Modified                 : 2023-11-22T15:10:49+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001695.csv')

# Distribution 19
# Package_id               : a3faf103-7b94-4036-b6bb-2138d08a45e1
# Description              : 
# Issued                   : 2020-07-07T17:02:14+01:00
# Modified                 : 2023-11-24T16:28:16+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00000695_00001700.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

wahlen@statistik.ji.zh.ch | Statistisches Amt des Kantons Zürich, Wahlen & Abstimmungen
