---
title: "Open Government Data, opendata.swiss"
date: "2023-12-06"
output: html_document
---

## Dataset: Entsorgungskalender CargoTram

Sammeltage CargoTram nach PLZ

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/entsorgungskalender-cargotram2)<br>
[Direct link by **Stadt Z端rich** for dataset](https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_cargotram)

Auto generated R starter code for data set 08480959-defa-41c1-81c4-b10bea2404ef@stadt-zurich.

## Metadata

- **Publisher** `Entsorgung + Recycling Z端rich, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Z端rich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['tabellen', 'entsorgungskalender', 'abfall', 'entsorgung', 'kalender', 'sachdaten']`
- **Issued** `2012-06-25T00:00:00`
- **Metadata_created** `2023-12-02T02:20:32.652711`
- **Metadata_modified** `2023-12-06T02:50:05.011073`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : a59dea87-ca7d-465f-8c74-b3b62c652679
# Description              : 
# Issued                   : 2023-01-12T11:55:06.212484
# Modified                 : 2023-05-12T16:10:24.393652
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_cargotram/download/entsorgungskalender_cargoTram_2023.csv')

# Distribution 1
# Package_id               : a59dea87-ca7d-465f-8c74-b3b62c652679
# Description              : 
# Issued                   : 2023-01-12T11:55:07.115227
# Modified                 : 2023-05-12T16:10:25.394714
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_cargotram/download/entsorgungskalender_cargoTram_2024.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Z端rich
