---
title: "Open Government Data, opendata.swiss"
date: "2023-09-25"
output: html_document
---

## Dataset: Feuerwehrstellflächen

Feuerwehrzufahrten, Bewegungs- und Stellflächen

**Zweck**: Dokumentation der Feuerwehrstellflächen

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/feuerwehrstellflachen)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_feuerwehrstellflaechen)

Auto generated R starter code for data set 4a6c84fc-30d8-4166-a9f8-ba12bf9d4286@stadt-zurich.

## Metadata

- **Publisher** `Einsatzplanung, Schutz & Rettung, Sicherheitsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['geoportal', 'stzh', 'polygondaten', 'vektordaten', 'geodaten']`
- **Issued** `nan`
- **Metadata_created** `2022-05-10T01:10:11.115627`
- **Metadata_modified** `2023-09-25T01:36:02.513949`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : a6c5cdcb-a04a-4846-9e47-e139a1b927b6
# Description              : 
# Issued                   : 2022-05-09T02:57:54.895068
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Feuerwehrstellflaechen?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
