---
title: "Open Government Data, opendata.swiss"
date: "2024-10-31"
output: html_document
---

## Dataset: Wahlen Gemeindekommissionen 2024: Kandidierendenresultate

Kommunale Wahlen vom 3. März 2024 (offiziell kandidierende Personen)

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/wahlen-gemeindekommissionen-2024-kandidierendenresultate)<br>
[Direct link by **Kanton Basel-Landschaft** for dataset](https://data.bl.ch/explore/dataset/12380/)

Auto generated R starter code for data set 12380@kanton-basel-landschaft.

## Metadata

- **Publisher** `kanton-basel-landschaft`
- **Organization.display_name.de** `Kanton Basel-Landschaft`
- **Organization.url** `https://www.baselland.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['name', 'geschlecht', 'vorname', 'jahrgang', 'gemeindewahlen', 'kommunalwahlen']`
- **Issued** `2024-02-28T00:00:00`
- **Metadata_created** `2024-02-28T04:44:54.257588`
- **Metadata_modified** `2024-10-31T03:39:11.166889`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : a9e877ab-e7cd-4e98-80d4-02d51e5ae7da
# Description              : Wahlen Gemeindekommissionen 2024: Kandidierendenresultate (csv)
# Issued                   : 2024-02-28T00:00:00
# Modified                 : 2024-10-15T11:39:07.761000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.bl.ch/api/v2/catalog/datasets/12380/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

wahlen-abstimmungen@bl.ch | Isabel Rabaglio
