---
title: "Open Government Data, opendata.swiss"
date: "2024-04-18"
output: html_document
---

## Dataset: Wöchentliche Todesfälle, 2010-2024

Dieses Dataset präsentiert die wöchentlichen Zahlen der Todesfälle, der erwarteten Todesfälle und der Übersterblichkeit nach Alter (0-64, 65+), 2010-2024.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/wochentliche-todesfalle-2010-20241)<br>
[Direct link by **Bundesamt für Statistik BFS** for dataset](https://www.bfs.admin.ch/asset/de/ts-d-14.03.04.03-wr)

Auto generated R starter code for data set 31786108@bundesamt-fur-statistik-bfs.

## Metadata

- **Publisher** `BFS/OFS`
- **Organization.display_name.de** `Bundesamt für Statistik BFS`
- **Organization.url** `https://www.bfs.admin.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['gesundheit']`
- **Issued** `2024-04-16T12:00:00+00:00`
- **Metadata_created** `2024-04-17T09:35:23.198251`
- **Metadata_modified** `2024-04-17T09:35:23.198257`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 4 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : aaa9b8e8-6954-4948-9c05-10becb01461a
# Description              : 
# Issued                   : 2024-04-16T12:00:00+00:00
# Modified                 : 2024-04-16T06:41:44.114000+00:00
# Rights                   : NonCommercialAllowed-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://dam-api.bfs.admin.ch/hub/api/dam/assets/31786132/master')

# Distribution 1
# Package_id               : aaa9b8e8-6954-4948-9c05-10becb01461a
# Description              : 
# Issued                   : 2024-04-16T12:00:00+00:00
# Modified                 : 2024-04-16T06:41:44.143000+00:00
# Rights                   : NonCommercialAllowed-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://dam-api.bfs.admin.ch/hub/api/dam/assets/31786120/master')

# Distribution 2
# Package_id               : aaa9b8e8-6954-4948-9c05-10becb01461a
# Description              : 
# Issued                   : 2024-04-16T12:00:00+00:00
# Modified                 : 2024-04-16T06:41:44.105000+00:00
# Rights                   : NonCommercialAllowed-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://dam-api.bfs.admin.ch/hub/api/dam/assets/31786128/master')

# Distribution 3
# Package_id               : aaa9b8e8-6954-4948-9c05-10becb01461a
# Description              : Dieses Dataset präsentiert die wöchentlichen Zahlen der Todesfälle, der erwarteten Todesfälle und der Übersterblichkeit nach Alter (0-64, 65+), 2010-2024.
# Issued                   : 2024-04-16T12:00:00+00:00
# Modified                 : 2024-04-16T06:41:44.112000+00:00
# Rights                   : NonCommercialAllowed-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://dam-api.bfs.admin.ch/hub/api/dam/assets/31786122/master')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

auskunftsdienst@bfs.admin.ch | info@bfs.admin.ch
