---
title: "Open Government Data, opendata.swiss"
date: "2023-10-23"
output: html_document
---

## Dataset: Wöchentliche Todesfälle, 2010-2019

Diese Tabelle wird nicht mehr aktualisiert. Sie finden neuere Daten in der Tabelle «Wöchentliche Todesfälle, 2010-2022» (siehe Link unten).

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/wochentliche-todesfalle-2010-2019)<br>
[Direct link by **Bundesamt für Statistik BFS** for dataset](https://www.bfs.admin.ch/asset/de/ts-d-14.03.04.03-wr_ZR)

Auto generated R starter code for data set 12607331@bundesamt-fur-statistik-bfs.

## Metadata

- **Publisher** `BFS/OFS`
- **Organization.display_name.de** `Bundesamt für Statistik BFS`
- **Organization.url** `https://www.bfs.admin.ch`
- **Maintainer** `info@bfs.admin.ch`
- **Maintainer_email** `auskunftsdienst@bfs.admin.ch`
- **Keywords.de** `['gesundheit']`
- **Issued** `2020-04-15T12:00:00+00:00`
- **Metadata_created** `2023-02-22T10:13:10.309937`
- **Metadata_modified** `2023-10-23T11:51:28.438661`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 4 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : ac0dc0b7-1de2-4fda-9b23-be8952df6c75
# Description              : 
# Issued                   : 2020-04-15T12:00:00+00:00
# Modified                 : 2021-07-14T09:15:37.379000+00:00
# Rights                   : NonCommercialAllowed-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.bfs.admin.ch/bfsstatic/dam/assets/12607335/master')

# Distribution 1
# Package_id               : ac0dc0b7-1de2-4fda-9b23-be8952df6c75
# Description              : 
# Issued                   : 2020-04-15T12:00:00+00:00
# Modified                 : 2021-07-14T09:15:37.366000+00:00
# Rights                   : NonCommercialAllowed-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.bfs.admin.ch/bfsstatic/dam/assets/12607334/master')

# Distribution 2
# Package_id               : ac0dc0b7-1de2-4fda-9b23-be8952df6c75
# Description              : 
# Issued                   : 2020-04-15T12:00:00+00:00
# Modified                 : 2021-07-14T09:15:37.361000+00:00
# Rights                   : NonCommercialAllowed-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.bfs.admin.ch/bfsstatic/dam/assets/12607333/master')

# Distribution 3
# Package_id               : ac0dc0b7-1de2-4fda-9b23-be8952df6c75
# Description              : Diese Tabelle wird nicht mehr aktualisiert. Sie finden neuere Daten in der Tabelle «Wöchentliche Todesfälle, 2010-2022» (siehe Link unten).
# Issued                   : 2020-04-15T12:00:00+00:00
# Modified                 : 2021-07-14T09:15:37.348000+00:00
# Rights                   : NonCommercialAllowed-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.bfs.admin.ch/bfsstatic/dam/assets/12607336/master')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

auskunftsdienst@bfs.admin.ch | info@bfs.admin.ch
