---
title: "Open Government Data, opendata.swiss"
date: "2024-01-07"
output: html_document
---

## Dataset: Mittlere Wohnbevölkerung


Mittlere Wohnbevölkerung pro Jahr.


[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/mittlere-wohnbevolkerung)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/bev_bestand_jahr_mittlerewbev_od3224)

Auto generated R starter code for data set 573fdd26-1199-42fe-bd2e-3a18137f8f8f@stadt-zurich.

## Metadata

- **Publisher** `Bevölkerungsamt, Präsidialdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['jahresmittel', 'bevoelkerung', 'tabelle', 'wohndichte', 'sasa', 'sachdaeten', 'mittel']`
- **Issued** `2020-04-16T00:00:00`
- **Metadata_created** `2021-03-18T04:11:01.550546`
- **Metadata_modified** `2024-01-07T03:36:53.449748`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : ac989d07-0d33-4bdb-b41c-8cdacb063a65
# Description              : 
# Issued                   : 2021-03-17T18:09:41.060476
# Modified                 : 2024-06-01T20:59:35.218597
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/bev_bestand_jahr_mittlerewbev_od3224/download/BEV322OD3224.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
