---
title: "Open Government Data, opendata.swiss"
date: "2024-11-06"
output: html_document
---

## Dataset: Ständeratswahlen 2015

Schlussresultate der eidgenössischen Wahl 'Ständeratswahlen 2015', 18. Oktober 2015, Graubünden - Grischun - Grigioni, aufgeschlüsselt nach Kandidaten und Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/standeratswahlen-2015)<br>
[Direct link by **Standeskanzlei Graubünden** for dataset](https://abstimmungen.gr.ch/election/staenderatswahlen-2015/data)

Auto generated R starter code for data set election-staenderatswahlen-2015@standeskanzlei-graubuenden.

## Metadata

- **Publisher** `Standeskanzlei Graubünden`
- **Organization.display_name.de** `Standeskanzlei Graubünden`
- **Organization.url** ``
- **Maintainer** `Standeskanzlei Graubünden`
- **Maintainer_email** `info@gr.ch`
- **Keywords.de** `['wahl', 'national']`
- **Issued** `2015-10-18T00:00:00`
- **Metadata_created** `2018-06-12T17:32:24.035526`
- **Metadata_modified** `2024-10-03T19:11:15.952730`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : ad1b2b2d-4d15-46a0-8b8c-0ebcec208456
# Description              : 
# Issued                   : 2018-06-08T20:34:26+00:00
# Modified                 : 2022-01-19T06:36:17+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://abstimmungen.gr.ch/election/staenderatswahlen-2015/data-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

info@gr.ch | Standeskanzlei Graubünden
