---
title: "Open Government Data, opendata.swiss"
date: "2024-08-17"
output: html_document
---

## Dataset: Soil solution monitoring of the Intercantonal Forest Observation Program



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/soil-solution-monitoring-of-the-intercantonal-forest-observation-program)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/soil-solution-monitoring-of-the-intercantonal-forest-observation-program)

Auto generated R starter code for data set 00a72e44-0d27-4a47-8046-7729a4de40d5@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2023-01-27T09:19:08+00:00`
- **Metadata_created** `2024-05-18T03:26:57.183412`
- **Metadata_modified** `2024-06-29T03:29:41.662647`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : aea5ce43-d2d9-4f62-a50b-57b9d435ee34
# Description              : 
# Issued                   : 2023-01-27T09:20:35+00:00
# Modified                 : 2023-01-27T09:20:35+00:00
# Rights                   : NonCommercialWithPermission-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/soil-solution-monitoring-of-the-intercantonal-forest-observation-program/resource/42360669-d833-4758-8482-9cc836f0af4b')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

simon.tresch@iap.ch | Simon Tresch
