---
title: "Open Government Data, opendata.swiss"
date: "2023-11-29"
output: html_document
---

## Dataset: Equiden - Verendungen

Anzahl Verendungen (ohne Euthanasie) unterteilt nach Equidentypen im Zeitverlauf. Die Meldungen zu Verendungen und Euthanasie können von Unschärfen betroffen sein.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/equiden-todesfalle)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set equids-deaths@identitas.

## Metadata

- **Publisher** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `Team Tierstatistik Identitas AG`
- **Maintainer_email** `tierstatistik@identitas.ch`
- **Keywords.de** `['verendungen', 'heimtiere', 'nutztiere', 'equiden', 'ruckverfolgbarkeit']`
- **Issued** `2023-10-31T00:00:00`
- **Metadata_created** `2022-06-07T11:18:50.447710`
- **Metadata_modified** `2023-11-28T03:53:49.449496`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : afb07afe-b64d-4d2e-a4d6-63e7a38cf679
# Description              : 
# Issued                   : 2023-11-27T00:00:00
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://tierstatistik.identitas.ch/data/equids-deaths.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
