---
title: "Open Government Data, opendata.swiss"
date: "2025-01-29"
output: html_document
---

## Dataset: Empfohlene Schwimmbereiche im Rhein

Der Datensatz enthält die empfohlenen Schwimmbereiche im Rhein.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/empfohlene-schwimmbereiche-im-rhein)<br>
[Direct link by **Kanton Basel-Stadt** for dataset](https://data.bs.ch/explore/dataset/100270/)

Auto generated R starter code for data set 100270@kanton-basel-stadt.

## Metadata

- **Publisher** `Kantonspolizei`
- **Organization.display_name.de** `Kanton Basel-Stadt`
- **Organization.url** `https://www.opendata.bs.ch`
- **Maintainer** `Fachstelle für OGD Basel-Stadt`
- **Maintainer_email** `opendata@bs.ch`
- **Keywords.de** `['fluss', 'bachapp', 'schwimmen', 'sup', 'paddeln', 'bachab', 'rhein', 'treiben', 'schiff', 'sport', 'schwimmzone', 'stand-up-paddeln', 'boot', 'baden', 'schifffahrt']`
- **Issued** `2023-05-15T00:00:00`
- **Metadata_created** `2023-05-16T00:28:04.921614`
- **Metadata_modified** `2025-01-29T02:07:02.232718`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : b0c9acf9-8975-4327-afdf-06b9544f1738
# Description              : Empfohlene Schwimmbereiche im Rhein (csv)
# Issued                   : 2023-05-15T00:00:00
# Modified                 : 2023-04-14T07:39:38.684000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.bs.ch/api/v2/catalog/datasets/100270/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@bs.ch | Fachstelle für OGD Basel-Stadt
