---
title: "Open Government Data, opendata.swiss"
date: "2025-06-27"
output: html_document
---

## Dataset: Hydrochemical Data Collected during Spring-Fall 2021 in the Erlenbach Catchment



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/hydrochemical-data-collected-during-spring-fall-2021-in-the-erlenbach-catchment)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/hydrochemical-data-collected-during-spring-fall-2021-in-the-erlenbach-catchment)

Auto generated R starter code for data set 08c5b677-618f-4758-a261-c7562522bb2a@envidat.

## Metadata

- **Publisher.name** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `EnviDat Support`
- **Maintainer_email** `envidat@wsl.ch`
- **Keywords.de** `[]`
- **Issued** `2024-11-13T09:03:34+00:00`
- **Metadata_created** `2025-02-01T04:27:02.916617`
- **Metadata_modified** `2025-06-21T04:48:01.070364`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : b29cd159-a6b9-4341-aa32-8514cc1622bd
# Description              : 
# Issued                   : 2025-01-29T09:29:49+00:00
# Modified                 : 2025-01-29T10:30:36+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://www.envidat.ch/dataset/hydrochemical-data-collected-during-spring-fall-2021-in-the-erlenbach-catchment/resource/82bfc5c5-c6af-4954-80aa-f1478fe92157')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
