---
title: "Open Government Data, opendata.swiss"
date: "2024-02-15"
output: html_document
---

## Dataset: Nationalratswahlen 2023: Kandidierende, erhaltene Stimmen und Status (gew채hlt/nicht gew채hlt) (Kantone, Gemeinden)



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/nationalratswahlen-2023-kandidierende-erhaltene-stimmen-und-status-gewahlt-nicht-gewahlt-kanton)<br>
[Direct link by **Bundesamt f체r Statistik BFS** for dataset](https://www.bfs.admin.ch/asset/de/sd-t-17.02-NRW2023-kandidierende)

Auto generated R starter code for data set 28845339@bundesamt-fur-statistik-bfs.

## Metadata

- **Publisher** `BFS/OFS`
- **Organization.display_name.de** `Bundesamt f체r Statistik BFS`
- **Organization.url** `https://www.bfs.admin.ch`
- **Maintainer** `info@bfs.admin.ch`
- **Maintainer_email** `auskunftsdienst@bfs.admin.ch`
- **Keywords.de** `['politik']`
- **Issued** `2023-11-30T07:30:00+00:00`
- **Metadata_created** `2023-11-30T09:36:41.272984`
- **Metadata_modified** `2024-02-14T09:47:23.194429`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : b517cf56-2059-43ef-a8c9-52e7b34cde11
# Description              : 
# Issued                   : 2023-11-30T07:30:00+00:00
# Modified                 : 2023-12-04T07:06:02.893000+00:00
# Rights                   : NonCommercialAllowed-CommercialWithPermission-ReferenceRequired

df <- read_delim('https://dam-api.bfs.admin.ch/hub/api/dam/assets/28845350/appendix')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

auskunftsdienst@bfs.admin.ch | info@bfs.admin.ch
