---
title: "Open Government Data, opendata.swiss"
date: "2023-12-26"
output: html_document
---

## Dataset: Schulzählkreise in der Stadt St.Gallen

Schulzählkreise in der Stadt St.Gallen, historisch gewachsen

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/schulzahlkreise-in-der-stadt-st-gallen)<br>
[Direct link by **Stadt St.Gallen** for dataset](https://daten.stadt.sg.ch/explore/dataset/schulzahlkreise-stadt-stgallen/)

Auto generated R starter code for data set schulzahlkreise-stadt-stgallen@stadt-st-gallen.

## Metadata

- **Publisher** `stadt-st-gallen`
- **Organization.display_name.de** `Stadt St.Gallen`
- **Organization.url** `2023-12-21-092646.943088Logostgallenrgb300dpi.jpg`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['open-data-hack-stgallen', 'schulwege', 'schule', 'einzugsgebiet', 'schuler']`
- **Issued** `2021-11-05T00:00:00`
- **Metadata_created** `2023-12-21T12:46:58.777498`
- **Metadata_modified** `2023-12-21T16:40:15.309486`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : b804a888-1353-4d5a-98b3-6606cd12b988
# Description              : Schulzählkreise in der Stadt St.Gallen (csv)
# Issued                   : 2021-11-05T00:00:00
# Modified                 : 2021-11-05T15:44:12.045000+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://daten.stadt.sg.ch/api/v2/catalog/datasets/schulzahlkreise-stadt-stgallen/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@stadt.sg.ch | OGD-Koordinationsstelle St.Gallen
