---
title: "Open Government Data, opendata.swiss"
date: "2025-09-13"
output: html_document
---

## Dataset: Internetzugang der Haushalte

Diese Tabelle wird nicht mehr aktualisiert, da die Daten nicht mehr verf端gbar sind.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/internetzugang-der-haushalte)<br>
[Direct link by **Bundesamt f端r Statistik BFS** for dataset](https://www.bfs.admin.ch/asset/de/ts-x-ind-30109)

Auto generated R starter code for data set 31606007@bundesamt-fur-statistik-bfs.

## Metadata

- **Publisher.name** `BFS/OFS`
- **Organization.display_name.de** `Bundesamt f端r Statistik BFS`
- **Organization.url** `https://www.bfs.admin.ch`
- **Maintainer** `info@bfs.admin.ch`
- **Maintainer_email** `auskunftsdienst@bfs.admin.ch`
- **Keywords.de** `['kultur-medien-informationsgesellschaft-sport']`
- **Issued** `2024-06-05T06:30:00+00:00`
- **Metadata_created** `2024-06-05T09:36:57.277620`
- **Metadata_modified** `2025-09-12T10:37:39.492015`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : b8291ab6-6d07-4959-87be-723dc8449b9f
# Description              : Diese Tabelle wird nicht mehr aktualisiert, da die Daten nicht mehr verf端gbar sind.
# Issued                   : 2024-06-05T06:30:00+00:00
# Modified                 : 2024-05-28T07:22:08.218000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by_ask

df <- read_delim('https://dam-api.bfs.admin.ch/hub/api/dam/assets/31606013/master')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

auskunftsdienst@bfs.admin.ch | info@bfs.admin.ch
