---
title: "Open Government Data, opendata.swiss"
date: "2026-01-11"
output: html_document
---

## Dataset: toilet-v2

Neue Version v2 der Stammdaten und Metadaten vom System atlas (https://atlas.app.sbb.ch), bereitgestellt seit 7. Januar 2026 (atlas-v2).

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/toilet-v2)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://data.opentransportdata.swiss/dataset/toilet-v2)

Auto generated R starter code for data set toilet-v2@oevch.

## Metadata

- **Publisher.name** `nan`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2026-01-05T23:00:00`
- **Metadata_created** `2026-01-07T00:47:59.378365`
- **Metadata_modified** `2026-01-11T00:22:36.616484`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 3 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : b8af7098-1fa4-4946-be06-4481759bfb3c
# Description              : 
# Issued                   : 2026-01-10T08:55:20.958997
# Modified                 : 2026-01-10T08:55:20.958997
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.opentransportdata.swiss/dataset/bc740b09-42ba-425b-9986-490d8938135c/resource/357737fa-29cb-41bc-8db8-e7428477695f/download/timetable-years-toilet.csv')

# Distribution 1
# Package_id               : b8af7098-1fa4-4946-be06-4481759bfb3c
# Description              : 
# Issued                   : 2026-01-10T08:55:18.649911
# Modified                 : 2026-01-10T08:55:18.649911
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.opentransportdata.swiss/dataset/bc740b09-42ba-425b-9986-490d8938135c/resource/bc7740c6-92be-443e-830e-807d9f9b595f/download/full-toilet.csv')

# Distribution 2
# Package_id               : b8af7098-1fa4-4946-be06-4481759bfb3c
# Description              : 
# Issued                   : 2026-01-10T08:55:16.377676
# Modified                 : 2026-01-10T08:55:16.377676
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.opentransportdata.swiss/dataset/bc740b09-42ba-425b-9986-490d8938135c/resource/ad75ffac-8810-48a2-ab16-62ac4e67d3c9/download/actual-date-toilet.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@sbb.ch | Open data platform mobility Switzerland
