---
title: "Open Government Data, opendata.swiss"
date: "2026-01-11"
output: html_document
---

## Dataset: stop-point-v2

Neue Version v2 der Stammdaten und Metadaten vom System atlas (https://atlas.app.sbb.ch), bereitgestellt seit 7. Januar 2026 (atlas-v2).

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/stop-point-v2)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://data.opentransportdata.swiss/dataset/stop-point-v2)

Auto generated R starter code for data set stop-point-v2@oevch.

## Metadata

- **Publisher.name** `nan`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2026-01-05T23:00:00`
- **Metadata_created** `2026-01-07T00:47:51.199868`
- **Metadata_modified** `2026-01-11T00:22:37.767722`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 3 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : bb69bc63-9e4f-4f53-894e-a767e74cc99e
# Description              : 
# Issued                   : 2026-01-10T08:55:03.838674
# Modified                 : 2026-01-10T08:55:03.838674
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.opentransportdata.swiss/dataset/e73d185a-e445-450f-9800-f485c7721a37/resource/40f31b3f-c11a-4242-91d0-cd2378be8bc5/download/timetable-years-stop-point.csv')

# Distribution 1
# Package_id               : bb69bc63-9e4f-4f53-894e-a767e74cc99e
# Description              : 
# Issued                   : 2026-01-10T08:55:00.206446
# Modified                 : 2026-01-10T08:55:00.206446
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.opentransportdata.swiss/dataset/e73d185a-e445-450f-9800-f485c7721a37/resource/1f889a17-2fed-418f-a96e-14380c281b62/download/full-stop-point.csv')

# Distribution 2
# Package_id               : bb69bc63-9e4f-4f53-894e-a767e74cc99e
# Description              : 
# Issued                   : 2026-01-10T08:54:57.115464
# Modified                 : 2026-01-10T08:54:57.115464
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.opentransportdata.swiss/dataset/e73d185a-e445-450f-9800-f485c7721a37/resource/5d32597d-845c-439d-a142-84102a0ff950/download/actual-date-stop-point.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@sbb.ch | Open data platform mobility Switzerland
