---
title: "Open Government Data, opendata.swiss"
date: "2026-01-11"
output: html_document
---

## Dataset: traffic-point-v2

Neue Version v2 der Stammdaten und Metadaten vom System atlas (https://atlas.app.sbb.ch), bereitgestellt seit 7. Januar 2026 (atlas-v2).

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/traffic-point-v2)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://data.opentransportdata.swiss/dataset/traffic-point-v2)

Auto generated R starter code for data set traffic-point-v2@oevch.

## Metadata

- **Publisher.name** `nan`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2026-01-05T23:00:00`
- **Metadata_created** `2026-01-07T00:47:59.552091`
- **Metadata_modified** `2026-01-11T00:22:36.068661`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 3 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : bdd312f3-7bff-4b49-a1dd-6dbf16a9e317
# Description              : 
# Issued                   : 2026-01-10T08:55:40.593845
# Modified                 : 2026-01-10T08:55:40.593845
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.opentransportdata.swiss/dataset/b06d90be-91c6-440e-ab97-09f579d2fad0/resource/e74a679f-bd22-4e36-ba2c-cac52f8bbd20/download/timetable-years-world-traffic-point.csv')

# Distribution 1
# Package_id               : bdd312f3-7bff-4b49-a1dd-6dbf16a9e317
# Description              : 
# Issued                   : 2026-01-10T08:55:34.489602
# Modified                 : 2026-01-10T08:55:34.489602
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.opentransportdata.swiss/dataset/b06d90be-91c6-440e-ab97-09f579d2fad0/resource/129922d8-b39c-4788-a1b6-e5be03541d1c/download/full-world-traffic-point.csv')

# Distribution 2
# Package_id               : bdd312f3-7bff-4b49-a1dd-6dbf16a9e317
# Description              : 
# Issued                   : 2026-01-10T08:55:26.587566
# Modified                 : 2026-01-10T08:55:26.587566
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.opentransportdata.swiss/dataset/b06d90be-91c6-440e-ab97-09f579d2fad0/resource/8fa44fa8-eb2a-48ff-a4d2-ee5466328cc3/download/actual-date-world-traffic-point.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@sbb.ch | Open data platform mobility Switzerland
