---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Chironico, Switzerland: Long-term forest meteorological data from the Long-term Forest Ecosystem Research Programme (LWF), from 2000 onwards



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/chironico-switzerland-long-term-forest-meteorological-data-from-the-long-term-forest-ecosystem-)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/lwfmeteo-chironico)

Auto generated R starter code for data set aa85a779-49cb-4d55-bcaf-e957a48d0771@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `Matthias Haeni`
- **Maintainer_email** `matthias.haeni@wsl.ch`
- **Keywords.de** `[]`
- **Issued** `2016-11-09T00:00:00`
- **Metadata_created** `2021-06-15T16:24:26.911479`
- **Metadata_modified** `2023-01-14T01:16:17.375755`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : bf6860ba-d6cf-478d-86cf-a784c3e447b3
# Description              : 
# Issued                   : 2016-11-15T00:00:00
# Modified                 : 2016-11-15T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/lwfmeteo-chironico/resource/5993f35c-f254-4f4e-b603-82f1999524f4')

# Distribution 1
# Package_id               : bf6860ba-d6cf-478d-86cf-a784c3e447b3
# Description              : 
# Issued                   : 2016-11-15T00:00:00
# Modified                 : 2016-11-15T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.envidat.ch/dataset/lwfmeteo-chironico/resource/d2125be5-ab36-4a79-8873-100747c9304a')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
