---
title: "Open Government Data, opendata.swiss"
date: "2024-11-28"
output: html_document
---

## Dataset: Nationalratswahlen: Wähleranteil EVP [%]

Wähleranteil aller Listen der Partei EVP bei den Nationalratswahlen

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/nrw-wahleranteil-evp)<br>
[Direct link by **Statistisches Amt Kanton Zürich** for dataset](https://www.zh.ch/de/politik-staat/gemeinden/gemeindeportraet.html)

Auto generated R starter code for data set 81@statistisches-amt-kanton-zuerich.

## Metadata

- **Publisher** `Statistisches Amt des Kantons Zürich`
- **Organization.display_name.de** `Statistisches Amt Kanton Zürich`
- **Organization.url** `https://www.zh.ch/de/direktion-der-justiz-und-des-innern/statistisches-amt.html`
- **Maintainer** `Statistisches Amt des Kantons Zürich, Data Shop`
- **Maintainer_email** `datashop@statistik.zh.ch`
- **Keywords.de** `['gemeinden', 'parteien', 'wahlen', 'kantonzuerich', 'nationalratswahlen', 'bezirke', 'politik']`
- **Issued** `2016-01-20T20:16:00+01:00`
- **Metadata_created** `2021-01-14T18:10:40.313257`
- **Metadata_modified** `2024-11-27T03:42:07.877086`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : c08aa6db-2fb5-43c9-a06b-db11d21fc3bb
# Description              : 
# Issued                   : 2016-01-21T16:30:35+01:00
# Modified                 : 2023-11-28T15:34:16+01:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://www.web.statistik.zh.ch/ogd/data/KANTON_ZUERICH_121.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

datashop@statistik.zh.ch | Statistisches Amt des Kantons Zürich, Data Shop
