---
title: "Open Government Data, opendata.swiss"
date: "2024-08-15"
output: html_document
---

## Dataset: Hydranten

Hydranten der Wasserversorgung Stadt Zürich und private Hydranten, welche von der Wasserversorgung Stadt Zürich unterhalten (gewartet) werden.

**Zweck**: Dokumentation des Bestandes

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/hydranten)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_hydranten)

Auto generated R starter code for data set aded4385-240c-40ae-9e94-c9163dd42abc@stadt-zurich.

## Metadata

- **Publisher** `GIS, Wasserversorgung, Departement der Industriellen Betriebe`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['geodaten', 'vektordaten', 'stzh', 'wasserversorgung', 'hydranten', 'punktdaten', 'geoportal']`
- **Issued** `nan`
- **Metadata_created** `2023-11-07T03:39:15.095178`
- **Metadata_modified** `2024-08-15T03:33:25.646722`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : c83536ae-2fbe-4563-aa53-e661c09f88a5
# Description              : 
# Issued                   : 2023-06-11T03:30:21.402179
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Hydranten?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
