---
title: "Open Government Data, opendata.swiss"
date: "2025-09-19"
output: html_document
---

## Dataset: Kantonsratswahl 2022 Gde Steinhausen

Schlussresultate der eidgenössischen Wahl 'Kantonsratswahl 2022 Gde Steinhausen', 2. Oktober 2022, Kanton Zug, aufgeschlüsselt nach Kandidaten und Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/kantonsratswahl-2022-gde-steinhausen)<br>
[Direct link by **Staatskanzlei Zug** for dataset](https://wab.zug.ch/election/kantonsratswahl-2022-gde-steinhausen/data)

Auto generated R starter code for data set election-kantonsratswahl-2022-gde-steinhausen@staatskanzlei-zug.

## Metadata

- **Publisher.name** `Staatskanzlei Zug`
- **Organization.display_name.de** `Staatskanzlei Zug`
- **Organization.url** ``
- **Maintainer** `Staatskanzlei Zug`
- **Maintainer_email** `info@zg.ch`
- **Keywords.de** `['wahl', 'kommunal']`
- **Issued** `2022-10-02T00:00:00`
- **Metadata_created** `2022-10-03T01:21:37.476074`
- **Metadata_modified** `2025-09-19T03:21:47.979469`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : c94f998f-4f2a-4ba1-90e9-dc40ccb03ff6
# Description              : 
# Issued                   : 2022-09-26T09:26:40+00:00
# Modified                 : 2024-06-18T10:31:41+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://wab.zug.ch/election/kantonsratswahl-2022-gde-steinhausen/data-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

info@zg.ch | Staatskanzlei Zug
