---
title: "Open Government Data, opendata.swiss"
date: "2023-09-03"
output: html_document
---

## Dataset: Equiden - Sömmerungen nach Kantonen

Bestand der registrierten, lebenden Equiden im Sömmerungsgebiet im Zeitverlauf nach Kantonen in der Schweiz und in Liechtenstein. Die Jahresansicht zeigt den Tierbestand zum 25. Juli (DZV Artikel 98).

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/equiden-sommerungen-nach-kantonen)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set equids-summering-canton@identitas.

## Metadata

- **Publisher** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `Team Tierstatistik Identitas AG`
- **Maintainer_email** `tierstatistik@identitas.ch`
- **Keywords.de** `['sommerung', 'equiden', 'kanton', 'nutztiere']`
- **Issued** `2023-07-31T00:00:00`
- **Metadata_created** `2022-10-25T01:34:01.958337`
- **Metadata_modified** `2023-08-29T02:48:50.061873`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : cc430215-1400-4f71-ba2b-e0eb7b95853c
# Description              : 
# Issued                   : 2023-08-28T00:00:00
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://tierstatistik.identitas.ch/data/equids-summering-canton.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
