---
title: "Open Government Data, opendata.swiss"
date: "2023-12-18"
output: html_document
---

## Dataset: Ständeratswahl Zug 2015

Schlussresultate der kantonalen Wahl 'Ständeratswahl Zug 2015', 18. Oktober 2015, Kanton Zug, aufgeschlüsselt nach Kandidaten und Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/standeratswahl-2015)<br>
[Direct link by **Staatskanzlei Zug** for dataset](https://wab.zug.ch/election/staenderatswahl-2015/data)

Auto generated R starter code for data set election-staenderatswahl-2015@staatskanzlei-zug.

## Metadata

- **Publisher** `Staatskanzlei Zug`
- **Organization.display_name.de** `Staatskanzlei Zug`
- **Organization.url** ``
- **Maintainer** `Staatskanzlei Zug`
- **Maintainer_email** `info@zg.ch`
- **Keywords.de** `['wahl', 'kantonal']`
- **Issued** `2015-10-18T00:00:00`
- **Metadata_created** `2017-10-05T09:24:03.257774`
- **Metadata_modified** `2023-12-18T02:47:53.584706`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : d12a8938-37fc-4a8a-a5d5-5b4a658dcb12
# Description              : 
# Issued                   : 2016-06-03T11:03:27+00:00
# Modified                 : 2023-10-04T08:47:59+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://wab.zug.ch/election/staenderatswahl-2015/data-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

info@zg.ch | Staatskanzlei Zug
