---
title: "Open Government Data, opendata.swiss"
date: "2025-06-29"
output: html_document
---

## Dataset: Entsorgungsdaten Sonderabfallmobil

Sammeltage Sonderabfall nach Station / PLZ

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/entsorgungsdaten-sonderabfallmobil)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_sonderabfall)

Auto generated R starter code for data set 96e74835-5678-406c-b86f-7a99f5dfff77@stadt-zurich.

## Metadata

- **Publisher.name** `Entsorgung + Recycling Zürich, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['tabellen', 'entsorgungskalender', 'entsorgungsdaten', 'sachdaten', 'entsorgung', 'kalender', 'abfall']`
- **Issued** `2012-06-25T00:00:00`
- **Metadata_created** `2024-12-03T03:38:14.265284`
- **Metadata_modified** `2025-06-28T03:04:43.652930`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : d241d81b-07ec-403d-9d36-d56562e5e1cc
# Description              : 
# Issued                   : 2024-02-12T07:59:56.493096
# Modified                 : 2025-06-27T16:11:15.143750
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_sonderabfall/download/entsorgungskalender_sonderabfall_2024.csv')

# Distribution 1
# Package_id               : d241d81b-07ec-403d-9d36-d56562e5e1cc
# Description              : 
# Issued                   : 2024-02-12T07:59:57.092676
# Modified                 : 2025-06-27T16:11:16.810329
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_sonderabfall/download/entsorgungskalender_sonderabfall_2025.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
