---
title: "Open Government Data, opendata.swiss"
date: "2024-05-25"
output: html_document
---

## Dataset: Wohnungsbestand nach Eigentumsart, Zimmerzahl und Stadtquartier seit 2010


Der Datensatz enthält den Wohnungsbestand in der Stadt Zürich nach Eigentumsart, Zimmerzahl und Stadtquartier seit 2010.



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/wohnungsbestand-nach-eigentumsart-zimmerzahl-und-stadtquartier-seit-20102)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/bau_whg_bestand_ea_zizahl_quartier_seit2010_od5221)

Auto generated R starter code for data set 6e37c17e-9c2d-4b32-9a3c-4acffa962597@stadt-zurich.

## Metadata

- **Publisher** `Statistik Stadt Zürich, Präsidialdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['tabelle', 'sachdaten', 'gwz', 'wohnung', 'zeitreihe', 'grundangebot-baur', 'sasa', 'quartier', 'bauwesen']`
- **Issued** `2018-11-30T00:00:00`
- **Metadata_created** `2023-10-30T01:57:19.906755`
- **Metadata_modified** `2024-05-25T03:06:14.578157`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : d2819893-25d2-48d9-9801-f9b17d7d8a39
# Description              : 
# Issued                   : 2019-07-29T13:23:08.991498
# Modified                 : 2024-05-24T20:47:51.109942
# Rights                   : None

df <- read_delim('https://data.stadt-zuerich.ch/dataset/bau_whg_bestand_ea_zizahl_quartier_seit2010_od5221/download/BAU522OD5221.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
