---
title: "Open Government Data, opendata.swiss"
date: "2024-07-13"
output: html_document
---

## Dataset: Grosser Rat: Dokumente

Dieser Datensatz zeigt Dokumente von Geschäften, die im Grossen Rat des Kantons Basel-Stadt behandelt werden.Die Daten können auch auf der Webseite des Grossen Rates eingesehen werden:https://grosserrat.bs.ch

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/grosser-rat-dokumente)<br>
[Direct link by **Kanton Basel-Stadt** for dataset](https://data.bs.ch/explore/dataset/100313/)

Auto generated R starter code for data set 100313@kanton-basel-stadt.

## Metadata

- **Publisher** `Parlamentsdienst des Grossen Rats`
- **Organization.display_name.de** `Kanton Basel-Stadt`
- **Organization.url** `https://www.opendata.bs.ch`
- **Maintainer** `Fachstelle für OGD Basel-Stadt`
- **Maintainer_email** `opendata@bs.ch`
- **Keywords.de** `['parlamentarische-vorstosse', 'regierungsrat', 'parlament', 'grosser-rat']`
- **Issued** `2023-09-29T00:00:00`
- **Metadata_created** `2023-09-30T00:27:58.562078`
- **Metadata_modified** `2024-07-13T02:30:03.890385`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : d33b1737-7122-4aec-8bd1-31bdb7b7ca97
# Description              : Grosser Rat: Dokumente (csv)
# Issued                   : 2023-09-29T00:00:00
# Modified                 : 2024-07-09T08:04:22.572000+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://data.bs.ch/api/v2/catalog/datasets/100313/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@bs.ch | Fachstelle für OGD Basel-Stadt
