---
title: "Open Government Data, opendata.swiss"
date: "2025-07-22"
output: html_document
---

## Dataset: Basler Index der Konsumentenpreise

Entwicklung des Basler Index der Konsumentenpreise BIK (Basis Dezember 2020 = 100) nach Hauptgruppe seit 1939.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/basler-index-der-konsumentenpreise)<br>
[Direct link by **Kanton Basel-Stadt** for dataset](https://data.bs.ch/explore/dataset/100003/)

Auto generated R starter code for data set 100003@kanton-basel-stadt.

## Metadata

- **Publisher.name** `Statistisches Amt`
- **Organization.display_name.de** `Kanton Basel-Stadt`
- **Organization.url** `https://data.bs.ch/pages/home/`
- **Maintainer** `Fachstelle für OGD Basel-Stadt`
- **Maintainer_email** `opendata@bs.ch`
- **Keywords.de** `['index', 'warenkorb', 'teuerung', 'konsum', 'preise']`
- **Issued** `2019-11-06T00:00:00`
- **Metadata_created** `2021-09-03T09:21:53.645523`
- **Metadata_modified** `2025-07-22T03:10:09.568541`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : d5377886-7b76-434e-860c-a9d58045347a
# Description              : Basler Index der Konsumentenpreise (csv)
# Issued                   : 2019-11-06T00:00:00
# Modified                 : 2025-07-03T06:39:41.474000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.bs.ch/api/v2/catalog/datasets/100003/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@bs.ch | Open Data Basel-Stadt
