---
title: "Open Government Data, opendata.swiss"
date: "2024-01-10"
output: html_document
---

## Dataset: Wohnviertel der Stadt St.Gallen (Statistische Quartiere)

Wohnviertel

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/wohnviertel-der-stadt-st-gallen-statistische-quartiere)<br>
[Direct link by **Stadt St.Gallen** for dataset](https://daten.stadt.sg.ch/explore/dataset/wohnviertel/)

Auto generated R starter code for data set wohnviertel@stadt-st-gallen.

## Metadata

- **Publisher** `stadt-st-gallen`
- **Organization.display_name.de** `Stadt St.Gallen`
- **Organization.url** `2023-12-21-092646.943088Logostgallenrgb300dpi.jpg`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['stadtkreis', 'quartiere', 'statistik', 'viertel', 'stadtteil']`
- **Issued** `2023-08-23T04:30:05+00:00`
- **Metadata_created** `2023-12-21T12:47:58.918884`
- **Metadata_modified** `2024-01-05T09:34:49.227269`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : d646a93d-d802-4a7e-b2eb-116f9658451a
# Description              : Wohnviertel der Stadt St.Gallen (Statistische Quartiere) (csv)
# Issued                   : 2023-08-23T04:30:05+00:00
# Modified                 : 2023-08-23T04:30:05+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://daten.stadt.sg.ch/api/v2/catalog/datasets/wohnviertel/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@stadt.sg.ch | OGD-Koordinationsstelle St.Gallen
