---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Brücken

Die Brücke ist ein Bauwerk, das über eine Strasse oder über ein Hindernis führt. Eine kleine Brücke bis 2 Meter wird als Durchlass bezeichnet. Brücken werden als Gesamtobjekt bestehend aus einzelnen Brückenbaueinheiten abgebildet. Letzter/last Update Juni 2021The bridge is a structure that crosses a road or an obstacle. A small bridge up to 2 meters is called a passage. Bridges are represented as a complete object consisting of individual bridge construction units.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/brucken1)<br>
[Direct link by **Schweizerische Bundesbahnen SBB** for dataset](https://data.sbb.ch/explore/dataset/brucken/)

Auto generated R starter code for data set brucken@schweizerische-bundesbahnen-sbb.

## Metadata

- **Publisher** `schweizerische-bundesbahnen-sbb`
- **Organization.display_name.de** `Schweizerische Bundesbahnen SBB`
- **Organization.url** ``
- **Maintainer** `Ansprechsstelle für Daten`
- **Maintainer_email** `data@sbb.ch`
- **Keywords.de** `['infrastruktur']`
- **Issued** `2017-12-05T00:00:00`
- **Metadata_created** `2019-09-11T10:47:48.290655`
- **Metadata_modified** `2023-01-16T00:28:07.038500`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : d6a83c67-0ad9-4196-98b0-5580c1e13e41
# Description              : Brücken (csv)
# Issued                   : 2017-12-05T00:00:00
# Modified                 : 2022-06-02T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://data.sbb.ch/api/v2/catalog/datasets/brucken/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

data@sbb.ch | Ansprechsstelle für Daten
