---
title: "Open Government Data, opendata.swiss"
date: "2025-03-03"
output: html_document
---

## Dataset: Bevölkerungsbilanz nach Gemeinde und Quartal (seit 2003)

Kantonale Bevölkerungsstatistik

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/bevolkerungsbilanz-nach-gemeinde-und-quartal-ab-2003)<br>
[Direct link by **Kanton Basel-Landschaft** for dataset](https://data.bl.ch/explore/dataset/10680/)

Auto generated R starter code for data set 10680@kanton-basel-landschaft.

## Metadata

- **Publisher** `kanton-basel-landschaft`
- **Organization.display_name.de** `Kanton Basel-Landschaft`
- **Organization.url** `https://www.baselland.ch`
- **Maintainer** `Tamara Bobst`
- **Maintainer_email** `tamara.bobst@bl.ch`
- **Keywords.de** `['burgerrechtswechsel', 'quartalsdaten', 'anfangsbestand', 'statistikdaten', 'wegzuge', 'todesfalle', 'wanderungen', 'endbestand', 'geburten', 'zuzuge']`
- **Issued** `2022-11-30T00:00:00`
- **Metadata_created** `2022-12-13T15:07:30.356169`
- **Metadata_modified** `2025-03-03T03:35:05.353567`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : dcd9e1bf-b9ca-44fc-a6c5-00822428c7dd
# Description              : Bevölkerungsbilanz nach Gemeinde und Quartal (seit 2003) (csv)
# Issued                   : 2022-11-30T00:00:00
# Modified                 : 2025-02-24T09:47:16.874000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.bl.ch/api/v2/catalog/datasets/10680/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

statistik@bl.ch | Fachbereich Demografie
