---
title: "Open Government Data, opendata.swiss"
date: "2024-12-02"
output: html_document
---

## Dataset: Sanitäre Anlagen

Öffentliche sanitäre Anlagen der Gemeinden Basel, Riehen und Bettingen: WC Anlage, WC Anlage rollstuhlgängig, nur Pissoir, Dusche, Anlage geschlossen (in Sanierung oder geschlossen).

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/sanitare-anlagen)<br>
[Direct link by **Kanton Basel-Stadt** for dataset](https://data.bs.ch/explore/dataset/100031/)

Auto generated R starter code for data set 100031@kanton-basel-stadt.

## Metadata

- **Publisher** `Tiefbauamt`
- **Organization.display_name.de** `Kanton Basel-Stadt`
- **Organization.url** `https://www.opendata.bs.ch`
- **Maintainer** `Fachstelle für OGD Basel-Stadt`
- **Maintainer_email** `opendata@bs.ch`
- **Keywords.de** `['toilette', 'wc', 'abort']`
- **Issued** `2019-11-06T00:00:00`
- **Metadata_created** `2022-06-14T07:36:45.309336`
- **Metadata_modified** `2024-12-02T01:44:37.802556`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : de39dcb1-6490-4b7f-b353-9c32a95da2fd
# Description              : Sanitäre Anlagen (csv)
# Issued                   : 2019-11-06T00:00:00
# Modified                 : 2024-12-01T05:07:57.972000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://data.bs.ch/api/v2/catalog/datasets/100031/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@bs.ch | Fachstelle für OGD Basel-Stadt
