---
title: "Open Government Data, opendata.swiss"
date: "2024-01-19"
output: html_document
---

## Dataset: Bevölkerung, seit 1901


Wirtschaftliche Wohnbevölkerung der Stadt Zürich nach Jahr, seit 1901.


[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/bevolkerung-seit-1901)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/bev_bestand_jahr_od3243)

Auto generated R starter code for data set 5c353669-41d3-45bd-a6c5-e8b6d89404e5@stadt-zurich.

## Metadata

- **Publisher** `Bevölkerungsamt, Präsidialdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['zeitreihe', 'bevolkerungsbestand', 'sasa', 'alter', 'sachdaten', 'quartier', 'tabelle']`
- **Issued** `nan`
- **Metadata_created** `2023-08-11T01:09:03.713262`
- **Metadata_modified** `2024-01-19T03:18:24.899775`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : dfb5dc5f-f314-4d33-8be8-71143ce1f631
# Description              : 
# Issued                   : 2023-10-08T08:14:53.268353
# Modified                 : 2024-01-18T20:58:05.006075
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/bev_bestand_jahr_od3243/download/BEV324OD3243.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
