---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Haltestelle: Billettautomat

Standorte der Billettautomaten der SBB. An den  Ticketautomaten der SBB können neben Bahntickets weitere Produkte bezogen werden.Diese enthalten - Prepay Guthaben für Mobiltelefone- Prepay Guthaben für paysafe- Kauf von Bitcoinshttp://www.sbb.ch/bahnhof-services/am-bahnhof/dienstleistungen-am-bahnhof/billettautomat.htmlLocations of SBB ticket vending machines. In addition to rail tickets, other products can be purchased at SBB ticket machines.These include - Prepay credit for mobile phones- Prepay credit for paysafe- Purchase of Bitcoinshttp://www.sbb.ch/bahnhof-services/am-bahnhof/dienstleistungen-am-bahnhof/billettautomat.html

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/haltestelle-billettautomat)<br>
[Direct link by **Schweizerische Bundesbahnen SBB** for dataset](https://data.sbb.ch/explore/dataset/billetautomat/)

Auto generated R starter code for data set billetautomat@schweizerische-bundesbahnen-sbb.

## Metadata

- **Publisher** `schweizerische-bundesbahnen-sbb`
- **Organization.display_name.de** `Schweizerische Bundesbahnen SBB`
- **Organization.url** ``
- **Maintainer** `Ansprechsstelle für Daten`
- **Maintainer_email** `data@sbb.ch`
- **Keywords.de** `['verkehr', 'dienstleistung', 'infrastruktur', 'bahnhof']`
- **Issued** `2023-01-10T00:00:00`
- **Metadata_created** `2019-09-11T10:45:17.092673`
- **Metadata_modified** `2023-01-16T00:28:48.433232`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : e0ba5c28-aa84-4b28-93a1-4ea9caa88a34
# Description              : Haltestelle: Billettautomat (csv)
# Issued                   : 2023-01-10T00:00:00
# Modified                 : 2023-01-10T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://data.sbb.ch/api/v2/catalog/datasets/billetautomat/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

data@sbb.ch | Ansprechsstelle für Daten
