---
title: "Open Government Data, opendata.swiss"
date: "2023-11-08"
output: html_document
---

## Dataset: Familienzentrum

Familienzentrumstandorte in der Stadt Z端rich

**Zweck**: Lokalisierung Familienzentrum

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/familienzentrum)<br>
[Direct link by **Stadt Z端rich** for dataset](https://data.stadt-zuerich.ch/dataset/geo_familienzentrum)

Auto generated R starter code for data set 542501c6-8acb-4050-85e5-c058e877ddcd@stadt-zurich.

## Metadata

- **Publisher** `Integration & Soziokultur, Departementssekretariat SD, Sozialdepartement`
- **Organization.display_name.de** `Stadt Z端rich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['geodaten', 'eltern-kind-zentrum', 'geoportal', 'kinderhaus', 'punktdaten', 'familien', 'vektordaten', 'stzh']`
- **Issued** `nan`
- **Metadata_created** `2023-11-07T03:43:23.446758`
- **Metadata_modified** `2023-11-08T03:36:24.074710`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : e14ff65c-5ad6-4a88-a0ad-8114f6becf0c
# Description              : 
# Issued                   : 2023-11-06T03:25:56.407638
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.stadt-zuerich.ch/geodaten/download/Familienzentrum?format=10008')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Z端rich
