---
title: "Open Government Data, opendata.swiss"
date: "2024-03-20"
output: html_document
---

## Dataset: Entsorgungskalender Karton

Sammeltage der Kartonentsorgung nach PLZ

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/entsorgungskalender-karton2)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_karton)

Auto generated R starter code for data set ac36f33b-2685-4b03-83c5-1d2e21ba50ee@stadt-zurich.

## Metadata

- **Publisher** `Entsorgung + Recycling Zürich, Tiefbau- und Entsorgungsdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['sachdaten', 'abfall', 'kalender', 'entsorgung', 'tabellen', 'entsorgungskalender']`
- **Issued** `2012-06-25T00:00:00`
- **Metadata_created** `2023-12-02T02:25:49.049812`
- **Metadata_modified** `2024-03-19T04:12:30.019941`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : e282f855-2a0c-4232-af19-fbda617e3835
# Description              : 
# Issued                   : 2023-01-12T11:55:03.008006
# Modified                 : 2024-03-18T16:10:31.258752
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_karton/download/entsorgungskalender_karton_2023.csv')

# Distribution 1
# Package_id               : e282f855-2a0c-4232-af19-fbda617e3835
# Description              : 
# Issued                   : 2023-01-12T11:55:04.090015
# Modified                 : 2024-03-18T16:10:32.522706
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/erz_entsorgungskalender_karton/download/entsorgungskalender_karton_2024.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
