---
title: "Open Government Data, opendata.swiss"
date: "2024-10-28"
output: html_document
---

## Dataset: Mortality of regeneration: Acer spp. and Fagus sylvatica



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/mortality-of-regeneration-acer-spp-and-fagus-sylvatica)<br>
[Direct link by **EnviDat: das Umwelt-Datenportal** for dataset](https://www.envidat.ch/#/metadata/mortality-of-regeneration-acer-spp-and-fagus-sylvatica)

Auto generated R starter code for data set 8d9df0cd-f20c-423f-a4ab-71fc213871de@envidat.

## Metadata

- **Publisher** `EnviDat`
- **Organization.display_name.de** `EnviDat: das Umwelt-Datenportal`
- **Organization.url** `https://www.envidat.ch/`
- **Maintainer** `Roksolana Petrovska`
- **Maintainer_email** `roksolana.petrovska@gmail.com`
- **Keywords.de** `[]`
- **Issued** `2021-11-04T16:03:34+00:00`
- **Metadata_created** `2021-11-06T03:46:31.432136`
- **Metadata_modified** `2024-10-26T04:44:48.376853`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : e2ee7304-c840-4c6a-b38c-950698a37e21
# Description              : 
# Issued                   : 2021-11-04T16:06:51+00:00
# Modified                 : 2021-11-04T16:06:51+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://www.envidat.ch/dataset/mortality-of-regeneration-acer-spp-and-fagus-sylvatica/resource/37fb69d9-c553-4931-89ba-31857ac15c04')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

envidat@wsl.ch | EnviDat Support
