---
title: "Open Government Data, opendata.swiss"
date: "2025-08-23"
output: html_document
---

## Dataset: Strassenverkehrsunf채lle

Die Strassenverkehrsunf채lle im Kanton Basel-Stadt seit 2011 werden nach Unfalltyp und Unfallschweregrad kategorisiert dargestellt. Die Daten werden j채hrlich aktualisiert.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/strassenverkehrsunfalle1)<br>
[Direct link by **Kanton Basel-Stadt** for dataset](https://data.bs.ch/explore/dataset/100120/)

Auto generated R starter code for data set 100120@kanton-basel-stadt.

## Metadata

- **Publisher.name** `nan`
- **Organization.display_name.de** `Kanton Basel-Stadt`
- **Organization.url** `https://data.bs.ch/pages/home/`
- **Maintainer** `Open Data Basel-Stadt`
- **Maintainer_email** `opendata@bs.ch`
- **Keywords.de** `['fussganger', 'verkehrsunfall', 'verkehrsunfalle', 'velo', 'unfall', 'gefahrdung', 'auto', 'schaden', 'motorrader']`
- **Issued** `2022-03-27T00:00:00`
- **Metadata_created** `2024-02-13T02:09:16.067184`
- **Metadata_modified** `2025-08-23T01:35:02.585941`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : e8e51461-5222-472a-8b1f-1fae68943db2
# Description              : Strassenverkehrsunf채lle (csv)
# Issued                   : 2022-03-27T00:00:00
# Modified                 : 2025-08-22T05:05:13.190000+00:00
# Rights                   : http://www.opendefinition.org/licenses/cc-by/

df <- read_delim('https://data.bs.ch/api/v2/catalog/datasets/100120/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@bs.ch | Open Data Basel-Stadt
