---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Wohnungssaldo durch Umbau seit 2015

Der Datensatz enthält den Wohnungssaldo durch Umbauten nach Jahr, Stadtkreis, Eigentumsart und Wohnungsgrösse seit 2015.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/wohnungssaldo-durch-umbau-seit-2015)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/bau_whg_bestand_umbau_ea_zizahlkat_kreis_saldo_jahr_od5101)

Auto generated R starter code for data set 5b749466-d6b8-43e3-b99f-dfa082c69787@stadt-zurich.

## Metadata

- **Publisher** `Statistik Stadt Zürich, Präsidialdepartement`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['sachdaten', 'kreis-wohnen', 'zeitreihe', 'stistische-zone', 'tabelle', 'bauwesen', 'bautatigkeit', 'umbau']`
- **Issued** `2017-02-28T00:00:00`
- **Metadata_created** `2021-11-09T02:50:57.061283`
- **Metadata_modified** `2023-01-16T00:49:35.277234`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : ed4d5069-b921-4efe-8d1e-77d7a00d3d27
# Description              : 
# Issued                   : 2021-11-08T00:00:00
# Modified                 : 2023-01-16T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/bau_whg_bestand_umbau_ea_zizahlkat_kreis_saldo_jahr_od5101/download/BAU510OD5101.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
