---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Hunde - Namen der Rüden

Rangfolge, Total und nach Sprachregion die häufigsten Namen der registrierten, lebenden Rüden. Tiere ohne Namen oder mit «technischen» Namensbezeichnungen werden in der Darstellung nicht berücksichtigt.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/hunde-namen-der-ruden)<br>
[Direct link by **Identitas AG** for dataset](https://tierstatistik.identitas.ch/)

Auto generated R starter code for data set dogs-topNamesMale@identitas.

## Metadata

- **Publisher** `Identitas AG`
- **Organization.display_name.de** `Identitas AG`
- **Organization.url** `http://www.identitas.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['namenshitparade', 'hunde', 'heimtiere', 'mannlich']`
- **Issued** `nan`
- **Metadata_created** `2022-06-07T11:23:54.125065`
- **Metadata_modified** `2023-01-10T01:10:38.192529`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : f0ac4a83-af2d-4928-a1fa-3512c4526613
# Description              : 
# Issued                   : None
# Modified                 : None
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://tierstatistik.identitas.ch/data/dogs-topNamesMale.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tierstatistik@identitas.ch | Team Tierstatistik Identitas AG
