---
title: "Open Government Data, opendata.swiss"
date: "2023-03-30"
output: html_document
---

## Dataset: Ständeratswahlen 2015

Schlussresultate der kantonalen Wahl 'Ständeratswahlen 2015', 18. Oktober 2015, Kanton Basel-Landschaft, aufgeschlüsselt nach Kandidaten und Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/standeratswahlen-20151)<br>
[Direct link by **Kanton Basel-Landschaft** for dataset](https://abstimmungen.bl.ch/election/staenderatswahlen-2015/data)

Auto generated R starter code for data set election-staenderatswahlen-2015@kanton-basel-landschaft.

## Metadata

- **Publisher** `Basel-Landschaft`
- **Organization.display_name.de** `Kanton Basel-Landschaft`
- **Organization.url** `https://www.bl.ch`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['kantonal', 'wahl']`
- **Issued** `2015-10-18T00:00:00`
- **Metadata_created** `2023-01-17T01:26:19.604493`
- **Metadata_modified** `2023-03-30T01:58:09.869806`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : f2449e81-c63e-41c0-a314-160d6d7c9163
# Description              : 
# Issued                   : 2023-01-16T00:00:00
# Modified                 : 2023-02-01T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://abstimmungen.bl.ch/election/staenderatswahlen-2015/data-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

wahlen-abstimmungen@bl.ch | Basel-Landschaft
