---
title: "Open Government Data, opendata.swiss"
date: "2023-08-16"
output: html_document
---

## Dataset: Bevölkerungsbestand nach Nationalität, Konfession, Gemeinde und Quartal (seit 2003)

Kantonale Bevölkerungsstatistik (Quartalserhebung)

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/bevolkerungsbestand-nach-nationalitat-konfession-gemeinde-und-quartal-ab-2003)<br>
[Direct link by **Kanton Basel-Landschaft** for dataset](https://data.bl.ch/explore/dataset/10020/)

Auto generated R starter code for data set 10020@kanton-basel-landschaft.

## Metadata

- **Publisher** `kanton-basel-landschaft`
- **Organization.display_name.de** `Kanton Basel-Landschaft`
- **Organization.url** `https://www.baselland.ch`
- **Maintainer** `Tamara Bobst`
- **Maintainer_email** `tamara.bobst@bl.ch`
- **Keywords.de** `['schweizerinnen', 'auslanderinnen', 'quartalsdaten', 'manner', 'frauen']`
- **Issued** `2022-09-05T00:00:00`
- **Metadata_created** `2022-12-13T15:08:32.995767`
- **Metadata_modified** `2023-08-16T01:51:14.737747`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : f2f5edd8-ae58-4ef8-b15c-046a595905a5
# Description              : Bevölkerungsbestand nach Nationalität, Konfession, Gemeinde und Quartal (seit 2003) (csv)
# Issued                   : 2022-09-05T00:00:00
# Modified                 : 2023-07-03T06:34:55.841000+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://data.bl.ch/api/v2/catalog/datasets/10020/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

tamara.bobst@bl.ch | Tamara Bobst
