---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Wahlbeteiligung Nationalrat [%]

Gültig eingelegte Listen (Wahlzettel) dividiert durch Anzahl Wahlberechtigte

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/wahlbeteiligung-nationalrat)<br>
[Direct link by **Statistisches Amt Kanton Zürich** for dataset](https://www.zh.ch/de/politik-staat/gemeinden/gemeindeportraet.html)

Auto generated R starter code for data set 282@statistisches-amt-kanton-zuerich.

## Metadata

- **Publisher** `Statistisches Amt des Kantons Zürich`
- **Organization.display_name.de** `Statistisches Amt Kanton Zürich`
- **Organization.url** `https://www.zh.ch/de/direktion-der-justiz-und-des-innern/statistisches-amt.html`
- **Maintainer** `Statistisches Amt des Kantons Zürich, Data Shop`
- **Maintainer_email** `datashop@statistik.zh.ch`
- **Keywords.de** `['gemeinden', 'kantonzuerich', 'politik', 'bezirke', 'wahlbeteiligung', 'nationalratswahlen', 'wahlen']`
- **Issued** `2016-01-20T00:00:00`
- **Metadata_created** `2021-01-14T17:52:07.147029`
- **Metadata_modified** `2023-01-16T03:06:31.029266`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : f3c636a4-944c-4adb-b40c-4c589e747be8
# Description              : 
# Issued                   : 2016-01-21T00:00:00
# Modified                 : 2019-10-21T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.web.statistik.zh.ch/ogd/data/KANTON_ZUERICH_804.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

datashop@statistik.zh.ch | Statistisches Amt des Kantons Zürich, Data Shop
