---
title: "Open Government Data, opendata.swiss"
date: "2024-08-01"
output: html_document
---

## Dataset: Gemeinderatswahlen Wahlbeteiligung

Gemeinderatswahlen Wahlbeteiligung.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/gemeinderatswahlen-wahlbeteiligung-seit-18921)<br>
[Direct link by **Stadt Zürich** for dataset](https://data.stadt-zuerich.ch/dataset/politik_gemeinderatswahlen_wahbeteiligung_seit1892_od7002)

Auto generated R starter code for data set 4d8eafe6-d404-41eb-8f06-e325a64a2780@stadt-zurich.

## Metadata

- **Publisher** `Statistik Stadt Zürich; Allgemeine Verwaltung, Stadtkanzlei (SKZ)`
- **Organization.display_name.de** `Stadt Zürich`
- **Organization.url** `http://www.stadt-zuerich.ch/opendata`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords.de** `['zeitreihe', 'sachdaten', 'tabelle', 'wahlen', 'sasa', 'politik', 'gemeinderatswahlen', 'wahlbeteiligung']`
- **Issued** `2018-03-26T00:00:00`
- **Metadata_created** `2019-07-30T00:37:46.793301`
- **Metadata_modified** `2024-08-01T03:13:27.628527`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : f521d9d2-334e-4ee8-8606-e7ba850e1c83
# Description              : 
# Issued                   : 2019-07-29T13:25:42.743189
# Modified                 : 2024-07-31T20:58:35.346119
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://data.stadt-zuerich.ch/dataset/politik_gemeinderatswahlen_wahbeteiligung_seit1892_od7002/download/POL700OD7002.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch | Open Data Zürich
