---
title: "Open Government Data, opendata.swiss"
date: "2024-11-15"
output: html_document
---

## Dataset: OGD Datensätze

Metadaten zu den im vorliegenden Datenportal publizierten OGD Datensätzen.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/ogd-datensatze)<br>
[Direct link by **Kanton Basel-Stadt** for dataset](https://data.bs.ch/explore/dataset/100057/)

Auto generated R starter code for data set 100057@kanton-basel-stadt.

## Metadata

- **Publisher** `Fachstelle für OGD Basel-Stadt`
- **Organization.display_name.de** `Kanton Basel-Stadt`
- **Organization.url** `https://www.opendata.bs.ch`
- **Maintainer** `Fachstelle für OGD Basel-Stadt`
- **Maintainer_email** `opendata@bs.ch`
- **Keywords.de** `['ogd', 'datensatz', 'metadaten']`
- **Issued** `2019-11-06T00:00:00`
- **Metadata_created** `2023-07-04T12:35:51.322807`
- **Metadata_modified** `2024-11-15T01:51:50.373653`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : f7813433-e2b5-4c2a-b6ba-e806314b25ed
# Description              : OGD Datensätze (csv)
# Issued                   : 2019-11-06T00:00:00
# Modified                 : 2024-11-15T01:03:12.863000+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_open

df <- read_delim('https://data.bs.ch/api/v2/catalog/datasets/100057/exports/csv?use_labels=true')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@bs.ch | Fachstelle für OGD Basel-Stadt
