---
title: "Open Government Data, opendata.swiss"
date: "2023-12-31"
output: html_document
---

## Dataset: W채rmeversorgung

Download PDF Erl채uterungen Energieplan - W채rmeversorgung	

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/warmeversorgung)<br>
[Direct link by **Stadt St.Gallen** for dataset](https://daten.stadt.sg.ch/explore/dataset/warmeversorgung/)

Auto generated R starter code for data set warmeversorgung@stadt-st-gallen.

## Metadata

- **Publisher** `stadt-st-gallen`
- **Organization.display_name.de** `Stadt St.Gallen`
- **Organization.url** `2023-12-21-092646.943088Logostgallenrgb300dpi.jpg`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `['energy-hackdays']`
- **Issued** `2020-10-31T00:00:00`
- **Metadata_created** `2023-12-21T12:46:54.700439`
- **Metadata_modified** `2023-12-21T16:40:55.724473`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : f7bafa7c-4e2c-4add-a7f7-3509068715e6
# Description              : W채rmeversorgung (csv)
# Issued                   : 2020-10-31T00:00:00
# Modified                 : 2023-08-23T04:30:08+00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://daten.stadt.sg.ch/api/v2/catalog/datasets/warmeversorgung/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@stadt.sg.ch | OGD-Koordinationsstelle St.Gallen
