---
title: "Open Government Data, opendata.swiss"
date: "2023-01-16"
output: html_document
---

## Dataset: Abfahrtsplakate

Abfahrtsplakate der SBB Haltestellen. Aktualisierung erfolgt laufend. Departure posters of the SBB stops. Updated on an ongoing basis. 

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/abfahrtsplakate2)<br>
[Direct link by **Schweizerische Bundesbahnen SBB** for dataset](https://data.sbb.ch/explore/dataset/abfahrtsplakate0/)

Auto generated R starter code for data set abfahrtsplakate0@schweizerische-bundesbahnen-sbb.

## Metadata

- **Publisher** `schweizerische-bundesbahnen-sbb`
- **Organization.display_name.de** `Schweizerische Bundesbahnen SBB`
- **Organization.url** ``
- **Maintainer** `Ansprechsstelle für Daten`
- **Maintainer_email** `data@sbb.ch`
- **Keywords.de** `['verkehr']`
- **Issued** `2019-12-14T00:00:00`
- **Metadata_created** `2019-12-13T21:46:24.609188`
- **Metadata_modified** `2023-01-16T00:27:49.585248`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : fa09506b-f05f-4367-bee6-130e523909d7
# Description              : Abfahrtsplakate (csv)
# Issued                   : 2019-12-14T00:00:00
# Modified                 : 2022-12-19T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://data.sbb.ch/api/v2/catalog/datasets/abfahrtsplakate0/exports/csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

data@sbb.ch | Ansprechsstelle für Daten
