---
title: "Open Government Data, opendata.swiss"
date: "2024-11-24"
output: html_document
---

## Dataset: Landratswahlen 2015 Wahlkreis Reinach

Schlussresultate der regionalen Wahl 'Landratswahlen 2015 Wahlkreis Reinach', 8. Februar 2015, Kanton Basel-Landschaft, aufgeschlüsselt nach Kandidaten und Gemeinden.

[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/landratswahlen-2015-wahlkreis-reinach)<br>
[Direct link by **Kanton Basel-Landschaft** for dataset](https://abstimmungen.bl.ch/election/landratswahlen-2015-region-2-4-reinach/data)

Auto generated R starter code for data set election-landratswahlen-2015-region-2-4-reinach@kanton-basel-landschaft.

## Metadata

- **Publisher** `Basel-Landschaft`
- **Organization.display_name.de** `Kanton Basel-Landschaft`
- **Organization.url** `https://www.baselland.ch`
- **Maintainer** `Basel-Landschaft`
- **Maintainer_email** `wahlen-abstimmungen@bl.ch`
- **Keywords.de** `['regional-district', 'wahl']`
- **Issued** `2015-02-08T00:00:00`
- **Metadata_created** `2023-01-18T01:12:22.329959`
- **Metadata_modified** `2024-10-03T19:04:35.117134`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : fa5a2bc1-dc25-4adc-98bb-6143eec963bc
# Description              : 
# Issued                   : 2023-01-17T08:04:57+00:00
# Modified                 : 2024-04-17T05:32:50+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://abstimmungen.bl.ch/election/landratswahlen-2015-region-2-4-reinach/data-parties-csv')

# Distribution 1
# Package_id               : fa5a2bc1-dc25-4adc-98bb-6143eec963bc
# Description              : 
# Issued                   : 2023-01-17T08:04:57+00:00
# Modified                 : 2024-04-17T05:32:50+00:00
# Rights                   : https://opendata.swiss/terms-of-use#terms_by

df <- read_delim('https://abstimmungen.bl.ch/election/landratswahlen-2015-region-2-4-reinach/data-csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

wahlen-abstimmungen@bl.ch | Basel-Landschaft
