---
title: "Open Government Data, opendata.swiss"
date: "2023-05-12"
output: html_document
---

## Dataset: Test GO dataset 2



[Direct link by **opendata.swiss** for dataset](https://opendata.swiss/de/dataset/test-go-dataset-2)<br>
[Direct link by **Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)** for dataset](https://opentransportdata.swiss/dataset/test-go-dataset-2)

Auto generated R starter code for data set test-go-dataset-2@oevch.

## Metadata

- **Publisher** `Publisher 1`
- **Organization.display_name.de** `Geschäftsstelle Systemaufgaben Kundeninformation (SBB AG)`
- **Organization.url** `https://www.opentransportdata.swiss`
- **Maintainer** `None`
- **Maintainer_email** `None`
- **Keywords.de** `[]`
- **Issued** `2023-05-11T00:00:00`
- **Metadata_created** `2023-05-12T00:44:03.129550`
- **Metadata_modified** `2023-05-12T00:44:03.129557`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 4 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Package_id               : fbb2837c-8b6c-4fdb-a97d-897193f6ca07
# Description              : 
# Issued                   : 2023-05-11T00:00:00
# Modified                 : 2023-05-11T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/56b8bd52-596f-415c-bd91-fb2b8c259525/resource/360348a8-7b8f-4d97-b50a-3fb947af4958/download/future_timetable_business_organisation_versions_2023-05-09.csv')

# Distribution 1
# Package_id               : fbb2837c-8b6c-4fdb-a97d-897193f6ca07
# Description              : 
# Issued                   : 2023-05-11T00:00:00
# Modified                 : 2023-05-11T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/56b8bd52-596f-415c-bd91-fb2b8c259525/resource/49352dfd-f02a-4616-90a9-0dd40773774f/download/future_timetable_business_organisation_versions_2023-05-08.csv')

# Distribution 2
# Package_id               : fbb2837c-8b6c-4fdb-a97d-897193f6ca07
# Description              : 
# Issued                   : 2023-05-11T00:00:00
# Modified                 : 2023-05-11T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/56b8bd52-596f-415c-bd91-fb2b8c259525/resource/c546c9ca-81dc-434d-8a04-0d5603b3d3d4/download/future_timetable_business_organisation_versions_2023-05-11.csv')

# Distribution 3
# Package_id               : fbb2837c-8b6c-4fdb-a97d-897193f6ca07
# Description              : 
# Issued                   : 2023-05-11T00:00:00
# Modified                 : 2023-05-11T00:00:00
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://opentransportdata.swiss/dataset/56b8bd52-596f-415c-bd91-fb2b8c259525/resource/fe808f74-34cc-4e49-b3f9-5cc30d420edc/download/future_timetable_business_organisation_versions_2023-05-10.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

contact@example.com | Contact Name
